### 2025-04-10 Live_Scripts/R_version_Rubisco_activation/Scripts/Temperature-response-of-Rubisco-activation-in-rice.Rmd
Add files via upload

---
title: "Temperature response of Rubisco activation state in rice"
author: "Supreeta Vijayakumar"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(readxl)
library(ggplot2)
```

## Data Extraction

To modify the regulation of Rubisco in the e-Photosynthesis model, we need to fit a model to be able to predict the response of activation state in rice to changes in temperature.

\
There is published data in Fig 4A of [Makino and Sage (2007)](https://academic.oup.com/pcp/article/48/10/1472/1938331) which plots the change in activation state across temperatures for rice:\
\
![](Data/Makino_Sage_Fig_4-01.png)

To be able to extract this data, the points can be estimated manually using measuring tools or software such as [GraphReader](https://www.graphreader.com/), [PlotDigitizer](https://plotdigitizer.com/app) or [WebPlotDigitizer](https://automeris.io/).\
\
Define the data points:

```{r load data}
## Use manual estimates
# x <-c(16,20,25,32,37,41) # Temperature
# y <-c(85,85,80,73,69,48) # Activation state (%)

# Load data from .csv file compiled from automated tools

# These points are extracted using Plot Digitizer
#plot_data1 <- read.csv("Data/Fig_4A-plot-data.csv")
#x1 <- plot_data$x # Temperature
#y1 <- plot_data$y # Activation state (%)

# These points are extracted using Web Plot Digitizer
plot_data <- read.csv("Data/Fig_4A_plot_data_2.csv", header = FALSE)

# Convert activation state from percentage to decimal
plot_data$V2<- plot_data$V2/100

# Specify variables
x <- plot_data$V1 # Temperature
y <- plot_data$V2 # Activation state (%)

print(plot_data)
```

Plot the points, setting y-axis breaks at 20% intervals:

```{r plot data}
ggplot(plot_data, 
       aes(x, y)) +
       geom_line(color = "black", 
                 linewidth = 1) +
       geom_point(color = "black", 
                  fill = "black", 
                  shape = 21, 
                  size = 2) +
       scale_x_continuous(limits = c(10, 45)) +
       scale_y_continuous(limits = c(0, 1.2), 
                          breaks = seq(0.2, 1.2, by = 0.2)) +
       labs(x = "Leaf temperature (°C)", 
            y = "Rubisco activation (%)") +
       theme_minimal()
```

## Polynomial curve fitting

Try fitting the data to quadratic, cubic and quartic models:

```{r fit polynomials}
poly_model2 <- lm(y ~ poly(x, 
                           2, 
                           raw = TRUE),
                      data = plot_data)
poly_model3 <- lm(y ~ poly(x, 
                           3, 
                           raw = TRUE),
                      data = plot_data)
poly_model4 <- lm(y ~ poly(x, 
                           4, 
                           raw = TRUE),
                      data = plot_data)
```

## Evaluation of fitted models

Check the summary statistics for the three fits:

```{r summarise polynomial fit stats}
summary_quad <- summary(poly_model2)
summary_quad

summary_cubic <- summary(poly_model3)
summary_cubic

summary_quartic <- summary(poly_model4)
summary_quartic
```

The coefficients for the 4th-degree polynomial indicate a very steep model, which could cause values to escalate or drop rapidly, especially near the boundaries or beyond the range of the data. So this is not likely to be an appropriate model, especially for fitting only 6 data points.\
\
When comparing fit summaries of the quadratic and cubic models, the cubic model explains a higher percentage of the variability (96.16% vs. 93.73%).

The cubic model has a slightly lower RSE and slightly higher adjusted $R^{2}$ value, so it fits slightly better to the data than the quadratic as it includes an extra term - adding to complexity. On the other hand, the quadratic model doesn't explain as much variance, but it is penalised less for including fewer predictors. It is also better than the cubic model in terms of statistical significance (P-val sig \**.*\* for intercept and quadratic term in the quadratic model = significant at 10% level vs. none of the terms being significant for the cubic model).

Extract the fit coefficients for the quadratic and cubic models:

```{r extract polynomial coefficients}
coef_quad <- coef(poly_model2)
coef_quad
coef_cubic <- coef(poly_model3)
coef_cubic
```

Extract the residuals for the quadratic and cubic models:

```{r extract residuals}
residuals_quad <- residuals(poly_model2)
residuals_cubic <- residuals(poly_model3)
```

Save the polynomial functions including the model coefficients for the quadratic and cubic models:

```{r save polynomial functions}
quad_func <- function(x) coef_quad[1] + 
                          coef_quad[2] * x + 
                          coef_quad[3] * x^2
cubic_func <- function(x) coef_cubic[1] + 
                          coef_cubic[2] * x + 
                          coef_cubic[3] * x^2 + 
                          coef_cubic[4] * x^3
```

Obtain formulae for the polynomial functions:

```{r polynomial formulae}
quad_formula <- bquote(Quadratic: y == 
                       .(round(coef_quad[3], 4)) * x^2 + 
                       .(round(coef_quad[2], 3)) * x + 
                       .(round(coef_quad[1], 2)))

cubic_formula <- bquote(Cubic: y == 
                        .(round(coef_cubic[4], 5)) * x^3 + 
                        .(round(coef_cubic[3], 4)) * x^2 + 
                        .(round(coef_cubic[2], 3)) * x + 
                        .(round(coef_cubic[1], 2)))
quad_formula
cubic_formula
```

The `bquote` function ensures creation of the formulae with LaTeX formatting.

`.()` is used to evaluate the expressions and insert the coefficients dynamically into the formulae.

Plot the polynomial models on top of the data points using stat_function:

```{r plot polynomials}
ggplot(plot_data, 
       aes(x, y)) +
  geom_line(color = "black", 
            linewidth = 1) +
  geom_point(color = "black", 
             fill = "black", 
             shape = 21, 
             size = 2) +
  stat_function(fun = quad_func, 
                aes(color = "Quadratic"), 
                linewidth = 1, 
                linetype = "dashed",
                xlim = c(0, 45)) +  
  stat_function(fun = cubic_func, 
                aes(color = "Cubic"), 
                linewidth = 1, 
                linetype = "dashed",
                xlim = c(0, 45)) +  
  scale_x_continuous(limits = c(10, 45)) +
  scale_y_continuous(limits = c(0, 1.2), 
                     breaks = seq(0.2, 1.2, by = 0.2)) +
  labs(x = "Leaf temperature (°C)", 
       y = "Rubisco activation (%)",
       color = "Polynomial Fit") +
  theme_minimal() +
  scale_color_manual(
    values = c("Quadratic" = "red", 
               "Cubic" = "blue"),
    labels = c(quad_formula, 
               cubic_formula))
```

Obtain predictions using the polynomial models:

```{r predict with polynomial models}
y_pred_quad <- predict(poly_model2)
y_pred_cubic <- predict(poly_model3)
```

Plot the residuals against temperature for the quadratic model:

```{r plot quad residuals vs. temp}
ggplot(plot_data, 
       aes(x = x)) +
       geom_point(aes
                  (y = residuals_quad), 
                  color = "red") +
       geom_hline(yintercept = 0,
                  linetype = "dashed") +
       ggtitle("Residuals of Quadratic Model vs. Temperature") +
       xlab("Leaf temperature (°C)") +
       ylab("Residuals") +
       theme_minimal()
```

Plot the residuals against temperature for the cubic model:

```{r plot cubic residuals vs. temp}
ggplot(plot_data, 
       aes(x = x)) +
       geom_point(aes
                  (y = residuals_cubic), 
                  color = "blue") +
       geom_hline(yintercept = 0,
                  linetype = "dashed") +
       ggtitle("Residuals of Cubic Model vs. Temperature") +
       xlab("Leaf temperature (°C)") +
       ylab("Residuals") +
       theme_minimal()
```

Plot the residuals against fitted values for the quadratic model:

```{r plot quad residuals vs. fitted}
ggplot(plot_data, 
       aes(x = y_pred_quad)) +
       geom_point(aes
                  (y = residuals_quad), 
                  color = "red") +
       geom_hline(yintercept = 0,
                  linetype = "dashed") +
       ggtitle("Residuals of Quadratic Model vs. Fitted Values") +
       xlab("Fitted Values") +
       ylab("Residuals") +
       theme_minimal()
```

Plot the residuals against fitted values for the cubic model:

```{r plot cubic residuals vs. fitted}
ggplot(plot_data, 
       aes(x = y_pred_cubic)) +
       geom_point(aes
                  (y = residuals_cubic), 
                  color = "blue") +
       geom_hline(yintercept = 0,
                  linetype = "dashed") +
       ggtitle("Residuals of Cubic Model vs. Fitted Values") +
       xlab("Fitted Values") +
       ylab("Residuals") +
       theme_minimal()
```

There is no observable pattern in the scatter of residuals and they are close to the RSE values, which suggests the models are appropriate and have captured the underlying relationship between leaf temperature and activation state - even if some of the residual values are a bit higher, they are all \<10.

Compute MSE, RMSE and AIC for the models:

```{r compute mse and aic}
mse_quad <- mean((y - y_pred_quad)^2)
mse_quad
mse_cubic <- mean((y - y_pred_cubic)^2)
mse_cubic
rmse_quad <- sqrt(mean((y - y_pred_quad)^2))
rmse_quad
rmse_cubic <- sqrt(mean((y - y_pred_cubic)^2))
rmse_cubic
aic_quad <- AIC(poly_model2)
aic_quad
aic_cubic <- AIC(poly_model3)
aic_cubic
```

The cubic has a lower MSE and AIC but there is not that much difference between the two AIC values.

### 2025-04-10 Live_Scripts/R_version_Vmax_temp/Scripts/Vmax_temp.Rmd
Add files via upload

---
title: "Temperature-dependent adjustment of $V_{c}$ and $V_{o}$"
author: "Supreeta Vijayakumar"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load any libraries here
library(ggplot2)
library(minpack.lm)
```

# Bernacchi temperature functions

Currently the e-Photosynthesis model sets PrV111 = PsV1 \* 0.24, according to the known value for tobacco at 25°C (Whitney et al., 1999).\

However, this ratio varies across different crop species and temperatures.\
Seeing as there is no existing temperature functions for rice, we will use the equations by Bernacchi (2001) and values from Makino (1988) to compare the temperature responses of the parameters.

Specify constants:

```{r}
T25 <- 25 + 273.15                 # Reference temperature in K 
Tp <- 28.9310407291759 + 273.15    # Average measurement temperature in K
R <- 0.008314                     # Ideal gas constant in kJ K-1 mol-1
c_Vc <- 26.35                       # Scaling constant, Vcmax             (N. tabacum L. cv. W38, Bernacchi et al 2001)
dHa_Vc <- 65.33                    # Activation energy, Vcmax, kJ mol -1 (N. tabacum L. cv. W38, Bernacchi et al 2001)
c_Vo <- 22.98                       # Scaling constant, Vomax             (N. tabacum L. cv. W38, Bernacchi et al 2001)
dHa_Vo <-60.11                     # Activation energy, Vomax, kJ mol -1 (N. tabacum L. cv. W38, Bernacchi et al 2001)
```

Use the Arrhenius equation to calculate the $\frac {V_{o}} {V_c}$ ratio at 25°C for N.
tabacum (c and dHa from Bernacchi et al., 2001):\

$$Parameter = exp (c- \frac{\Delta H_{a}} {R \times T_{K}})$$\

```{r}
Bernacchi_Vc_25 <- exp(c_Vc - dHa_Vc / (R * T25))
Bernacchi_Vo_25 <- exp(c_Vo - dHa_Vo / (R * T25))
Bernacchi_PrPs_ratio_25 <- Bernacchi_Vo_25 / Bernacchi_Vc_25
print(Bernacchi_PrPs_ratio_25)
```

Calculate $\frac {V_{o}} {V_c}$ ratios across a range of temperatures (10-40°C) :

```{r}
Temp_Range <- data.frame(Temp_C = 10:40)                       # Temperatures in °C
Temp_Range$Temp_K <- Temp_Range$Temp_C + 273.15                # Temperatures in Kelvin
Temp_Range$Vc <- exp(c_Vc - dHa_Vc / (R * Temp_Range$Temp_K))  # Vc values
Temp_Range$Vo <- exp(c_Vo - dHa_Vo / (R * Temp_Range$Temp_K))  # Vo values
Temp_Range$Vo_Vc_ratio <- Temp_Range$Vo / Temp_Range$Vc        # Vo/Vc ratios
```

Plot $\frac {V_{o}} {V_c}$ data:

```{r}
ggplot(Temp_Range, aes(x = Temp_C, y = Vo_Vc_ratio)) +
                   geom_line(color = "blue") +
                   geom_point(color = "blue", size = 2) +
                   labs(x = expression("Temperature ("*degree*C*")"), y = "Vo/Vc") +
                   theme_minimal()
ggsave("Outputs/Temp_vs_VcVo.png")
```

Plot $V_{o}$:

```{r}
ggplot(Temp_Range, aes(x = Temp_C, y = Vo)) +
                   geom_line(color = "green") +
                   geom_point(color = "green", size = 2) +
                   labs(x = expression("Temperature ("*degree*C*")"), y = "Vo") +
                   theme_minimal()
ggsave("Outputs/Temp_vs_Vo.png")
```

Plot $V_{c}$:

```{r}
ggplot(Temp_Range, aes(x = Temp_C, y = Vc)) +
                   geom_line(color = "red") +
                   geom_point(color = "red", size = 2) +
                   labs(x = expression("Temperature ("*degree*C*")"), y = "Vc") +
                   theme_minimal()
ggsave("Outputs/Temp_vs_Vc.png")
```

Calculate Bernacchi values at measurement temperature:

```{r}
Bernacchi_Vc_Tp <- exp(c_Vc - dHa_Vc / (R * Tp))
Bernacchi_Vo_Tp <- exp(c_Vo - dHa_Vo / (R * Tp))
Bernacchi_PrPs_ratio_Tp <- Bernacchi_Vo_Tp / Bernacchi_Vc_Tp
print(Bernacchi_PrPs_ratio_Tp)
```

Calculate Makino values at 25°C:

```{r}
Makino_Vc_25 <- 1.77                                # Carboxylase activity (µmol (mg enzyme)⁻¹ min⁻¹)
Makino_Vo_25 <- 0.58                                # Oxygenase activity (µmol (mg enzyme)⁻¹ min⁻¹)
Makino_PrPs_ratio_25 <- Makino_Vo_25 / Makino_Vc_25 # Vo/Vc ratio
print(Makino_PrPs_ratio_25)
```

## Adjusting the value $V_{cmax}$ at 25°C to measurement temperature $T{p}$

We can use one of two approaches to calculate the Makino value of $\frac {V_{o}} {V_c}$ at Tp:

1)  Use the ratios of Makino and Bernacchi at 25°C and multiply by Bernacchi parameter estimate at a given temperature

2)  Fit an Arrhenius equation to a non-linear model to find the Bernacchi temperature response of (plotted above)

Use linear scaling of Makino to Bernacchi ratios:

```{r}
Makino_PrPs_ratio_Tp <- Makino_PrPs_ratio_25*Bernacchi_PrPs_ratio_Tp/Bernacchi_PrPs_ratio_25
print(Makino_PrPs_ratio_Tp)
```

## Non-linear fits for $\frac {V_{o}} {V_c}$

Define predictor and response variables:

```{r}
T <- Temp_Range$Temp_K      # Temperature in K
y <- Temp_Range$Vo_Vc_ratio # Vo/Vc ratio
```

So far, we have defined the Arrhenius equation as:

$$Parameter = exp (c- \frac{\Delta H_{a}} {R \times T_{K}})$$\

$c$ is meant to scale the amplitude of the function whereas $\Delta H_{a}$ represents the temperature dependence relationship.

Using the term $c−\Delta H_{a}$ combined these two effects into one, making them harder to interpret individually.
Without $c$, the model assumes that $\Delta H_{a}$ depends solely on temperature and ignores other potential variations.

This means the equation can also be rewritten as

$$y = c \times exp(-\frac{\Delta H_{a}} {R \times T_{K}})$$\

to ensure that the exponent has a negative sign - previously $exp(\frac{c- \Delta H_{a}} {R \times T_{K}})$ was causing errors since the exponent was positive.

Define an exponential model with non-linear parameters using this form of the Arrhenius equation.
Start by creating a fit type for a custom nonlinear model using nls():

```{r}
#nls_model <- nls(y ~ c_VoVc * exp(-dHa_VoVc / (R * T)), data = Temp_Range, start = list(c_VoVc = 0.3, dHa_VoVc = 60))
```

This is producing errors so use nlsLM() - which uses the Levenberg-Marquardt algorithm instead of the Gauss-Newton used by nls() for nonlinear least-squares estimation - for a more robust fitting process:

```{r}
nls_model <- nlsLM(Vo_Vc_ratio ~ c_VoVc * exp(-dHa_VoVc / (R * T)),
                                 data = Temp_Range,
                                 start = list(c_VoVc = 0, 
                                              dHa_VoVc = 2))
```

View the plot summary:

```{r}
summary(nls_model)
```

nlsLM() converged successfully so we can add the fitted values and new parameter estimates for c and dHa to Temp_Range dataframe:

```{r}
Temp_Range$fitted <- predict(nls_model)
```

Plot the non-linear fit of the model to the data:

```{r}
ggplot(Temp_Range, aes(x = Temp_K, y = Vo_Vc_ratio)) +
                   geom_point() +
                   geom_line(aes(y = fitted), color = "red") +
                   labs(x = "Temperature (K)", 
                        y = "Vo/Vc Ratio", 
                        title = "Non-linear Fit for Vo/Vc")
ggsave("Outputs/Temp_vs_VoVc_nlsLM.png")
```

Calculate the residuals by subtracting the fitted values from the observed responses:

```{r}
Temp_Range$nls_residuals <- Temp_Range$Vo_Vc_ratio - Temp_Range$fitted
```

Plot residuals against temperature:

```{r}
ggplot(Temp_Range, aes(x = Temp_K, y = nls_residuals)) +
                       geom_point() +
                       geom_hline(yintercept = 0, 
                                  linetype = "dashed", 
                                  color = "red") +
                       scale_y_continuous(limits = c(-8e-16, +8e-16)) +
                       labs(x = "Temperature (K)", 
                            y = "Residuals", 
                            title = "Non-Linear Residuals vs. Temperature")
ggsave("Outputs/nlsLM_residuals_temp.png")
```

Plot residuals against fitted values:

```{r}
ggplot(Temp_Range, aes(x = fitted, y = nls_residuals)) +
                       geom_point() +
                       geom_hline(yintercept = 0, 
                                  linetype = "dashed", 
                                  color = "red") +
                       scale_y_continuous(limits = c(-8e-16, +8e-16)) +
                       labs(x = "Fitted Values", 
                            y = "Residuals", 
                            title = "Non-Linear Residuals vs. Fitted Values")
ggsave("Outputs/nlsLM_residuals_fitted.png")
```

Random scatter around zero indicates we have a good fit of model to data.
The values of the residuals are also very small ($<8 \times 10^{-16}$), indicating the model accounts for all variations in the data and there are no unexplained residuals left.

Calculate R-squared:

```{r}
SST <- sum((Temp_Range$Vo_Vc_ratio - mean(Temp_Range$Vo_Vc_ratio))^2)     # Total sum of squares
SSR <- sum(Temp_Range$nls_residuals^2)                                    # Residual sum of squares
R_squared <- 1 - (SSR / SST)
print(R_squared)
```

The R-squared is exactly 1, which indicates all the data points lie on the fitted curve perfectly.
This is expected because the data points being fit are predictions from fitted models for $V_{c}$ and $V_{o}$ rather than actual data, so they have no associated measurement error.

However, R-squared is not always recommended for non-linear regression, because non-linear models do not usually have an intercept term and the total sum of squares is not necessarily equal to the sum of the regression sum of squares and the residual sum of squares.

Alternatively, we can calculate the mean squared error (MSE) or Akaike Information Criterion (AIC) instead:
```{r}
squared_residuals <- Temp_Range$nls_residuals^2

mse <- mean(squared_residuals)
print(mse)

nls_AIC <- AIC(nls_model)
print(nls_AIC)
```

The mse value is very low (\<$1\times10^{-31}$), indicating that the model’s predictions are very close to the data points.
Likewise, lower AIC values also indicate a better model with a good balance between fit and complexity.

Fit a linear model for comparison:
```{r}
linear_model <- lm(Vo_Vc_ratio ~ Temp_K, data = Temp_Range)
summary(linear_model)

linear_AIC <- AIC(linear_model)
print(linear_AIC)

Temp_Range$lin_fitted <- predict(linear_model)
```

Plot the linear fit of the model to the data:
```{r}
ggplot(Temp_Range, aes(x = Temp_K, y = Vo_Vc_ratio)) +
                   geom_point() +
                   geom_line(aes(y = lin_fitted), color = "red") +
                   labs(x = "Temperature (K)", 
                        y = "Vo/Vc Ratio", 
                        title = "Linear Fit for Vo/Vc")
ggsave("Outputs/Temp_vs_VoVc_linear.png")
```

The simpler linear model seems to perform almost as well as the more complex non-linear model, but does not predict correctly across the entire range. We can see that its AIC value is much higher, indicating a poorer predictive model.
However, in some cases it would be have been advantageous to simplify the model e.g. if we wanted to avoid overfitting.

Extract the nlsLM derived parameter coefficients:

```{r}
coefficients <- coef(nls_model)
c_VoVc <- as.numeric(coefficients["c_VoVc"])
dHa_VoVc <- as.numeric(coefficients["dHa_VoVc"])
```

Work out the conversion ratio between Bernacchi and Makino Vo/Vc ratios at 25°C:

```{r}
conv_ratio <- Makino_PrPs_ratio_25/Bernacchi_PrPs_ratio_25
```

Predict Vo/Vc value at Tp using the estimated parameters:

```{r}
Bernacchi_PrPs_ratio_Tp2 <- (c_VoVc * exp(-dHa_VoVc / (R * Tp)))
print(Bernacchi_PrPs_ratio_Tp2)
```

Correct for the conversion to Makino:

```{r}
Makino_PrPs_ratio_Tp2 <- Bernacchi_PrPs_ratio_Tp2*conv_ratio
print(Makino_PrPs_ratio_Tp2)
```

Compare the two values obtained for Makino ratios at Tp and print TRUE if they are equal:

```{r}
are_equal <- Makino_PrPs_ratio_Tp == Makino_PrPs_ratio_Tp2
print(are_equal)  
```

Although are_equal is FALSE, the Tp2 value is essentially the same (upto 15 dp) as the Tp value calculated using Method 1) multiplying the ratios of Makino and Bernacchi at 25°C by the Bernacchi parameter estimate at Tp.

### Normalization fitting method

We can also compare the values by re-scaling the $\frac {V_{o}} {V_c}$ ratio from Bernacchi so that it has a value of 1 at 25°C and then fitting the Arrhenius function using these values.

Divide all $\frac {V_{o}} {V_c}$ values calculated at different temperatures by the value at 25°C:

```{r}
normalized_ratios <- Temp_Range$Vo_Vc_ratio/Bernacchi_PrPs_ratio_25;
```

Obtain Arrhenius constants using the re-scaled values:

```{r}
nls_norm_model <- nlsLM(normalized_ratios ~ c_VoVc * exp(-dHa_VoVc / (R * T)),
                                            data = Temp_Range,
                                            start = list(c_VoVc = 0, 
                                                         dHa_VoVc = 2))
summary(nls_norm_model)
```

Extract the coefficients from this second model:

```{r}
norm_coefficients <- coef(nls_norm_model)
c_norm <- as.numeric(norm_coefficients["c_VoVc"])
dHa_norm <- as.numeric(norm_coefficients["dHa_VoVc"])
```

Predict the Bernacchi ratio at Tp using the parameters obtained from the non-linear fit of normalized values:

```{r}
Bernacchi_PrPs_ratio_Tp3 <- (c_norm * exp(-dHa_norm / (R * Tp)))
print(Bernacchi_PrPs_ratio_Tp3)
```

This ratio is different from the other two ratios since we re-scaled the values and obtained a new parameter estimate for $c$.

Multiply the Bernacchi ratio at Tp by the Makino ratio at 25°C:

```{r}
Makino_PrPs_ratio_Tp3 <- Makino_PrPs_ratio_25*Bernacchi_PrPs_ratio_Tp3
print(Makino_PrPs_ratio_Tp3)
```

Compare the third value obtained for Makino ratios to the first two and print TRUE if equal:

```{r}
are_equal <- (Makino_PrPs_ratio_Tp == Makino_PrPs_ratio_Tp3) | 
             (Makino_PrPs_ratio_Tp2 == Makino_PrPs_ratio_Tp3)

print(are_equal) 
```

### 2025-04-10 Plotting/extract_PR_constraints.m
Updated plotting commands

@@ -1,0 +1,36 @@
+% Read in all 129 optimization results, average the results and export PR
+% enzyme Vmax values to PR_constraints to serve as constraints for full optimizations
+
+% Define the folder containing the Excel files
+folder_129 = 'Outputs\rice_params\enzymes\129\';
+
+% Get the list of text files containing enzyme Vmax of optimizations at 129 ppm
+optimized_129_list = dir(fullfile(folder_129, '*.txt')); % get all text files in that folder
+
+% Initialize an empty cell array to store the matrices
+optimized_129_matrices = cell(numel(optimized_129_list), 1);
+
+% Loop over the files
+for i = 1:numel(optimized_129_list)
+    % Read the current file using readmatrix
+    optimized_129_matrix = readmatrix(fullfile(folder_129, optimized_129_list(i).name));
+    
+    % Store the matrix in the cell array
+    optimized_129_matrices{i} = optimized_129_matrix;
+end
+
+% Combine all cells in the array 
+combined_129_matrix = horzcat(optimized_129_matrices{:,1});
+blank_rows = zeros(1,10);
+combined_129_matrix_new = vertcat(combined_129_matrix(2:8,:), ...
+    blank_rows,combined_129_matrix(9,:),blank_rows,combined_129_matrix(10:11,:),blank_rows,combined_129_matrix(12:25,:));
+
+% Average across the columns for each enzyme Vmax
+avg_optimized_129 = mean(combined_129_matrix,2);
+
+% Extract rows for photorespiratory constraints and save in text file
+PR_constraints = avg_optimized_129(12:18);
+writematrix(PR_constraints,'PR_constraints.txt');
+
+% Update results in file
+% writematrix(combined_129_matrix_new,'Outputs/rice_params/Results_optimization_rice_new_2.xlsx','Sheet','129','Range','K4')

### 2025-04-10 Plotting/extract_optimization_results.m

@@ -1,0 +1,33 @@
+% Read in optimization results for each Cc (130-380) and average the results 
+
+% One Cc at a time-
+% Define the folder containing the Excel files
+folder_130 = 'Outputs\rice_params\enzymes\130\';
+
+% Get the list of text files containing enzyme Vmax of optimizations at 130 ppm
+optimized_130_list = dir(fullfile(folder_130, '*.txt')); % get all text files in that folder
+
+% Initialize an empty cell array to store the matrices
+optimized_130_matrices = cell(numel(optimized_130_list), 1);
+
+% Loop over the files
+for i = 1:numel(optimized_130_list)
+    % Read the current file using readmatrix
+    optimized_130_matrix = readmatrix(fullfile(folder_130, optimized_130_list(i).name));
+    
+    % Store the matrix in the cell array
+    optimized_130_matrices{i} = optimized_130_matrix;
+end
+
+% Combine all cells in the array 
+combined_130_matrix = horzcat(optimized_130_matrices{:,1});
+blank_rows = zeros(1,10);
+combined_130_matrix_new = vertcat(combined_130_matrix(2:8,:), ...
+    blank_rows,combined_130_matrix(9,:),blank_rows,combined_130_matrix(10:11,:),blank_rows,combined_130_matrix(12:25,:));
+% Average across the columns for each enzyme Vmax
+avg_optimized_130 = mean(combined_130_matrix_new,2);
+
+% Update results in file
+writematrix(combined_130_matrix_new,'Results_optimization_rice_new_2.xlsx','Sheet','130','Range','I4')
+
+

### 2025-04-10 Plotting/import_optimization_results.m

@@ -1,0 +1,43 @@
+% This script imports data for non-optimized vs optimized enzyme concentrations in a loop
+
+% Import data from excel file containing results of e-Photosynthesis optimization using rice data 
+file = 'Outputs/rice_params/Results_optimization_rice_new_2.xlsx';
+
+% Define range to import data from
+non_optimized_range = 'AI5:AI30'; %
+optimized_range = 'V5:X30'; %import averages, STDEV and SEM
+
+% Define sheet names to import data from
+sheet_names = string(num2cell(130:10:380)); % if there are regular intervals between values
+
+% Create cell array to import non-optimized and optimized protein data from each Cc on a different sheet
+results_data = cell(2, numel(sheet_names));
+
+% Loop through all sheets and import values into results_data
+for i = 1:numel(sheet_names)
+    % Read the specified range as a numeric array
+    numeric_data_non_optimized = readmatrix(file, 'Sheet', sheet_names{i}, 'Range', non_optimized_range);
+    %numeric_data_optimized = readmatrix(file, 'Sheet', '140', 'Range', 'AI5:AI30');
+    numeric_data_optimized = readmatrix(file, 'Sheet', sheet_names{i}, 'Range', optimized_range);
+    % Replace zero values with NaN
+    numeric_data_non_optimized(numeric_data_optimized == 0) = NaN;
+    numeric_data_optimized(numeric_data_optimized == 0) = NaN;
+    % Remove rows containing all NaN values
+    rows_to_keep = any(~isnan(numeric_data_optimized), 2);
+    numeric_data_optimized = numeric_data_optimized(rows_to_keep, :);
+    numeric_data_non_optimized = numeric_data_non_optimized(rows_to_keep, :);
+    % Store data in cell array using sheet names as indices (1-26 = 130-380)
+    results_data{1,i} = numeric_data_non_optimized;
+    results_data{2,i} = numeric_data_optimized;
+end
+
+% Get enzyme names 
+cats = readcell(file, 'Sheet', '130', 'Range', 'C5:C30'); % Read enzyme names
+cats = categorical(cats(rows_to_keep, :)); % Remove duplicate enzymes and convert into categorical
+
+% Get PR constraints from optimizations at 129 ppm
+% PR_constraints_protein = PR_constraints;
+% Get protein constraints
[…]

### 2025-04-10 Plotting/plot_A_Cc_new.m

@@ -1,18 +1,18 @@
 %% Plotting Cc vs A for FvCB and e-Photosynthesis models (combined graph)
 % Use intersection points to get ranges to plot gross A for each limitation
-load('Farq_ePhoto_results_new2.mat') % result of running Farq_ePhoto_comparison but with new alpha values
+load('Farq_ePhoto_results_new.mat') % result of running Farq_ePhoto_comparison but with new alpha values
 figure
 for j = 1:numel(Net_Ac)
     if     Net_Ac(j) < Net_Aj(j)   
-           p = scatter(Cc_Ac(j),Gross_Ac(j),20,'filled', MarkerFaceColor="#D95319");
+           p = scatter(Cc_Ac(j),Gross_Ac(j),100, MarkerFaceColor="#FFFFFF", MarkerEdgeColor ='black',LineWidth = 1.0);           
            %p.Color = "#D95319";
     elseif Net_Aj(j) < Net_Ap(j)
            hold on
-           q = scatter(Cc_Aj(j),Gross_Aj(j),20,'filled', MarkerFaceColor="#0072BD");
+           q = scatter(Cc_Aj(j),Gross_Aj(j),100, MarkerFaceColor="#0D1793",MarkerEdgeColor='none'); 
            %q.Color = "#0072BD";
     else   
            hold on
-           r=scatter(Cc_Ap(j),Gross_Ap(j),20,'filled', MarkerFaceColor="#EDB120");
+           r = scatter(Cc_Ap(j),Gross_Ap(j),100,'square', MarkerFaceColor="#EDB120",MarkerEdgeColor='none');
            %r.Color = "#EDB120";
     end
 end
@@ -21,33 +21,30 @@ hold on
 
 % Plot Cc (x) against Gross Assimilation (y) for alpha values=1 (black dashed lines)
 nonopt_plot = plot(Cc_ePhoto, Gross_A_nonopt, ...
-            '-x', ...
-            'Color', 'k');
-            %'MarkerFaceColor', 'k', ... % k=black markers and line
-            %'MarkerEdgeColor', 'k', ...
-            %'MarkerSize', 6, ...
-            %'DisplayName', 'ePhotosynthesis (α_Enzymes = 1, α_Rubisco = 1)');
-
+            '--', ...
[…]

### 2025-04-10 Plotting/plot_violins_new.m

@@ -1,7 +1,7 @@
 % Produce violin plots for enzyme sensitivity analysis using the violinplot
 % function from cobratoolbox (https://github.com/opencobra/cobratoolbox/blob/master/external/base/utilities/violinPlots/violinplot.m)
-%% Load data
-load output_enzyme_adjustment_test_2000_5_new.mat; % Load results from 2000 node test simulation
+%% Load results from 2000 node test simulation
+load output_enzyme_adjustment_test_2000_5_new.mat; 
 %% Create outputs for increases in gross CO2 assimilation rate
 [IncreaseInGrossAssimilationRate_RS_130,...%two
  IncreaseInGrossAssimilationRate_RS_250,...%two
@@ -110,8 +110,15 @@ CO2_data_percent = horzcat(PercentChangeGrossAssimilationRate_RS_130,...
                    PercentChangeGrossAssimilationRate_RSAPFT_250,...
                    PercentChangeGrossAssimilationRate_RSAPFT_360);
 % Find mean, min and max of percentages
+mean_CO2_uptake = mean(CO2_data);
+min_max_CO2_uptake = vertcat(min(CO2_data),max(CO2_data));
+range_CO2_uptake = range(CO2_data);
 mean_percents = mean(CO2_data_percent);
 min_max_percents = vertcat(min(CO2_data_percent),max(CO2_data_percent));
+% Find percentages of outcomes that were negative for current and future
+% strategies at Cc = 360
+percent_negative_360_current = nnz(CO2_data(:,6)<0)/2000*100;
+percent_negative_360_future = nnz(CO2_data(:,9)<0)/2000*100;
 %% Create the violin plot for the different enzyme combinations
 % Set colors with triplet codes
 violinColors_Stress = [0.9529 0.4588 0.5059; %Red
@@ -131,11 +138,12 @@ groupLabels = {'130', '250', '360'};
 %% STRESS
 figure;
 for i = 1:3
-    Violin(CO2_data(:, (i-1)*3+1), i, 'ViolinColor', violinColors_Stress(i, :), 'ShowMean', true, 'ShowData', false);
[…]

### 2025-04-10 Plotting/plotting_A_rates.m

@@ -1,4 +1,4 @@
-% Plot assimilation rates for rice data, possibly also compare to potato
+% Plot assimilation rates for rice data
 
 % Import assimilation rates from results file
 file = 'Outputs/rice_params/Results_optimization_rice_new_2.xlsx';
@@ -15,7 +15,6 @@ twofold_ambient = num2cell(readmatrix('ambient2_A.txt'));
 twofold_elevated = num2cell(readmatrix('elevated2_A.txt'));
 
 % Create cell array to import average assimilation rates from each Ci/sheet
-%assimilation_data = cell(4, numel(sheet_names));
 reoptimized_assimilation_data = cell(8, numel(sheet_names));%non opt, opt and three strategies (2/4/6 optimized enzymes) and three strategies with twofold increases in Vmax
 %reoptimized_assimilation_data = cell(2, numel(sheet_names)); % only non opt and opt A
 
@@ -46,47 +45,48 @@ percent_change_elevated2=vertcat(sheet_names,(cell2mat(reoptimized_assimilation_
 figure;
 % Plot scatter graph of Cc (x) against average assimilation rates
 % Plot non-optimized A
-scatter(Cc, cell2mat(reoptimized_assimilation_data(1,:)),100,'black','filled','o'); 
+p1 = scatter(Cc, cell2mat(reoptimized_assimilation_data(1,:)),100,'black','filled','o','MarkerEdgeColor','black','LineWidth',0.5); 
+p1.DisplayName = 'Non-Optimised';
 hold on
 % Plot optimized A averages
-scatter(Cc, cell2mat(reoptimized_assimilation_data(2,:)),100,'green','filled','^');
+p2 = scatter(Cc, cell2mat(reoptimized_assimilation_data(2,:)),100,'white','filled','^','MarkerEdgeColor','black','LineWidth',0.5);
+p2.DisplayName = 'Optimised';
 hold on
 % Plot non-optimized A with optimized A averages for Aldolase, SBPase, PRK at 250
-scatter(Cc, cell2mat(reoptimized_assimilation_data(4,:)),100,'magenta','filled','square');
+p4 = scatter(Cc, cell2mat(reoptimized_assimilation_data(4,:)),100,'magenta','filled','square');
[…]

### 2025-04-10 Plotting/plotting_scatter_averages_new.m

@@ -60,36 +60,38 @@ for j = 1:length(y{1,i}(:,2)) % For all enzymes
 end
 
 % Create CBB panel
-    figure('Position', [100, 100, 300, 1200]); % [left, bottom, width, height];
-    tiledlayout(4,2, 'TileSpacing', 'compact', 'Padding', 'compact','TileIndexing', 'columnmajor');
-    %tiledlayout(8,1,'TileSpacing', 'compact', 'Padding', 'compact','TileIndexing', 'columnmajor')
-    % Plot scatter graphs of Cc (x) against absolute protein concentrations of individual enzymes 
-    for j = 1:length(CBB_indices) % For each enzyme j 
+figure('Position', [100, 100, 300, 1200]); % [left, bottom, width, height];
+tiledlayout(4,2, 'TileSpacing', 'compact', 'Padding', 'compact','TileIndexing', 'columnmajor');
+% Create scatter plots with dummy data for legend
+h1 = scatter(nan, nan, 'black', 'filled', 'o', 'MarkerEdgeColor', 'black', 'LineWidth', 0.5); % Non-optimised
+hold on
+h2 = scatter(nan, nan, 'white', 'filled', '^', 'MarkerEdgeColor', 'black', 'LineWidth', 0.5); % Optimised
+hold off   
+% Plot scatter graphs of Cc (x) against absolute protein concentrations of individual enzymes 
+for j = 1:length(CBB_indices) % For each enzyme j 
         CBB_index = CBB_indices(j);
-        nexttile
+        nexttile;
         %semilogy(Cc, enzyme_nopt_concs(CBB_index,:), '.', 'MarkerSize', 15);
-        scatter(Cc, enzyme_nopt_concs(CBB_index,:),'black','filled','o'); % Plot non-optimized series
+        h1 = scatter(Cc, enzyme_nopt_concs(CBB_index,:),50,'black','filled','o','MarkerEdgeColor','black','LineWidth',0.5); % Plot non-optimized series
         hold on
         %semilogy(Cc, all_opt_concs(CBB_index,:), '^', 'MarkerSize', 15);
-        scatter(Cc, all_opt_concs(CBB_index,:),'green','filled','^'); % Plot optimized series
+        h2 = scatter(Cc, all_opt_concs(CBB_index,:),50,'white','filled','^','MarkerEdgeColor','black','LineWidth',0.5); % Plot optimized series
         hold off
         % Cc x axis limits
[…]

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_130.sh
Updated shell scripts

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_129
+#SBATCH -J job_array_gpmain_rice_130
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_129_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_130_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_140.sh

@@ -3,7 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_140
-#SBATCH -a 1-10
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_150.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_150
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_150_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_160.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_160
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_170.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_170
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_170_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_180.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_180
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_190.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_190
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_190_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_200.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_200
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_210.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_210
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_210_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_230.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_230
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_230_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_240.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_240
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_250.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_250
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_250_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_260.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_260
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_270.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_270
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_270_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_280.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_280
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_290.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_290
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_290_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_300.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_300
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_310.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_310
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_310_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_320.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_320
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_330.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_330
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_330_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_340.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_340
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_350.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_350
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_350_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_360.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_360
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_370.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_370
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_370_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_380.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_380
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_400.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_400
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_420.sh

@@ -3,6 +3,7 @@
 #SBATCH -p serial
 #SBATCH --mem=8g
 #SBATCH -J job_array_gpmain_rice_420
+#SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a

### 2025-04-10 Shell_Scripts/Arrays/job_array_gpmain_rice_600.sh

@@ -2,12 +2,12 @@
 
 #SBATCH -p serial
 #SBATCH --mem=8g
-#SBATCH -J job_array_gpmain_rice_220
+#SBATCH -J job_array_gpmain_rice_600
 #SBATCH -a 1-15
 
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "gpmain_rice_220_new;quit"
+matlab -nodisplay -nodesktop -r "gpmain_rice_600_new;quit"
 
 echo This is job task ${SLURM_ARRAY_TASK_ID} running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Single_Scripts/job_Farq_ePhoto.sh
Updated shell scripts

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+#SBATCH -p serial
+#SBATCH --mem=5g
+#SBATCH -J job_Farq_ePhoto
+
+source /etc/profile
+module add matlab/2022a
+
+matlab -nodisplay -nodesktop -r "Farq_ePhoto_compariosn;quit"
+
+echo Job running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Single_Scripts/job_enzyme_adjustment_test_new.sh

@@ -1,0 +1,12 @@
+#!/bin/bash
+
+#SBATCH -p serial
+#SBATCH --mem=8g
+#SBATCH -J job_enzyme_adjustment_test_new_2000_4
+
+source /etc/profile
+module add matlab/2022a
+
+matlab -nodisplay -nodesktop -r "enzyme_adjustment_test_new_2000_4;quit"
+
+echo Job running on compute node `uname -n`

### 2025-04-10 Shell_Scripts/Single_Scripts/job_Farq_ePhoto.sh
Update job_Farq_ePhoto.sh

@@ -7,6 +7,6 @@
 source /etc/profile
 module add matlab/2022a
 
-matlab -nodisplay -nodesktop -r "Farq_ePhoto_compariosn;quit"
+matlab -nodisplay -nodesktop -r "Farq_ePhoto_comparison;quit"
 
 echo Job running on compute node `uname -n`

### 2025-04-10 gpmain/gpmain_rice_129_new.m
Add files via upload

@@ -18,25 +18,23 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_129_new(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
-Ci=129;% adj 200,220,240 or 260
-CO2i=Ci;% adj 200,220,240 or 260 %CO2i=Ci if input given to function
-%PPFDi=1500; %PPFD from Acevedo-Siaca
-PPFDi=2000; %PPFD from IRRI
-WeatherTemp=28.9310407291759;
-GRNC=0;
-Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
-Eio=Edata.data(:,1);
-Eio(1)=Edata.data(1,1)*Vrubusco_adj;
-Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
-Enzyme=importdata('MW&Kcat.txt');
-MWKcat=Enzyme.data;
+CO2i = 129;% adj 200,220,240 or 260 %CO2i=Ci if input given to function
+PPFDi = 2000; %PPFD from IRRI
+WeatherTemp = 28.9310407291759;
+GRNC = 0;
+Einput = ones(37,1);%No gene expression data input
+Edata = importdata('Einput7.txt');
+Eio = Edata.data(:,1);
+Eio(1) = Edata.data(1,1)*Vrubusco_adj;
+Eio(2:26) = Edata.data(2:26,1)*VmaxAdj;
+Enzyme = importdata('MW&Kcat.txt');
+MWKcat = Enzyme.data;
 MWKcat([7,9,12],:) = []; %remove rows corresponding to V8, V10 and V16
 %%%%%%%%%%%%%%%%%%% Initialize Variables %%%%%%%%%%%%%%%%%%%
 global pcfactor; 
@@ -89,17 +87,17 @@ end
 %%%% Initialize BK and MW Array %%%%
 
 global BK;
-BK=MWKcat(:,2);
+BK = MWKcat(:,2);
 %BK([7,9,12],:) = [];
[…]

### 2025-04-10 gpmain/gpmain_rice_130_new.m

@@ -24,8 +24,7 @@ Vrubusco_adj = 1.32;
 global VmaxAdj;
 VmaxAdj = 1.12;
 
-%Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=130;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
@@ -100,7 +99,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -272,7 +271,7 @@ PR_constraints = importdata('PR_constraints.txt');
 	    if rem(i/100,1)==0
         i
         Ci_str = num2str(CO2i);
-        task_id=getenv('SLURM_ARRAY_TASK_ID');
+		task_id=getenv('SLURM_ARRAY_TASK_ID');
         % Specify unique filenames for each Ci
         workspacefileName = strcat ("CO2_rice_",Ci_str,"_",task_id,".mat");
         % Save the work space 

### 2025-04-10 gpmain/gpmain_rice_140_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=140;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_150_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=150;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end

### 2025-04-10 gpmain/gpmain_rice_160_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=160;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_170_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=170;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_180_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=180;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_190_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=190;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_200_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=200;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_210_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=210;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_220_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=220;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_230_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=230;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_240_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=240;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_250_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=250;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_260_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=260;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_270_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=270;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_280_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=280;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_290_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=290;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_300_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=300;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_310_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=310;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_320_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=320;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_330_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=330;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_340_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=340;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_350_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=350;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_360_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=360;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_370_new.m

@@ -25,7 +25,7 @@ global VmaxAdj;
 VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=380;% Ci given as input to function
+CO2i=370;% Ci given as input to function
 PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;

### 2025-04-10 gpmain/gpmain_rice_400_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=400;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_420_new.m

@@ -18,10 +18,11 @@
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %function gpmain_rice_all(Ci)
+%Adjust alpha values here and read in Einput7.txt
 global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
+Vrubusco_adj = 1.32; 
+global VmaxAdj;
+VmaxAdj = 1.12;
 
 %Ci=__;% Adjust Ci= 140-420 here in script or
 CO2i=420;% Ci given as input to function
@@ -29,8 +30,7 @@ PPFDi=2000;
 WeatherTemp=28.9310407291759;
 GRNC=0;
 Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
+Edata=importdata('Einput7.txt');
 Eio=Edata.data(:,1);
 Eio(1)=Edata.data(1,1)*Vrubusco_adj;
 Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
@@ -100,7 +100,7 @@ MW=MWKcat(:,3);
 sumd = 0;
 for k = 1:VmaxNum
     if k == 1
-    sumd= sumd + (1.2*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80%
+    sumd= sumd + (1.1*pop(k+2,1))/BK(k)*MW(k); % For Rubisco, adjust activity to 80% - 10% inhibition
     else
     sumd= sumd + pop(k+2,1)/BK(k)*MW(k);
     end
@@ -142,8 +142,8 @@ for i = 1:numofGen
 %     Lapse = clock-TimeBegin
 
 % Load constraints for photorespiratory enzymes (= average of values calculated during enzyme adjustment running at 129 ppm)
-PR_constraints_data=importdata('PR_constraints.txt');    
-PR_constraints=PR_constraints_data.data(:,1);
+PR_constraints = importdata('PR_constraints.txt');    
+%PR_constraints=PR_constraints_data.data(:,1);
 
     for j = 1:popSize
 %         gp2condition_RuCon = pop(3,j)/2;

### 2025-04-10 gpmain/gpmain_rice_new.m
Delete gpmain/gpmain_rice_new.m

@@ -1,287 +1,0 @@
-%   Copyright   Xin-Guang Zhu and Stephen P. Long, University of Illinois 
-%   Copyright ©  2007
-
-%   This file is part of CarbonMetabolism.
-
-%    CarbonMetabolism is free software; you can redistribute it and/or modify
-%    it under the terms of the GNU General Public License as published by
-%    the Free Software Foundation; either version 3 of the License, or
-%    (at your option) any later version.
-
-%    CarbonMetabolism is distributed in the hope that it will be useful,
-%    but WITHOUT ANY WARRANTY; without even the implied warranty of
-%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-%    GNU General Public License for more details.
-
-%    You should have received a copy of the GNU General Public License (GPL)
-%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-function gpmain_rice_new(Ci)
-global Vrubusco_adj;
-Vrubusco_adj=1.0; %keep as 1.0 after fixed optimization
-global VmaxAdj;%
-VmaxAdj=1.0;
-
-%Ci=__;% Adjust Ci= 140-420 here in script or
-CO2i=Ci;% Ci given as input to function
-PPFDi=2000;
-WeatherTemp=28.9310407291759;
-GRNC=0;
-Einput=ones(37,1);%No gene expression data input
-%Edata=importdata('Einput7.txt');
-Edata=importdata('Einput_rice.txt');
-Eio=Edata.data(:,1);
-Eio(1)=Edata.data(1,1)*Vrubusco_adj;
-Eio(2:26)=Edata.data(2:26,1)*VmaxAdj;
-Enzyme=importdata('MW&Kcat.txt');
-MWKcat=Enzyme.data;
-MWKcat([7,9,12],:) = []; %remove rows corresponding to V8, V10 and V16
-%%%%%%%%%%%%%%%%%%% Initialize Variables %%%%%%%%%%%%%%%%%%%
-global pcfactor; 
-pcfactor=1;
-global VmaxNum;
-%global NConc; 
-% IntContinue = 0;        % This is a flag to indicate whether we need to use the external data or not for the initialization. Default is 0.
-% WriteExcel = 0;
-
-% The following variables are used to output data from the simulation. 
-
[…]

### 2025-04-29 ComputeEnergyBalance.m
Delete ComputeEnergyBalance.m

@@ -1,76 +1,0 @@
-%Compute energy balance
-function CalLeafTemperature=ComputeEnergyBalance(Gb,Gs,NetAssimilation,LeafTemperature,RH,WeatherTemperature,Pressure,Boltzman,ConstantsCp,LatentHeatVaporization,Radiation_PAR,Radiation_NIR,Radiation_LW)
-
-%ComputeEnergyBalance(10,10,25,26,0.6,28,101325.0,5.6697E-8,29.3,44000.0,200,0,0)
-% Temporary variables
- MaximumLeafTemperature=80;
- Epsilon = 0.96;% Leaf thermal emissivity
- G = Gb * Gs / (Gb+Gs); % moles/m2 leaf area/s
- ESaturation = 0.0; Ea = 0.0; %Vapor pressure KPa
- LEFactor = 1.0; %%%%1.0%%%%%
- LWFactor = 2.0; 
- HFactor = 2.0;%%%%%GGGGGGGG
- EnergyBalanceResidual = 0.0;
- LeafEnergyFluxMe = 0.506 * NetAssimilation; %Energy in biochemical reactions W/m2
- ESaturation = 0.611 * exp(17.502 * LeafTemperature / (LeafTemperature + 240.97));%KPa
- Ea = RH * ESaturation;%KPa
- 
-     if Radiation_LW == 0
-     Radiation_LW = LWFactor * Epsilon * Boltzman *(273.15 + WeatherTemperature) ^4;
-     end
-
-
- CoefficientESaturation(1)=5.82436 / 10000.0 / 1000.0; % pow(LeafTemperature,4) KPa
- CoefficientESaturation(2)=1.5842 / 100.0 / 1000; %pow(LeafTemperature,3) KPa
- CoefficientESaturation(3)=1.55186 / 1000.0; %pow(LeafTemperature,2) KPa
- CoefficientESaturation(4)=44.513596 / 1000.0; %pow(LeafTemperature,1) KPa
- CoefficientESaturation(5)=607.919 / 1000.0; %pow(LeafTemperature,0) KPa
-
- CoefficientTemperature(1) = LEFactor * G * LatentHeatVaporization / (Pressure / 1000.0)*CoefficientESaturation(1) + LWFactor * Epsilon * Boltzman; %pow(LeafTemperature,4)
[…]

### 2025-04-29 ComputeBoundaryLayerConductance.m
Delete ComputeBoundaryLayerConductance.m

@@ -1,35 +1,0 @@
-function BoundaryCound=ComputeBoundaryLayerConductance(WeatherTemperature,LeafTemperature,WeatherRH,WeatherWind,Pressure,LeafGs,NetAssimilation, Air_CO2)
-
-%ComputeBoundaryLayerConductance(28,26,0.6,1,101325.0,0.01,20,380)
-%Temporary variable
- ESaturation = 0.0; Ei = 0.0; Ea = 0.0; % Vapor pressure Pa
- LeafDimension = 0.06; %Leaf width/needle diameter m
- CForced = 4.322 / 1000.0; 
- CFree = 1.6361 / 1000.0;
- TemperatureKelvin = WeatherTemperature + 273.15;% Air temperature K
- LeafTemperatureKelvin = LeafTemperature + 273.15;%Leaf temperature K
- ESaturation = 0.611 * exp(17.502 * LeafTemperature / (LeafTemperature + 240.97)) * 1000.0;%Vapor pressure Pa
- Ei = ESaturation; %Vapor pressure Pa
- Ea = WeatherRH * ESaturation; %Vapor pressure Pa
-
- %Forced convection
- GbForced = CForced * TemperatureKelvin^0.56 * sqrt((TemperatureKelvin + 120.0)* (WeatherWind / LeafDimension / Pressure)); %// m/s
-
- %Free convection
- GbFree = GbForced;% m/s
- Eb = (LeafGs / 41.1 * Ei + GbFree * Ea) / (LeafGs / 41.1 + GbFree); % Stomatal conductance from moles/m2 leaf area/s to m/s
- TDifference = (LeafTemperatureKelvin / (1.0 - 0.378 * Eb /Pressure)) -(TemperatureKelvin / (1.0 - 0.378 * Ea / Pressure));
- GbFree = CFree * LeafTemperatureKelvin^0.56 * sqrt((LeafTemperatureKelvin + 120.0) /Pressure) * (abs(TDifference) / LeafDimension)^0.25;% m/s
-
-% Maximum of two conductances
- if GbFree >= GbForced
-     Gb = GbFree;
- else
-     Gb = GbForced; % m/s
- end
- Gb = Gb * 41.4; %Conversion from m/s to moles/m2 leaf area/s
- Cb = Air_CO2 - 1.37 * NetAssimilation / Gb; % ppm
- BoundaryCound(1)=Gb;
- BoundaryCound(2)=Cb;
- BoundaryCound(3)=Eb;
-end

### 2025-04-29 CalAMatrix.m
Delete CalAMatrix.m

@@ -1,155 +1,0 @@
-%clear all;
-    Edata=importdata('Einput7.txt');
-    Eio=Edata.data(:,1);
-    PPFDi=2000*0.85*0.85;
-    %Tempi=25;
-    global pcfactor;
-    pcfactor=1.025;
-    
-for i=1:15 %Temp
-    i
-    Tempi=20+i;
-    for j=1:120   %Ci
-        j
-        CO2i=j*10;
-    Ao(i,j,PPFDi)=EPS_Drive_GRNs('MeM_input5_0.txt',CO2i,PPFDi,Tempi,0,0,Eio);
-    Ag(i,j,PPFDi)=EPS_Drive_GRNs('MeM_input5_0.txt',CO2i,PPFDi,Tempi,1,0,Eio);
-
-    end
-    save AmatrixVc120_3P1.mat;
-end
-
-clear all;
- Edata=importdata('Einput7vc100.txt');
- Eio=Edata.data(:,1);
- PPFDi=2000*0.85*0.85;
- 
- global pcfactor;
- pcfactor=1.025;
-    
- 
- for i=1:15 %Temp
-    i
-    Tempi=20+i;
-    for j=1:120   %Ci
-        j
-        CO2i=j*10;
-    Ao(i,j,PPFDi)=EPS_Drive_GRNs('MeM_input5_0.txt',CO2i,PPFDi,Tempi,0,0,Eio);
-    Ag(i,j,PPFDi)=EPS_Drive_GRNs('MeM_input5_0.txt',CO2i,PPFDi,Tempi,1,0,Eio);
-
-    end
-    save AmatrixVc100_3P1.mat;
-end
-    Edata=importdata('Einput7.txt');
-    Eio=Edata.data(:,1);
-    PPFDi=2000*0.85*0.85;
-    %Tempi=25;
-    global pcfactor;
-    pcfactor=1.056;
-    
-for i=1:15 %Temp
-    i
-    Tempi=20+i;
-    for j=1:120   %Ci
-        j
-        CO2i=j*10;
-    Ao(i,j,PPFDi)=EPS_Drive_GRNs('MeM_input5_0.txt',CO2i,PPFDi,Tempi,0,0,Eio);
-    Ag(i,j,PPFDi)=EPS_Drive_GRNs('MeM_input5_0.txt',CO2i,PPFDi,Tempi,1,0,Eio);
-
-    end
[…]

### 2025-04-29 ComputGsBallBerry.m
Delete ComputGsBallBerry.m

@@ -1,23 +1,0 @@
-function CalGs=ComputGsBallBerry(BallBerryIntercept,BallBerrySlope,WaterStressFactor,Eb,Cb,Gb,NetAssimilation,LeafTemp,Air_CO2)
-%ComputGsBallBerry(0.008,10.5,1.0,1000,10,345,25,25,370)
-%%Saturated water vapor pressure
-ESaturation=0.611 * exp(17.502 * LeafTemp/ (LeafTemp+240.97)) * 1000.0;
-
-%%Update stomatal conductance moles/m2 leaf area/s
-Gs = BallBerryIntercept + BallBerrySlope*NetAssimilation * Eb / ESaturation/Cb;
-Gs = Gs * WaterStressFactor; %Apply water stress factor
-
-%     if (LeafState->Gs < Photosynthesis->BallBerryIntercept || Photosynthesis->CO2 < LeafState->GammaStar)
-%     {
-%         LeafState->Gs = Photosynthesis->BallBerryIntercept;
-%     }
-
-%% Update Ci
-Ci = Air_CO2 - 1.37 * NetAssimilation / Gb - 1.6 * NetAssimilation / Gs; % Update leaf internal CO2 concentration ppm
-%     if (LeafState->Ci <= LeafState->GammaStar)
-%     {
-%         LeafState->Ci = LeafState->GammaStar; // ppm
-%     }
-CalGs(1)=Gs;
-CalGs(2)=Ci;
-end

### 2025-04-29 SimCO2.m
Delete SimCO2.m

@@ -1,101 +1,0 @@
-global pcfactor;  
-ProteinTotalRatio=0.973;
-pcfactor=1/ProteinTotalRatio;
-inE=importdata('MeM_input5_0.txt');
-Einput=inE.data;
-Edata=importdata('Einput7.txt');
-Eio=Edata.data(:,1);
-% WeatherTemp=25;
-% Air_CO2=400;
-% WeatherRH=0.6;
-% WeatherWind=5;
-% Radiation_PAR=470/2000*2000*0.85;%%%%
-% Radiation_NIR=0;
-% Radiation_LW=0;
-% PhotosynthesisType=1.1;
-% Vcmax25=100;
-% Jmax25=200;
-% GRNC=1;
-% LeafResult=Leaf(WeatherRH,WeatherTemp,Air_CO2,WeatherWind,Radiation_PAR,Radiation_NIR,Radiation_LW,PhotosynthesisType,Vcmax25,Jmax25,GRNC,Einput,Eio);
-% %Result=Leaf(0.6,28,5,400,0,0,1)
-% 
-% Cii(i)=LeafResult(1);
-% NetAssimilationi(i)=LeafResult(2);
-% Gsi(i)=LeafResult(3);
-% LeafTemperaturei(i)=LeafResult(4);
-% Transpirationi(i)=LeafResult(5);
-
-
-for i=1:40
-WeatherTemp=25;
-Air_CO2=10+40*i;
-Air_CO2i(i)=Air_CO2;
-WeatherRH=0.6;
-WeatherWind=5;
-Radiation_PAR=470/2000*2000*0.85*0.85;%%%%
-Radiation_NIR=0;
-Radiation_LW=0;
-PhotosynthesisType=1.1;
-Vcmax25=100;
-Jmax25=200;
-GRNC=0;
-LeafResult=Leaf(WeatherRH,WeatherTemp,Air_CO2,WeatherWind,Radiation_PAR,Radiation_NIR,Radiation_LW,PhotosynthesisType,Vcmax25,Jmax25,GRNC,Einput,Eio);
-%Result=Leaf(0.6,28,5,400,0,0,1)
-
-Cii(i)=LeafResult(1);
-NetAssimilationi(i)=LeafResult(2);
-Gsi(i)=LeafResult(3);
-LeafTemperaturei(i)=LeafResult(4);
-Transpirationi(i)=LeafResult(5);
-end
-Air_CO2=0;
-for j=1:40
[…]

### 2025-04-29 SYSInitial.m
Delete SYSInitial.m

@@ -1,71 +1,0 @@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- 
-%   Copyright   Xin-Guang Zhu, Yu Wang, Donald R. ORT and Stephen P. LONG
-%CAS-MPG Partner Institute for Computational Biology, Shanghai Institutes for Biological Sciences, CAS, Shanghai,200031 
-%China Institute of Genomic Biology and Department of Plant Biology, Shanghai Institutes for Biological Sciences, CAS, Shanghai,200031 
-%University of Illinois at Urbana Champaign
-%Global Change and Photosynthesis Research Unit, USDA/ARS, 1406 Institute of Genomic Biology, Urbana, IL 61801, USA.
- 
-%   This file is part of e-photosynthesis.
- 
-%    e-photosynthesis is free software; you can redistribute it and/or modify
-%    it under the terms of the GNU General Public License as published by
-%    the Free Software Foundation; 
- 
-%    e-photosynthesis is distributed in the hope that it will be useful,
-%    but WITHOUT ANY WARRANTY; without even the implied warranty of
-%    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-%    GNU General Public License for more details.
- 
-%    You should have received a copy of the GNU General Public License (GPL)
-%    along with this program.  If not, see <http://www.gnu.org/licenses/>.
- 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% SYSInitial.m
-% This routine initialze the parameters used for all the routines.
-
-function fin = SYSInitial(Begin)
-
-% The total runing time is set as tglobal
-global tglobal;
-global Primer; 
-Primer = 300; 
-
-tglobal = 1000; 
-
- 
-global options1
-options1 = odeset('RelTol',1e-4);
-
-global PS12ratio;        
-global input_PSIIcore;
-global input_PSI;
-global PSIIantennaSize;
-global PSIantennaSize;
-global input_LHCII;
-global input_LHCI; 
-
-input_PSIIcore=1;
-input_PSI=1;
[…]

### 2025-04-29 Jmax_adj.m
Delete Jmax_adj.m

@@ -1,121 +1,0 @@
-clear all;
-% Fitting WT IR64 data provided by IRRI (Gas exchange measurement WT plants)
-% Tleaf average of 8 replicates = 28.93104073C
-Vcmax_m=134.380530667391;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-J=189.091184437385;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-
-%%%%%%%%%%
-Lii=2000;%light intensity from IRRI
-
-%Farquhar model parameters
-%Gr=50.2248975;%µbar %Gamma Star calculated from fitting IR64 of IRRI using Hermida-Carrera rice parameters at Tleaf
-Gr = 49.6558492521714;%µmol mol-1
-
-%Rd=1;%default
-Rd = 1.33898789673117; %umol m-2 s-1, estimated using msuRACiFit (Gregory et al 2021) rice parameters at Tleaf 
-
-%Gm = 5.395926789339; %umol m-2 s-1 Pa-1
-Gm = 0.545813281251705; %umol m-2 s-1
-
-I2=Lii/2*0.85*(1-0.15);
-Theta=0.7;
-
-%Kc=348.318266403677;%ubar, 34.832 Pa, avg of Tleaf values, rice c and dHa
-%Ko=275.324214275076;%mbar, 27.532 kPa, avg of Tleaf values, rice c and dHa 
-%Kc_air = 613.901254795337;%ubar, 61.390 Pa avg of Tleaf values, rice c and dHa
-Kc_air = 606.946980366782;%umol mol-1
-
-O=210;%mbar
-
-%J=(I2+Jmax_m-sqrt((I2+Jmax_m)^2-4*Theta*I2*Jmax_m))/(2*Theta);
-%%%%%%%%%%%%%%%%%%%%%
-CA=[800,1200,1500,1800];
-global Vrubusco_adj;
-%Vrubusco_adj=1.12; 
-Vrubusco_adj=1.0; % keep same rubisco activity as original Einput
-global VmaxAdj;%adjust enzyme activity
-global pcfactor;  
-ProteinTotalRatio=0;
-pcfactor=1/ProteinTotalRatio;
-% inE=importdata('MeM_input5_0.txt');
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
[…]

### 2025-04-29 Jmax_adj_simple_25.m
Delete Jmax_adj_simple_25.m

@@ -1,132 +1,0 @@
-%% Simplified Jmax_adj for running only the metabolic model (MetaOnly==1)
-% Parameters have been adjusted from 28.9 to 25C
-Vcmax_m = 134.380530667391/1.408711051;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-J = 189.091184437385/1.259126805;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-Lii = 2000;%Light intensity from IRRI
-
-%Farquhar model parameters
-Gr = 42.9424603786498;%µmol mol-1
-Rd = 1.33898789673117/1.276318536; %umol m-2 s-1
-Gm = 0.545813281251705/1.29400125830567; %umol m-2 s-1
-Kc_air = 222.419986169190;%umol mol-1
-
-O = 210;%mbar
-
-%%%%%%%%%%%%%%%%%%%%%
-%CA=[800,1200,1500,1800]; %need to establish range of Cc as inputs
-CA = [400,600,800,1000];
-
-% Before beginning, we need to replot Ci vs A and 
-% substitute the mean fitted params Vcmax, J and TPU in the Farq model equations 
-% to ascertain where CO2 ranges of Ac,Aj and Ap lie 
-% Transition point between RuBP and TPU limitation is around Ci = 798 umol
-% equivalent to CA = 1140 umol
-% Thus the initial range of CA=[800,1200,1500,1800] looks already to be in the TPU limited range
-% A better range for scaling RuBP limitation would be CA = [400,600,800,1000]
-
-global Vrubusco_adj;
-Vrubusco_adj = 1.0; % keep same rubisco activity as original Einput
-global VmaxAdj;%adjust enzyme activity
-global pcfactor;  
-ProteinTotalRatio=0;
-%pcfactor=1/ProteinTotalRatio;
-%21/05/24 Change pcfactor to 1 here to avoid Inf
-pcfactor = 1;
-%%%%%%%%%%%%%%%%%%%%%
-
-Einput = ones(37,1);%No gene expression data input
-Edata = importdata('Einput7.txt');
-Eio = Edata.data(:,1);
-%MetaOnly=1;% if MetaOnly=1 run only Metabolic model
-WeatherTemp = 25; %Avg Tleaf, Original = 25C
[…]

### 2025-04-29 SensitivityA.m
Delete SensitivityA.m

@@ -1,82 +1,0 @@
-clear all;
-        k=2000*0.85*0.85;
-        PPFDi=k;
-        Tempi=25;
-        CO2iH=550*0.7;
-        CO2iL=370*0.7;
-        Edata=importdata('Einput7.txt');
-        Eio=Edata.data(:,1);
-        
-        global pcfactor;
-         pcfactor=1.045;%1/0.973;%1.423;
-         Eiot=Eio;
-% %          Eiot(1:27)=Eio(1:27)*pcfactor;
-% %          Eiot(38)=Eio(38)*pcfactor;
-% %          Eiot(45)=Eio(45)*pcfactor;
-% %      if pcfactor==1.059;
-% %          Eiot(1)=Eiot(1)/pcfactor;
-% %      end
-     if pcfactor==1.045;%1.423;
-         Eiot(1)=Eio(1)*pcfactor;
-         Eiot(4)=Eio(4)*pcfactor;
-         Eiot(5)=Eio(5)*pcfactor;
-         Eiot(8)=Eio(8)*pcfactor;
-         Eiot(11)=Eio(11)*pcfactor;
-         Eiot(21)=Eio(21)*pcfactor;
-         Eiot(22)=Eio(22)*pcfactor;
-         Eiot(25)=Eio(25)*pcfactor;
-         Eiot(38)=Eio(38)*pcfactor;
-     end
-      pcfactor=1;
-     
-%         if pcfactor==1.423;
-%          Eiot(4)=Eio(4)*pcfactor;
-%          Eiot(5)=Eio(5)*pcfactor;
-%          Eiot(8)=Eio(8)*pcfactor;
-%          Eiot(11)=Eio(11)*pcfactor;
-%          Eiot(21)=Eio(21)*pcfactor;
-%          Eiot(22)=Eio(22)*pcfactor;
-%          Eiot(25)=Eio(25)*pcfactor;
-%          Eiot(38)=Eio(38)*pcfactor;
-%      end
-
-inE=importdata('MeM_input5_0.txt');
-Einput=inE.data;
-        
-        StanAo=EPS_Drive_GRNs(Einput,CO2iL,PPFDi,Tempi,0,0,Eio);
-        StanAe=EPS_Drive_GRNs(Einput,CO2iH,PPFDi,Tempi,0,0,Eio);
[…]

### 2025-04-29 SimPAR.m
Delete SimPAR.m

@@ -1,73 +1,0 @@
-% PCfactorMri=[0.964,1.002,0.960,0.984,0.977,1.003,0.981,1.007,0.986,1.011,0.998,1.021,1.012,1.033,0.972,0.999];
-% inE=importdata('MeM_input8.txt');
-% PCfactorMri=[0.700,0.687,1.01,1.037,0.961,0.980];
-% inE=importdata('MeM_input9.txt');
-% PCfactorMri=[0.897,0.9225,0.821,0.826,0.704,0.695];
-% inE=importdata('MeM_input10.txt');
-% 
-% PCfactorMri=[0.973,1];
-
-global pcfactor;  
-ProteinTotalRatio=0.973;
-pcfactor=1/ProteinTotalRatio;
-inE=importdata('MeM_input5_0.txt');
-Einput=inE.data;
-Edata=importdata('Einput7.txt');
-Eio=Edata.data(:,1);
-
-
-for i=1:25
-WeatherTemp=25;
-Air_CO2=400;
-WeatherRH=0.6;
-WeatherWind=5;
-Radiation_PAR=20*i-10;
-Radiation_PARi(i)=Radiation_PAR;
-Radiation_PARa=Radiation_PAR*0.85*0.85;
-Radiation_NIR=0;
-Radiation_LW=0;
-PhotosynthesisType=1.1;
-Vcmax25=100;
-Jmax25=200;
-GRNC=0;
-LeafResult=Leaf(WeatherRH,WeatherTemp,Air_CO2,WeatherWind,Radiation_PARa,Radiation_NIR,Radiation_LW,PhotosynthesisType,Vcmax25,Jmax25,GRNC,Einput,Eio);
-%Result=Leaf(0.6,28,5,400,0,0,1)
-
-Cii(i)=LeafResult(1);
-NetAssimilationi(i)=LeafResult(2);
-Gsi(i)=LeafResult(3);
-LeafTemperaturei(i)=LeafResult(4);
-Transpirationi(i)=LeafResult(5);
-end
-Radiation_PAR=0;
-
-for j=1:25
-WeatherTemp=25;
-Air_CO2=400;
-WeatherRH=0.6;
-WeatherWind=5;
-Radiation_PAR=20*j-10;
-Radiation_PARa=Radiation_PAR*0.85*0.85;
-%Radiation_PARi(i)=Radiation_PAR;
-Radiation_NIR=0;
-Radiation_LW=0;
-PhotosynthesisType=1.1;
-Vcmax25=100;
[…]

### 2025-04-29 SimTF.m
Delete SimTF.m

@@ -1,87 +1,0 @@
-clear all;
-% PCfactorMri=[0.964,1.002,0.960,0.984,0.986,1.011,0.972,0.999];
-% inE=importdata('MeM_input11.txt');
-
-% PCfactorMri=[0.700,0.687,1.01,1.037,0.961,0.980];
-% inE=importdata('MeM_input9.txt');
-PCfactorMri=[1,0.973,0.981,1.008];
-inE=importdata('MeM_input12.txt');
-
-
-[row,col]=size(inE.data);
-% PCfactorMri=[0.973,1];
-
-global pcfactor;  
-% ProteinTotalRatio=0.973;
-% pcfactor=1/ProteinTotalRatio;
-% inE=importdata('MeM_input5_0.txt');
-% Einput=inE.data;
-Edata=importdata('Einput7.txt');
-Eio=Edata.data(:,1);
-
-for TFno=3:4
-    TFno
-ProteinTotalRatio=PCfactorMri(TFno);
-pcfactor=1/ProteinTotalRatio;
-Einput=inE.data(:,TFno);
-for j=1:20
-WeatherTemp=25;
-Air_CO2=750;
-WeatherRH=0.6;
-WeatherWind=5;
-Radiation_PAR=20*j-10;
-Radiation_PARi(j)=Radiation_PAR;
-Radiation_PARa=Radiation_PAR*0.85*0.85;
-Radiation_NIR=0;
-Radiation_LW=0;
-PhotosynthesisType=1.1;
-Vcmax25=100;
-Jmax25=200;
-GRNC=1;
-LeafResult2=Leaf(WeatherRH,WeatherTemp,Air_CO2,WeatherWind,Radiation_PAR,Radiation_NIR,Radiation_LW,PhotosynthesisType,Vcmax25,Jmax25,GRNC,Einput,Eio);
-%Result=Leaf(0.6,28,5,400,0,0,1)
-HCii(j,TFno)=LeafResult2(1);
-HNetAssimilationi(j,TFno)=LeafResult2(2);
-HGsi(j,TFno)=LeafResult2(3);
-HLeafTemperaturei(j,TFno)=LeafResult2(4);
-HTranspirationi(j,TFno)=LeafResult2(5);
-end
-end
-
-Radiation_PARi=Radiation_PARi*1E6/(2.35E5); %Convert W m^{-2} to u moles m^{-2} s^{-1}
-% figure;
[…]

### 2025-04-29 Vcmax_adj.m
Delete Vcmax_adj.m

@@ -1,123 +1,0 @@
-clear all;
-% Fitting WT IR64 data provided by IRRI (Gas exchange measurement WT plants)
-% Tleaf average of 8 replicates = 28.93104073C
-Vcmax_m=134.380530667391;% Avg Estimated using msuRACiFit (Gregory et al 2016) with rice Gamma Star at 28.9C
-J=189.091184437385;% Avg Estimated using msuRACiFit (Gregory et al 2016) with rice Gamma Star at 28.9C
-
-%%%%%%%%%%
-Lii=2000;%light intensity from IRRI
-%Lii=1500;%light intensity from Acevedo-Siaca
-
-%Farquhar model parameters
-%Gr=38.6;%µbar von caemmerer 2020 %Gamma Star
-%Gr=50.2248975;%µbar %Gamma Star calculated from fitting IR64 of IRRI using Hermida-Carrera rice parameters at Tleaf
-Gr = 49.6558492521714;%µmol mol-1
-
-%Rd=1; %default value for day respiration (in light)
-Rd = 1.33898789673117; %umol m-2 s-1, estimated using msuRACiFit (Gregory et al 2016) rice parameters at Tleaf 
-%Gm = 5.395926789339; %umol m-2 s-1 Pa-1
-Gm = 0.545813281251705; %umol m-2 s-1
-
-I2=Lii/2*0.85*(1-0.15);
-Theta=0.7;
-
-%Kc=348.318266403677;%ubar, 34.832 Pa, avg of Tleaf values, rice c and dHa
-%Ko=275.324214275076;%mbar, 27.532 kPa, avg of Tleaf values, rice c and dHa
-%Kc_air = 613.901254795337;%ubar, 61.390 Pa avg of Tleaf values, rice c and dHa
-Kc_air = 606.946980366782;%umol mol-1
-
-O=210;%mbar
-
-%Rearrange
-%Kc_air=Kc*(1+(O/Ko))
-%Ko=O/((Kc_air/Kc)-1)
-%%%%%%%%%%%%%%%%%%%%%
-% Check range to avoid intersection of Rubisco-limited and electron transport
-% limited points
-CA=[100,150,200,250,300];
-
-global Vrubusco_adj;
[…]

### 2025-04-29 Vcmax_adj_simple_25.m
Delete Vcmax_adj_simple_25.m

@@ -1,124 +1,0 @@
-%% Simplified Vcmax_adj for running only the metabolic model (MetaOnly==1)
-% Parameters have been adjusted from 28.9 to 25C
-Vcmax_m = 134.380530667391/1.408711051;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-J = 189.091184437385/1.259126805;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-Lii = 2000;%Light intensity from IRRI
-
-%Farquhar model parameters
-Gr = 42.9424603786498;%µmol mol-1
-Rd = 1.33898789673117/1.276318536; %umol m-2 s-1
-Gm = 0.545813281251705/1.29400125830567; %umol m-2 s-1
-Kc_air = 222.419986169190;%umol mol-1
-
-O = 210;%mbar
-
-%%%%%%%%%%%%%%%%%%%%%
-CA = [100,150,200,250,300];
-%Transition point between Rubisco and RuBP limitations is around Ci = 210
-%umol/mol or 21 Pa which in terms of CA = 300 umol
-%So this range is OK
-global Vrubusco_adj;
-global VmaxAdj;%adjust enzyme activity
-VmaxAdj = 0.98;%adjust enzyme activity i.e. sub in optimal Vmaxadj from Jmax_adj % default 1.3
-global pcfactor;  
-ProteinTotalRatio = 0;
-%pcfactor=1/ProteinTotalRatio;
-%21/05/24 Change pcfactor to 1 here to avoid Inf
-pcfactor = 1;
-%%%%%%%%%%%%%%%%%%%%%
-
-Einput = ones(37,1);%No gene expression data input
-Edata = importdata('Einput7.txt');
-Eio = Edata.data(:,1);
-%MetaOnly=1;% if MetaOnly=1 run only Metabolic model
-WeatherTemp = 25; %Avg Tleaf, Original = 25C
-GRNC = 0; % In EPS_Drive_GRNs, if GRNC==0 cATPsyn,CPSi,cNADPHsyn and cpsii=1 are all set to 1
-
-%% Assimilation rates for Farquhar model 
-% Other than 5 different Ci values, everything else is the same - 
-% Maybe for indexing in later steps its easier to keep the repeated values of assimilation?
-Farq_Matrix_V = zeros(250,5);
[…]

### 2025-04-29 testjob.sh
Delete testjob.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-
-#SBATCH -p test
-#SBATCH -J testjob_twotimes
-
-source /etc/profile
-module add matlab/2022a
-
-matlab -nodisplay -nodesktop -r "twotimes('5');quit"
-
-echo Job running on compute node `uname -n`

### 2025-04-29 testloop.m
Delete testloop.m

@@ -1,29 +1,0 @@
-list = ([1,4,0.5;4,6,2;5,4,1;23,20,25;89,87,90;3,2,1;5,7,2;31,33,25])';
-for j = 1:3
-if list(1)<1 
-    disp('list item 1 is below the limit.')
-           continue
-elseif list(2)<4
-    disp('list item 2 is below the limit.')
-           continue
-elseif list(3)<5
-    disp('list item 3 is below the limit.')
-           continue
-elseif list(4)<23
-    disp('list item 4 is below the limit.')
-           continue 
-elseif list(5)<89
-    disp('list item 5 is below the limit.')
-           continue
-elseif list(6)<3
-    disp('list item 6 is below the limit.')
-           continue
-elseif list(7)<5
-    disp('list item 7 is below the limit.')
-           continue
-elseif list(8)<31
-    disp('list item 8 is below the limit.')
-           continue
-else 
-end   
-end

### 2025-04-29 strcat_example.m
Delete strcat_example.m

@@ -1,7 +1,0 @@
-function strcat_example(x)
-
-bestmatrixfilename = strcat ("outputenz_", x, "_potato_1.txt");
-fprintf ('Filename for best matrix output file will be: %s\n', bestmatrixfilename);
-d_plotfilename = strcat ("d_plot_", x, "_potato_1.xls");
-fprintf ('Filename for d_plot output file will be: %s\n', d_plotfilename);
-

### 2025-04-29 percentages.m
Delete percentages.m

@@ -1,32 +1,0 @@
-% ENZYME_PERTURBATION 
-% This script generates random percentages of enzyme activities Vmax by drawing random floating point values between 0-1
-
-rng("shuffle");
-% Generate a random vector to get list of percentages to increase Vmax of Rubisco Aldolase SBPase
-
-% Random percentages (drawn between 0 and 1 to act as multipliers)
-a = 0; 
-b = 1;
-rand_multiplier = (b-a).*abs(rand(100,1)) + a;
-rand_percent = rand_multiplier.*100;
-%Check percentage is between limits
-rand_range = [min(rand_percent) max(rand_percent)];
-
-% % Aldolase percentages
-% aldolase_low = 1; 
-% aldolase_high = 100;
-% aldolase = (aldolase_high-aldolase_low).*rand(100,1) + aldolase_low;
-% a_range = [min(a) max(a)];
-% 
-% % SBPase percentages 
-% sbpase_low = 1; 
-% sbpase_high = 100;
-% sbpase = (sbpase_low-sbpase_high).*rand(100,1) + sbpase_low;
-% s_range = [min(s) max(s)];
-
-% c1 = c(100); % select new percentages in vectors c1, f1 and p1 corresponding to nodes 1-100
-% f1 = f(100);
-% p1 = p(100);
-% A = [c1, f1, p1];
-% 
-% alluptakes = [carbuptake; fatuptake; protuptake]; % recombine into single vector of uptakes

### 2025-04-30 Plotting/Farq_ePhoto_comparison.m
Delete Plotting/Farq_ePhoto_comparison.m

@@ -1,118 +1,0 @@
-%% 19/09/2024
-%% Plot A/Cc curve for measured average parameters from IRRI data and using Ac and Aj equations from Vcmax_adj_simple and Jmax_adj_simple
-% Vcmax, J and TPU parameters are the averaged values of parameters derived from fitting eight curves 
-% using the R package msuRACiFit described in Gregory et al (2021) and is available at: https://github.com/poales/msuRACiFit
-
-%% Farquhar model parameters
-Vcmax_m=134.380530667391;% Mean of 8 curves estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-J=189.091184437385;% Mean of 8 curves estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-TPU=12.9252127787927;% Mean of 8 curves estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-Lii=2000;% Light intensity from IRRI
-
-Gr = 49.6558492521714;% CO2 compensation point (µmol mol-1)
-Rd = 1.33898789673117; % Day respiration (umol m-2 s-1)
-Gm = 0.545813281251705; % Mesophyll conductance (umol m-2 s-1)
-Kc_air = 606.946980366782;% Michaelis Menten of Rubisco carboxylation in 21% O2 (umol mol-1)
-
-O=210;%mbar
-
-%%%%%%%%%%%%%%%%%%%%%
-
-%% e-Photosynthesis model parameters
-%% For running the untuned e-Photosynthesis model
-%global Vrubusco_nonopt;
-Vrubusco_nonopt=1.0;%adjust enzyme activity to 1
-%global VmaxAdj_nonopt;
-VmaxAdj_nonopt=1.0;%adjust enzyme activity to 1 
-
-%% For running the tuned e-Photosynthesis model
-% ORIGINALLY WRONG WAY AROUND - AFFECTING RESULT?
-% global Vrubusco_opt;
[…]

### 2025-04-30 Plotting/plot_A_Cc.m
Delete Plotting/plot_A_Cc.m

@@ -1,88 +1,0 @@
-% 21/06/2024
-% Plot A/Cc curve for measured average parameters from IRRI data and using Ac and Aj equations from Vcmax_adj_simple and Jmax_adj_simple
-% Vcmax, J and TPU parameters are the averaged values of parameters derived from fitting eight curves 
-% using the R package msuRACiFit described in Gregory et al (2021) and is available at: https://github.com/poales/msuRACiFit
-
-Vcmax_m=134.380530667391;% Mean of 8 curves estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-J=189.091184437385;% Mean of 8 curves estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-TPU=12.9252127787927;% Mean of 8 curves estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-Lii=2000;% Light intensity from IRRI
-
-%Farquhar model parameters
-Gr = 49.6558492521714;% CO2 compensation point (µmol mol-1)
-Rd = 1.33898789673117; % Day respiration (umol m-2 s-1)
-Gm = 0.545813281251705; % Mesophyll conductance (umol m-2 s-1)
-Kc_air = 606.946980366782;% Michaelis Menten of Rubisco carboxylation in 21% O2 (umol mol-1)
-
-O=210;%mbar
-
-% Specify range of CAs 
-%Ca=(100:50:2000)';
-Ca=(100:50:1200)';
-
-% Preallocate vectors to store outputs including Ci calculated from CA, and
-% constants for Rubisco limited assimilation, RuBP regeneration limited
-% assimilation and TPU limited assimilation
-[Ci, ...
-    Ac_b, Ac_c, Aj_b, ...
-    Aj_c, Ap_b, Ap_c, ...
-    Net_Ac, Net_Aj, Net_Ap, ...
-    Cc_Ac, Cc_Aj, Cc_Ap, ...
-    Gross_Ac, Gross_Aj, Gross_Ap] = deal(zeros(numel(Ca),1));
-
-for i = 1:numel(Ca)
[…]

### 2025-04-30 Plotting/plot_models.m
Delete Plotting/plot_models.m

@@ -1,105 +1,0 @@
-%% 18/09/2024
-%% Simplified calibration for running only the metabolic model (MetaOnly==1)
-%
-Vcmax_m=134.380530667391;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-J=189.091184437385;% Avg Estimated using msuRACiFit (Gregory et al 2021) with rice Gamma Star at 28.9C
-Lii=2000;%Light intensity from IRRI
-
-%Farquhar model parameters
-Gr = 49.6558492521714;%µmol mol-1
-Rd = 1.33898789673117; %umol m-2 s-1
-Gm = 0.545813281251705; %umol m-2 s-1
-Kc_air = 606.946980366782;%umol mol-1
-
-O=210;%mbar
-
-%%%%%%%%%%%%%%%%%%%%%
-CA=[20:20:1000];% include full range of points (including intersection of GammaStar) extending through both Vcmax and J ranges
-
-%For running the untuned e-Photosynthesis model
-%global Vrubusco_nonopt;
-Vrubusco_nonopt=1.0;%adjust enzyme activity to 1
-%global VmaxAdj_nonopt;
-VmaxAdj_nonopt=1.0;%adjust enzyme activity to 1 
-
-% For running the tuned e-Photosynthesis model
-%global Vrubusco_opt;
-Vrubusco_opt=0.98;%adjust enzyme activity sub in optimal Vrubisco from Vcmax_adj_simple_3 
-%global Vmax_opt;
-VmaxAdj_opt=0.96;%adjust enzyme activity i.e. sub in optimal Vmaxadj from Jmax_adj_simple_3
-
-global pcfactor;  
-ProteinTotalRatio=0;
-%pcfactor=1/ProteinTotalRatio;
-%21/05/24 Change pcfactor to 1 here to avoid Inf
-pcfactor=1;
-%%%%%%%%%%%%%%%%%%%%%
-Einput=ones(37,1);%No gene expression data input
-Edata=importdata('Einput7.txt');
-Eio=Edata.data(:,1);
-%MetaOnly=1;% if MetaOnly=1 run only Metabolic model
-WeatherTemp=28.9310407291759; %Avg Tleaf, Original = 25C
-GRNC=0; % In EPS_Drive_GRNs, if GRNC==0 cATPsyn,CPSi,cNADPHsyn and cpsii=1 are all set to 1
-
-%% Assimilation rates for Farquhar model 
[…]

### 2025-04-30 Plotting/plot_sensitivity.m
Delete Plotting/plot_sensitivity.m

@@ -1,228 +1,0 @@
-%% Plotting results of sensitivity analysis
-%% Load data
-%load output_enzyme_adjustment_test_250.mat; % 100 sims at 250 ppm
-load output_enzyme_adjustment_test_250_2000_2.mat; % 2000 sims at 250 ppm
-%% Create outputs for increases in Gross CO2 assimilation rate
-[IncreaseInGrossAssimilationRate_RSAP,... %four
-    IncreaseInGrossAssimilationRate_RA,IncreaseInGrossAssimilationRate_RS,...
-    IncreaseInGrossAssimilationRate_RP,IncreaseInGrossAssimilationRate_AS,...
-    IncreaseInGrossAssimilationRate_AP,IncreaseInGrossAssimilationRate_SP,...
-        IncreaseInGrossAssimilationRate_R,IncreaseInGrossAssimilationRate_A,...%two
-        IncreaseInGrossAssimilationRate_S,IncreaseInGrossAssimilationRate_P] = deal(zeros(2000,1)); %ones
-%% Convert values for plotting
-% Expressing the y-axis as the increases/decreases in Gross CO2 assimilation rate
-for n=1:length(IncreaseInGrossAssimilationRate_RSAP)
-IncreaseInGrossAssimilationRate_RSAP(n) = GrossAssimilationRate_RSAP(n)-GrossAssimilationRate_RSAP(1);
-IncreaseInGrossAssimilationRate_RA(n) = GrossAssimilationRate_RA(n)-GrossAssimilationRate_RA(1);
-IncreaseInGrossAssimilationRate_RS(n) = GrossAssimilationRate_RS(n)-GrossAssimilationRate_RS(1);
-IncreaseInGrossAssimilationRate_RP(n) = GrossAssimilationRate_RP(n)-GrossAssimilationRate_RP(1);
-IncreaseInGrossAssimilationRate_AS(n) = GrossAssimilationRate_AS(n)-GrossAssimilationRate_AS(1);
-IncreaseInGrossAssimilationRate_AP(n) = GrossAssimilationRate_AP(n)-GrossAssimilationRate_AP(1);
-IncreaseInGrossAssimilationRate_SP(n) = GrossAssimilationRate_SP(n)-GrossAssimilationRate_SP(1);
[…]

### 2025-04-30 Plotting/plot_sensitivity_2.m
Delete Plotting/plot_sensitivity_2.m

@@ -1,286 +1,0 @@
-%% Load data
-load output_enzyme_adjustment_test_250_2000_3.mat; % Load results from 2000 node test simulation
-%% Create outputs for increases in gross CO2 assimilation rate
-[IncreaseInGrossAssimilationRate_RSAP,... %four
-    IncreaseInGrossAssimilationRate_RA,IncreaseInGrossAssimilationRate_RS,IncreaseInGrossAssimilationRate_RP,...
-        IncreaseInGrossAssimilationRate_AS,IncreaseInGrossAssimilationRate_AP,IncreaseInGrossAssimilationRate_SP,...%two
-        IncreaseInGrossAssimilationRate_R,IncreaseInGrossAssimilationRate_A,IncreaseInGrossAssimilationRate_S,IncreaseInGrossAssimilationRate_P] = deal(zeros(2000,1));
-%% Convert values for plotting
-%Expressing the y-axis as the increases/decreases in gross CO2 assimilation rate resulting from FC = 1  (first row in each vector of assimilation rates)
-for n=1:length(GrossAssimilationRate_RSAP)
-IncreaseInGrossAssimilationRate_RSAP(n) = GrossAssimilationRate_RSAP(n)-GrossAssimilationRate_RSAP(1);
-IncreaseInGrossAssimilationRate_RA(n) = GrossAssimilationRate_RA(n)-GrossAssimilationRate_RA(1);
-IncreaseInGrossAssimilationRate_RS(n) = GrossAssimilationRate_RS(n)-GrossAssimilationRate_RS(1);
-IncreaseInGrossAssimilationRate_RP(n) = GrossAssimilationRate_RP(n)-GrossAssimilationRate_RP(1);
-IncreaseInGrossAssimilationRate_AS(n) = GrossAssimilationRate_AS(n)-GrossAssimilationRate_AS(1);
-IncreaseInGrossAssimilationRate_AP(n) = GrossAssimilationRate_AP(n)-GrossAssimilationRate_AP(1);
-IncreaseInGrossAssimilationRate_SP(n) = GrossAssimilationRate_SP(n)-GrossAssimilationRate_SP(1);
-IncreaseInGrossAssimilationRate_R(n) = GrossAssimilationRate_R(n)-GrossAssimilationRate_R(1);
[…]

### 2025-04-30 Plotting/plotting_bars_in_log_new.m
Delete Plotting/plotting_bars_in_log_new.m

@@ -1,84 +1,0 @@
-% Import data from excel file containing results of e-Photosynthesis optimization using rice data
-file = 'Results_optimization_rice_new.xlsx';
-
-% Define range to import data from
-range = 'V5:X30'; %Average, STDEV, SEM for optimized enzyme protein concentrations
-
-% Define sheet names to import data from
-sheet_names = {'140','160','180','200','220','240','260','280','300','320','340','360','380','400','420'};
-
-% Create cell array to import non-optimized and optimized protein data from each Ci/sheet
-results_data = cell(2, numel(sheet_names));
-
-% Loop through all sheets and import values into results_data
-for i = 1:numel(sheet_names)
-    % Read the specified range as a numeric array
-    numeric_data_unoptimized = readmatrix(file, 'Sheet', sheet_names{i}, 'Range', 'AI5:AI30');
-    %numeric_data_optimized = readmatrix(file, 'Sheet', '140', 'Range', 'AI5:AI30');
-    numeric_data_optimized = readmatrix(file, 'Sheet', sheet_names{i}, 'Range', range);
-    % Replace zero values with NaN
-    numeric_data_unoptimized(numeric_data_optimized == 0) = NaN;
-    numeric_data_optimized(numeric_data_optimized == 0) = NaN;
-    % Remove rows containing all NaN values
-    rows_to_keep = any(~isnan(numeric_data_optimized), 2);
-    numeric_data_optimized = numeric_data_optimized(rows_to_keep, :);
-    numeric_data_unoptimized = numeric_data_unoptimized(rows_to_keep, :);
-    % Store data in cell array using sheet names as indices (1-15 = 140-420)
-    results_data{1,i} = numeric_data_unoptimized;
-    results_data{2,i} = numeric_data_optimized;
-end
-
-% Get enzyme names 
-cats = readcell(file, 'Sheet', '140', 'Range', 'C5:C30'); % Read enzyme names
-cats = categorical(cats(rows_to_keep, :)); % Remove duplicate enzymes and convert into categorical 
-
-% Assign x and y for bar graphs
-y = 1:23; % Y-axis values refer to enzymes
-x = horzcat(results_data{1,1},results_data{2,15}(:,1)); % X-axis values refer to protein levels, replace second column results_data {2,i} for each Ci or make a loop e.g. 
[…]

### 2025-04-30 Plotting/plot_bars_in_log.m
Delete Plotting/plot_bars_in_log.m

@@ -1,62 +1,0 @@
-%% Plotting bar charts for non-optimized vs optimized enzyme concentrations
-% This function returns a bar chart taking inputs of the filename,
-% sheet_name i.e. Ci and the ranges (cell_references) of non-optimized and optimized concentration values
-function [results_data,x,x_log,error_values,error_values_log,h] = plot_bars_in_log(file,sheet_name,non_optimized_range,optimized_range)
-
-% Create cell array to import non-optimized and optimized protein data from each Ci/sheet
-results_data = cell(2, 1);
-
-% Import values into results_data
-% Read the enzyme names as a cell array
-cats = readcell(file, 'Sheet', sheet_name, 'Range', 'C5:C30'); % Read enzyme names
-% Read the specified range as a numeric array
-numeric_data_non_optimized = readmatrix(file, 'Sheet', sheet_name, 'Range', non_optimized_range);
-numeric_data_optimized = readmatrix(file, 'Sheet', sheet_name, 'Range', optimized_range);
-% Replace zero values with NaN
-numeric_data_non_optimized(numeric_data_optimized == 0) = NaN;
-numeric_data_optimized(numeric_data_optimized == 0) = NaN;
-% Remove rows containing all NaN values
-rows_to_keep = any(~isnan(numeric_data_optimized), 2);
-numeric_data_optimized = numeric_data_optimized(rows_to_keep, :);
-numeric_data_non_optimized = numeric_data_non_optimized(rows_to_keep, :);
-% Remove enzyme rows containing all NaN values and convert into categorical 
-cats = categorical(cats(rows_to_keep, :)); 
-% Store data in cell array using sheet names as indices (1-15 = 140-420)
-results_data{1,1} = numeric_data_non_optimized;
-results_data{2,1} = numeric_data_optimized;
-
-% Assign x and y for bar graphs
-y = 1:23; % Y-axis values refer to enzymes, doesn't change
-% Assign output variables to non-optimized and optimized protein data  
-x = horzcat(results_data{1,1},results_data{2,1}(:,1)); %Concatenate unoptimized and optimized protein levels
-error_values = results_data{2,1}(:,3); % Error values
-% Convert data and error values to log scale
-x_log = log10(x); % Log-transformed protein data
[…]

### 2025-04-30 Plotting/plotting_scatter_averages.m
Delete Plotting/plotting_scatter_averages.m

@@ -1,266 +1,0 @@
-% This script loops scatter plots for average non-optimized and optimized enzyme
-% concentrations in a loop, creating panels for individual enzymes
-
-%Import all required data in a separate script
-import_optimization_results; %import average of ten replicates
-%import_optimization_reps; % import ten replicates
-
-% Assign x and y for scatter graphs
-% Assign output variables to non-optimized and optimized protein data in linear and log scale 
-y = cell(1, numel(sheet_names));
-y_log = cell(1, numel(sheet_names));
-y_fold = cell(1, numel(sheet_names));
-%y_log_fold = cell(1, numel(sheet_names)); redundant
-
-for i = 1:numel(sheet_names)
-    % Combine full data for non-optimized and optimized at each Cc
-    y{1,i} = horzcat(results_data{1,1},results_data{2,i}(:,1));
-    % Convert data to log scale
-    y_log{1,i} = horzcat(log10(y{1,i}(:,1)),log10(y{1,i}(:,2))); % log x
-    % Calculate y fold changes
-    y_fold{1,i} = y{1,i}(:,2:end)./y{1,i}(:,1);
-    % Calculate y_log fold changes - essentially the same as y fold since
-    % the ratios of non-opt to opt are equal
-    %y_log_fold{1,i} = y_log{1,i}(:,2:end)./y_log{1,i}(:,1);
-end
-
-% Convert sheet_names into x values 
-% Ci = str2double(sheet_names);
-Cc = str2double(sheet_names);
-% Ca = Ci/0.7;
-enzymes=string(cats);
-
-% Output variables for all enzymes
-enzyme_nopt_concs = zeros(size(cats,1),size(y,2)); 
-all_opt_concs = zeros(size(cats,1),size(y,2)); 
-all_opt_FC = zeros(size(cats,1),size(y,2)); 
-all_opt_log_FC = zeros(size(cats,1),size(y,2)); 
-
-CBB_indices = 1:8;
-PR_indices = 10:16;
-SS_indices = [9,17:23];
-
-% Replace PR_constraints reaction IDs with enzyme names 
-PR_blanks = cell(7,1);
-PR_constraints_protein = cat(2,PR_blanks,PR_constraints_protein);
-PR_constraints_protein(:,1) = cellstr(enzymes(PR_indices));
-
-% Horizontally stack PR_limits values for each Cc by repeating col 2 of PR_constraints
-PR_limits = cell2mat(repmat(PR_constraints_protein(:,2),1,26));% last no represents no. of Cc levels
[…]

### 2025-04-30 Plotting/plot_histogram.m
Delete Plotting/plot_histogram.m

@@ -1,109 +1,0 @@
-% Produce a histogram for enzyme sensitivity analysis 
-%% Load data
-load output_enzyme_adjustment_test_250_2000_3.mat; % Load results from 2000 node test simulation
-%% Create outputs for increases in gross CO2 assimilation rate
-[IncreaseInGrossAssimilationRate_RSAP,... %four
-    IncreaseInGrossAssimilationRate_RA,IncreaseInGrossAssimilationRate_RS,IncreaseInGrossAssimilationRate_RP,...
-        IncreaseInGrossAssimilationRate_AS,IncreaseInGrossAssimilationRate_AP,IncreaseInGrossAssimilationRate_SP,...%two
-        IncreaseInGrossAssimilationRate_R,IncreaseInGrossAssimilationRate_A,IncreaseInGrossAssimilationRate_S,IncreaseInGrossAssimilationRate_P] = deal(zeros(2000,1));
-%% Convert values for plotting
-%Expressing the y-axis as the increases/decreases in gross CO2 assimilation rate resulting from FC = 1  (first row in each vector of assimilation rates)
-for n=1:length(GrossAssimilationRate_RSAP)
-IncreaseInGrossAssimilationRate_RSAP(n) = GrossAssimilationRate_RSAP(n)-GrossAssimilationRate_RSAP(1);
-IncreaseInGrossAssimilationRate_RA(n) = GrossAssimilationRate_RA(n)-GrossAssimilationRate_RA(1);
-IncreaseInGrossAssimilationRate_RS(n) = GrossAssimilationRate_RS(n)-GrossAssimilationRate_RS(1);
-IncreaseInGrossAssimilationRate_RP(n) = GrossAssimilationRate_RP(n)-GrossAssimilationRate_RP(1);
-IncreaseInGrossAssimilationRate_AS(n) = GrossAssimilationRate_AS(n)-GrossAssimilationRate_AS(1);
-IncreaseInGrossAssimilationRate_AP(n) = GrossAssimilationRate_AP(n)-GrossAssimilationRate_AP(1);
-IncreaseInGrossAssimilationRate_SP(n) = GrossAssimilationRate_SP(n)-GrossAssimilationRate_SP(1);
-IncreaseInGrossAssimilationRate_R(n) = GrossAssimilationRate_R(n)-GrossAssimilationRate_R(1);
-IncreaseInGrossAssimilationRate_A(n) = GrossAssimilationRate_A(n)-GrossAssimilationRate_A(1);
[…]

### 2025-04-30 Plotting/plot_violins.m
Delete Plotting/plot_violins.m

@@ -1,219 +1,0 @@
-% Produce violin plots for enzyme sensitivity analysis using the violinplot
-% function from cobratoolbox (https://github.com/opencobra/cobratoolbox/blob/master/external/base/utilities/violinPlots/violinplot.m)
-%% Load data
-load output_enzyme_adjustment_test_2000_5_new.mat; % Load results from 2000 node test simulation
-%% Create outputs for increases in gross CO2 assimilation rate
-[IncreaseInGrossAssimilationRate_RS_130,...%two
- IncreaseInGrossAssimilationRate_RS_250,...%two
- IncreaseInGrossAssimilationRate_RS_360,...%two
-    IncreaseInGrossAssimilationRate_RSAP_130,... %four
-    IncreaseInGrossAssimilationRate_RSAP_250,... %four
-    IncreaseInGrossAssimilationRate_RSAP_360,... %four
-        IncreaseInGrossAssimilationRate_RSAPFT_130,...
-        IncreaseInGrossAssimilationRate_RSAPFT_250,...
-        IncreaseInGrossAssimilationRate_RSAPFT_360] = deal(zeros(2000,1));
-%% To express this as % change
-[PercentChangeGrossAssimilationRate_RS_130,...%two
- PercentChangeGrossAssimilationRate_RS_250,...%two
- PercentChangeGrossAssimilationRate_RS_360,...%two
-    PercentChangeGrossAssimilationRate_RSAP_130,... %four
-    PercentChangeGrossAssimilationRate_RSAP_250,... %four
-    PercentChangeGrossAssimilationRate_RSAP_360,... %four
-        PercentChangeGrossAssimilationRate_RSAPFT_130,...
-        PercentChangeGrossAssimilationRate_RSAPFT_250,...
-        PercentChangeGrossAssimilationRate_RSAPFT_360] = deal(zeros(2000,1));
-%% Convert values for plotting
-%Expressing the y-axis as the increases/decreases in gross CO2 assimilation rate resulting from FC = 1  (first row in each vector of assimilation rates)
-for n=1:length(GrossAssimilationRate_RS_130)
-    IncreaseInGrossAssimilationRate_RS_130(n) = GrossAssimilationRate_RS_130(n)-GrossAssimilationRate_RS_130(1);
[…]

### 2025-04-30 Plotting/Violin.m
Copy violin plotting commands from cobratoolbox

@@ -1,0 +1,304 @@
+classdef Violin < handle
+    % Violin creates violin plots for some data
+    %   A violin plot is an easy to read substitute for a box plot
+    %   that replaces the box shape with a kernel density estimate of
+    %   the data, and optionally overlays the data points itself.
+    %
+    %   Additional constructor parameters include the width of the
+    %   plot, the bandwidth of the kernel density estimation, and the
+    %   X-axis position of the violin plot.
+    %
+    %   Use <a href="matlab:help('violinplot')">violinplot</a> for a
+    %   <a href="matlab:help('boxplot')">boxplot</a>-like wrapper for
+    %   interactive plotting.
+    %
+    %   See for more information on Violin Plots:
+    %   J. L. Hintze and R. D. Nelson, "Violin plots: a box
+    %   plot-density trace synergism," The American Statistician, vol.
+    %   52, no. 2, pp. 181-184, 1998.
+    %
+    % Violin Properties:
+    %    ViolinColor - Fill color of the violin area and data points.
+    %                  Defaults to the next default color cycle.
+    %    ViolinAlpha - Transparency of the ciolin area and data points.
+    %                  Defaults to 0.3.
+    %    EdgeColor   - Color of the violin area outline.
+    %                  Defaults to [0.5 0.5 0.5]
+    %    BoxColor    - Color of the box, whiskers, and the outlines of
+    %                  the median point and the notch indicators.
+    %                  Defaults to [0.5 0.5 0.5]
+    %    MedianColor - Fill color of the median and notch indicators.
+    %                  Defaults to [1 1 1]
+    %    ShowData    - Whether to show data points.
+    %                  Defaults to true
+    %    ShowNotches - Whether to show notch indicators.
+    %                  Defaults to false
+    %    ShowMean    - Whether to show mean indicator.
+    %                  Defaults to false
+    %
+    % Violin Children:
+    %    ScatterPlot - <a href="matlab:help('scatter')">scatter</a> plot of the data points
+    %    ViolinPlot  - <a href="matlab:help('fill')">fill</a> plot of the kernel density estimate
+    %    BoxPlot     - <a href="matlab:help('fill')">fill</a> plot of the box between the quartiles
+    %    WhiskerPlot - line <a href="matlab:help('plot')">plot</a> between the whisker ends
+    %    MedianPlot  - <a href="matlab:help('scatter')">scatter</a> plot of the median (one point)
[…]

### 2025-04-30 Plotting/plotting_heatmap.m
Delete Plotting/plotting_heatmap.m

@@ -1,37 +1,0 @@
-% Import data from excel file containing results of e-Photosynthesis optimization using rice data - This version loops both the generation of data and the graphing process
-file = 'Results_optimization_rice.xlsx';
-
-% Define range to import data from
-range = 'V5:X30'; %Average, STDEV, SEM for optimized enzyme protein concentrations
-
-% Define sheet names to import data from
-sheet_names=num2cell(140:20:420);
-
-% Create cell array to import non-optimized and optimized protein data from each Ci/sheet
-results_data = cell(2, numel(sheet_names));
-
-% Loop through all sheets and import values into results_data
-for i = 1:numel(sheet_names)
-    % Read the specified range as a numeric array
-    numeric_data_unoptimized = readmatrix(file, 'Sheet', sheet_names{i}, 'Range', 'AI5:AI30');
-    %numeric_data_optimized = readmatrix(file, 'Sheet', '140', 'Range', 'AI5:AI30');
-    numeric_data_optimized = readmatrix(file, 'Sheet', sheet_names{i}, 'Range', range);
-    % Replace zero values with NaN
-    numeric_data_unoptimized(numeric_data_optimized == 0) = NaN;
-    numeric_data_optimized(numeric_data_optimized == 0) = NaN;
-    % Remove rows containing all NaN values
-    rows_to_keep = any(~isnan(numeric_data_optimized), 2);
-    numeric_data_optimized = numeric_data_optimized(rows_to_keep, :);
-    numeric_data_unoptimized = numeric_data_unoptimized(rows_to_keep, :);
-    % Store data in cell array using sheet names as indices (1-15 = 140-420)
-    results_data{1,i} = numeric_data_unoptimized;
-    results_data{2,i} = numeric_data_optimized;
-end
-
-% Calculate percentage changes per Ci
-x = zeros(numel(y),2); % X-axis values refer to protein levels
-for j = 1:numel(y)
-    i = 1:numel(sheet_names);
-    x(i) = horzcat(results_data{1,1},results_data{2,i}(:,1)); %Replace second column in results_data for each Ci
-    percentage_change(j,i) = (x(i,2)-x(i,1))/x(i,1)*100;
-end

### 2025-04-30 Plotting/scatter3script.m
Delete Plotting/scatter3script.m

@@ -1,207 +1,0 @@
-%% Load data
-load output_enzyme_adjustment_test_250.mat; 
-%% Create outputs for increases in gross CO2 assimilation rate
-[IncreaseInGrossAssimilationRate_RSAP,... %four
-    IncreaseInGrossAssimilationRate_RA,IncreaseInGrossAssimilationRate_RS,IncreaseInGrossAssimilationRate_RP,...%two
-        IncreaseInGrossAssimilationRate_AS,IncreaseInGrossAssimilationRate_AP,IncreaseInGrossAssimilationRate_SP] = deal(zeros(2000,1));
-%% Convert values for plotting
-%Expressing the y-axis as the increases/decreases in net CO2 assimilation rate
-for n=1:length(IncreaseInGrossAssimilationRate_RSAP)
-IncreaseInGrossAssimilationRate_RSAP(n) = GrossAssimilationRate_RSAP(n)-GrossAssimilationRate_RSAP(1);
-IncreaseInGrossAssimilationRate_RA(n) = GrossAssimilationRate_RA(n)-GrossAssimilationRate_RA(1);
-IncreaseInGrossAssimilationRate_RS(n) = GrossAssimilationRate_RS(n)-GrossAssimilationRate_RS(1);
-IncreaseInGrossAssimilationRate_RP(n) = GrossAssimilationRate_RP(n)-GrossAssimilationRate_RP(1);
-IncreaseInGrossAssimilationRate_AS(n) = GrossAssimilationRate_AS(n)-GrossAssimilationRate_AS(1);
-IncreaseInGrossAssimilationRate_AP(n) = GrossAssimilationRate_AP(n)-GrossAssimilationRate_AP(1);
-IncreaseInGrossAssimilationRate_SP(n) = GrossAssimilationRate_SP(n)-GrossAssimilationRate_SP(1);
-end
-
-%Expressing the x-axis as the multiplicative change in protein content
-change_aldolase_FC = aldolase_FC-1;
-change_rubisco_FC = rubisco_FC-1;
-change_sbpase_FC = sbpase_FC-1;
-change_prk_FC = prk_FC-1;
-%% Create scatter plots for each enzyme pair
-%% Rubisco
-figure;
-%scatter(rubisco_FC, GrossAssimilationRate_R, 'filled','MarkerFaceColor',"#D95319");
[…]

### 2025-04-30 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Update and rename 03_msuRACiFit_rice_params.Rmd to msuRACiFit_rice_params.Rmd

### Install A/Ci fitting package if necessary

## msuRACiFit

```{r}
library(devtools)
devtools::install_github("poales/msuRACiFit")
```

OR

```{r}
remotes::install_github("poales/msuRACiFit")
```

### Load the msuRACiFit and readxl libraries:

```{r}
library(readxl)
library(msuRACiFit)
```

### Import excel data from the original file:

```{r}
#gas_exchange_data <- read_excel("Data/Gas_exchange_measurement_WT_plants.xls")
# ABSOLUTE PATH
gas_exchange_data <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/Gas_exchange_measurement_WT_plants.xls")
```

#### OR load each dataset as a separate file:

```{r}
#A330502WT1 <- read_excel("Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
#A330502WT2 <- read_excel("Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
#A330504WT1 <- read_excel("Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
#A330504WT2 <- read_excel("Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
#A330506WT1 <- read_excel("Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
#A330506WT2 <- read_excel("Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
#A330509WT1 <- read_excel("Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
#A330509WT2 <- read_excel("Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")

#ABSOLUTE PATHS
A330502WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
A330502WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
A330504WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
A330504WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
A330506WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
A330506WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
A330509WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
A330509WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")

```

### Append datasets in a list:

```{r}
datasets <- list(c(A330502WT1),
                 c(A330502WT2),
                 c(A330504WT1),
                 c(A330504WT2),
                 c(A330506WT1),
                 c(A330506WT2),
                 c(A330509WT1),
                 c(A330509WT2))
```

### Calculate Gamma Star at diff temperatures, we use the function

```{r}
msuRACiFit::calcGammaStar(c,dHa,tleaf,oxygen)
```

#### The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.

##### Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.

#### So, the $c$ and $\Delta H_a$ for gamma\* presented in the app/ preset table are for ppm, \#' and gamma\* is corrected \# as follows: gamma(Pa) = gamma(ppm) \* 1000 / 1000000 \* patm, \#' Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* patm, \#' Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* patm, \#' Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000

### Create vectors of mean temperature and pressure

```{r}
mean_temps <- numeric(length = 8) 
mean_press <- numeric(length = 8)
```

```{r}
for (i in seq_along(datasets)) { 
  mean_temps[i] <- mean(datasets[[i]]$Tleaf) 
  mean_press[i] <- mean(datasets[[i]]$Press) }
```

### Call calcgammastar function with different temp inputs and get outputs saved in single vector for 8 files

```{r}
Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
```

### Next, we account for the variation in Press for each dataset and convert GammaStar back to Pa

```{r}
Gstars_Pa_rice<-Gstars_rice*(1000 / 1000000)*mean_press 
```

### Gamma Star at 25C differs for each file/dataset because the mean press differs

```{r}
Gstars_25_rice<-msuRACiFit::calcGammaStar(13.7,24.6,25,21)  
Gstars_25_Pa_rice<-Gstars_25_rice*(1000 / 1000000)*mean_press 
```

### Save these gamma star values

```{r}
write.csv(Gstars_rice,file = "Outputs/Parameters/Gstars_rice.csv") #ppm
```

```{r}
write.csv(Gstars_Pa_rice,file = "Outputs/Parameters/Gstars_Pa_rice.csv") #Pa
```

```{r}
write(Gstars_25_Pa_rice,file="Outputs/Parameters/Gstars_25_Pa_rice.csv",sep=" ")
```

### To fit data using Shiny app, run

```{r}
msuRACiFit::genApp()
```

### Select O.sativa as preset plant and copy in the average Tleaf and Pa for each curve

#### Generate guess and fit, saving output, png and table

#### Compare the fits found using complete sets of Sharkey's parameters for tobacco and Carmen's parameters for rice

#### 11/12/2023

#### We couldn't get a good estimate of Ko c and dHa via nls

#### (As it was fitted with near zero residuals, should not have converged)

##### It may be better to calculate a series of Ko values (one at each Tleaf) and pass them onto the fitting function

#### But first- calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko

#### Make sure all constants are named differently within the function to what they are called outside the function

### Load data containing kinetic parameters for rice

```{r}
param_data <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/Rubisco_kinetics_Oryza_sativa.xlsx")
```

### Import data for Kc_c and Kc_dHa

```{r}
Kc_c <- mean(na.omit(as.numeric(param_data$`c Kc (from μmolmol-1) (dimensionless)`))) 
Kc_dHa <- mean(na.omit(as.numeric(param_data$`DHA Kc (from μmolmol-1) (KJmol-1)`)))
```

### Import data for Kcair_c and Kcair_dHa

```{r}
Kcair_c <- mean(na.omit(as.numeric(param_data$`c Kcair (from μmolmol-1) (dimensionless)`))) 
Kcair_dHa <- mean(na.omit(as.numeric(param_data$`DHA Kcair (from μmolmol-1) (KJmol-1)`)))
```

### Write function to use the mean temperature in celsius from each curve for calculating Kc and Kcair

```{r}
kinetic_params <- function(tempinC) 
    { ideal_gas <- 0.008314 # Ideal gas constant 
    kelvin <- 273.15 # Kelvin constant 
    Kc_scaling <- Kc_c # Kc scaling constant (unitless)
    Kc_activation <- Kc_dHa # Kc energy of activation (kJ mol -1) 
    Kcair_scaling <- Kcair_c # Kcair scaling constant (unitless) 
    Kcair_activation <- Kcair_dHa # Kcair energy of activation (kJ mol -1) 
    O2 <- 21000 # Oxygen concentration (Pa) 
    # Calculate Kc in umol at a specific temperature 
    Kc <- exp(Kc_scaling - (Kc_activation / (ideal_gas * (kelvin + tempinC)))) 
    # Calculate Kcair in umol at a specific temperature 
    Kcair <- exp(Kcair_scaling - (Kcair_activation / (ideal_gas * (kelvin + tempinC))))      
    return(c(Kc,Kcair)) }
```

### Create an empty dataframe to store all Kc and Kcair outputs

```{r}
all_param <- data.frame(Kc = numeric(length(mean_temps)), 
                        Kcair = numeric(length(mean_temps)))
```

### Loop through kinetic_params function, calculate Kc and Ko values at each temperature in mean_temps and convert values from ppm to Pa according to each mean_press

```{r}
for (j in seq_along(mean_temps)) { 
  # Call the kinetic_params function to calculate Kc and Kcair for the current temperature and convert them to Pa based on mean pressure 
  param <- kinetic_params(mean_temps[j])*(1000 / 1000000)*mean_press[j] 
  # Store the results in the output dataframe 
  all_param[j, ] <- param }
```

### Currently Kc and Kcair are in Pa

### Append a column for calculating Ko from Kc and Kcair and converting these values to kPa

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press 
write.csv(all_param,file = "C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
```

### Input Kc and Ko values from all_param into fitComplete

### Call fitComplete with different inputs and use a list of lists to store outputs

### Initialise an empty list to store output of fitComplete

```{r}
complete_Fits_rice_list <- vector("list", length(datasets)) 
```

### This loop indexes through vectors (mean_temps,mean_press,Gstars_Pa_rice) and lists (assimilation_rates, intercellular_CO2) to fit 8 curves using fitComplete and save their outputs

### Vector of forceValues/bound_l/bound_h in order: VcMax, J, TPU, gm, Rd, aG, aS

```{r}
for (k in seq_along(datasets)) {  
  data_k <- datasets[[k]]
  if ("data" %in% colnames(data_k)) {
    data_k <- data_k$data  
  }
  data_k <- as.data.frame(data_k)

  complete_Fits_rice <- fitComplete(
    data = data_k,  
    name_assimilation = "Photo",
    name_ci = "Ci",
    gammastar = Gstars_Pa_rice[k],
    O2 = 21,
    pressure = mean_press[k],
    tleaf = mean_temps[k],
    initialGuess = NA,
    forceValues = c(NA, NA, NA, NA, NA, NA, NA),
    bound_l = c(1, 1, 1, .001, .001, 0, 0),
    bound_h = c(1000, 1000, 1000, 30, 10, 1, .75),
    ignoreTPU = F,
    maxiter = 500,
    Kc = all_param[k, "Kc"],
    Ko = all_param[k, "Ko"]
  )

  complete_Fits_rice_list[[k]] <- complete_Fits_rice
}
```

### Fit curves individually using fitComplete algorithm

```{r}
completeFit1_rice <- fitComplete(A330502WT1, 
                                name_assimilation = "Photo", 
                                name_ci = "Ci", 
                                gammastar = Gstars_Pa_rice[1], 
                                O2 = 21, 
                                pressure = mean_press[1], 
                                tleaf = mean_temps[1], 
                                initialGuess = NA,
                                forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                ignoreTPU = F, 
                                maxiter = 500, 
                                Kc = all_param[1, "Kc"], 
                                Ko = all_param[1, "Ko"]) 
```

### Save parameter outputs

```{r}
write.csv(completeFit1_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")
```

```{r}
completeFit2_rice <- fitComplete(A330502WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[2], 
                                 O2 = 21, 
                                 pressure = mean_press[2], 
                                 tleaf = mean_temps[2], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA),
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, maxiter = 500, 
                                 Kc = all_param[2, "Kc"], 
                                 Ko = all_param[2, "Ko"]) 
```

### Save parameter outputs

```{r}
write.csv(completeFit2_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")
```

```{r}
completeFit3_rice <- fitComplete(A330504WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[3], 
                                 O2 = 21, 
                                 pressure = mean_press[3], 
                                 tleaf = mean_temps[3], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[3, "Kc"], 
                                 Ko = all_param[3, "Ko"]) 
```

### Save parameter

```{r}
write.csv(completeFit3_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")
```

```{r}
completeFit4_rice <- fitComplete(A330504WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[4], 
                                 O2 = 21, 
                                 pressure = mean_press[4], 
                                 tleaf = mean_temps[4], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[4, "Kc"], 
                                 Ko = all_param[4, "Ko"]) 
```

### Save parameter outputs

```{r}
write.csv(completeFit4_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")
```

```{r}
completeFit5_rice <- fitComplete(A330506WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[5], 
                                 O2 = 21, 
                                 pressure = mean_press[5], 
                                 tleaf = mean_temps[5], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[5, "Kc"], 
                                 Ko = all_param[5, "Ko"])
```

### Save parameter outputs

```{r}
write.csv(completeFit5_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")
```

```{r}
completeFit6_rice <- fitComplete(A330506WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[6], 
                                 O2 = 21, 
                                 pressure = mean_press[6], 
                                 tleaf = mean_temps[6], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[6, "Kc"], 
                                 Ko = all_param[6, "Ko"]) 
```

### Save parameter outputs

```{r}
write.csv(completeFit6_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")
```

```{r}
completeFit7_rice <- fitComplete(A330509WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[7], 
                                 O2 = 21, 
                                 pressure = mean_press[7], 
                                 tleaf = mean_temps[7], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[7, "Kc"], 
                                 Ko = all_param[7, "Ko"]) 
```

### Save parameter outputs

```{r}
write.csv(completeFit7_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")
```

```{r}
completeFit8_rice <- fitComplete(A330509WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[8], 
                                 O2 = 21, pressure = mean_press[8], 
                                 tleaf = mean_temps[8], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[8, "Kc"], 
                                 Ko = all_param[8, "Ko"]) 
```

### Save parameter outputs

```{r}
write.csv(completeFit8_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
```

## Produce data tables for each curve

```{r}
completeTables1_rice <- reconstituteTable(data=A330502WT1, fitParams = completeFit1_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[1], O2=21, pressure=mean_press[(1)], tleaf = mean_temps[(1)], ignoreTPU=F, Kc=all_param[1, "Kc"], Ko=all_param[1, "Ko"])

```

### Save data table

```{r}
write.csv(completeTables1_rice, file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
```

`{SSR1<-sum(completeTables1_rice$res^2)}`

### Plot graph of limitations

```{r}
completeGraph1_rice <- reconstituteGraph(data=A330502WT1, 
                                         fitParams = completeFit1_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[1], 
                                         O2=21, 
                                         pressure=mean_press[(1)], 
                                         tleaf=mean_temps[(1)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[1, "Kc"], 
                                         Ko=all_param[1, "Ko"])
```

```{r}
#png("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
plot(completeGraph1_rice) 
#dev.off()
```

completeTables2_rice \<- reconstituteTable(data=A330502WT2, fitParams = completeFit2_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[2], O2=21, pressure=mean_press[(2)], tleaf = mean_temps[(2)], ignoreTPU=F, Kc=all_param[2, "Kc"], Ko=all_param[2, "Ko"]) #Save data table write.csv(completeTables2_rice, file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv") SSR2\<-sum(completeTables2_rice\$`res^2`)

completeGraph2_rice \<- reconstituteGraph(data=A330502WT2, fitParams = completeFit2_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[2], O2=21, pressure=mean_press[(2)], tleaf=mean_temps[(2)], ignoreTPU=F, Kc=all_param[2, "Kc"], Ko=all_param[2, "Ko"])

png("Outputs/Graphs/fitComplete/Rice/completefits2_console_rice.png", width = 519, height = 457) plot(completeGraph2_rice) dev.off()

completeTables3_rice \<- reconstituteTable(data=A330504WT1, fitParams = completeFit3_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[3], O2=21, pressure=mean_press[(3)], tleaf = mean_temps[(3)], ignoreTPU=F, Kc=all_param[3, "Kc"], Ko=all_param[3, "Ko"]) #Save data table write.csv(completeTables3_rice, file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") SSR3\<-sum(completeTables3_rice\$`res^2`)

completeGraph3_rice \<- reconstituteGraph(data=A330504WT1, fitParams = completeFit3_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[3], O2=21, pressure=mean_press[(3)], tleaf=mean_temps[(3)], ignoreTPU=F, Kc=all_param[3, "Kc"], Ko=all_param[3, "Ko"])

png("Outputs/Graphs/fitComplete/Rice/completefits3_console_rice.png", width = 519, height = 457) plot(completeGraph3_rice) dev.off()

completeTables4_rice \<- reconstituteTable(data=A330504WT2, fitParams = completeFit4_rice[[1]], name_assimilation = "Photo",name_ci=c("Ci"), gammastar=Gstars_Pa_rice[4], O2=21, pressure=mean_press[(4)], tleaf = mean_temps[(4)], ignoreTPU=F, Kc=all_param[4, "Kc"], Ko=all_param[4, "Ko"]) #Save data table write.csv(completeTables4_rice, file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv") SSR4\<-sum(completeTables4_rice\$`res^2`)

completeGraph4_rice \<- reconstituteGraph(data=A330504WT2, fitParams = completeFit4_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[4], O2=21, pressure=mean_press[(4)], tleaf=mean_temps[(4)], ignoreTPU=F, Kc=all_param[4, "Kc"], Ko=all_param[4, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) plot(completeGraph4_rice) dev.off()

completeTables5_rice \<- reconstituteTable(data=A330506WT1, fitParams = completeFit5_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[5], O2=21, pressure=mean_press[(5)], tleaf = mean_temps[(5)], ignoreTPU=F, Kc=all_param[5, "Kc"], Ko=all_param[5, "Ko"]) #Save data table write.csv(completeTables5_rice, file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv") SSR5\<-sum(completeTables5_rice\$`res^2`)

completeGraph5_rice \<- reconstituteGraph(data=A330506WT1, fitParams = completeFit5_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[5], O2=21, pressure=mean_press[(5)], tleaf=mean_temps[(5)], ignoreTPU=F, Kc=all_param[5, "Kc"], Ko=all_param[5, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) plot(completeGraph5_rice) dev.off()

completeTables6_rice \<- reconstituteTable(data=A330506WT2, fitParams = completeFit6_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[6], O2=21, pressure=mean_press[(6)], tleaf = mean_temps[(6)], ignoreTPU=F, Kc=all_param[6, "Kc"], Ko=all_param[6, "Ko"]) #Save data table write.csv(completeTables6_rice, file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") SSR6\<-sum(completeTables6_rice\$`res^2`)

completeGraph6_rice \<- reconstituteGraph(data=A330506WT2, fitParams = completeFit6_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[6], O2=21, pressure=mean_press[(6)], tleaf=mean_temps[(6)], ignoreTPU=F, Kc=all_param[6, "Kc"], Ko=all_param[6, "Ko"])

png("Outputs/Graphs/fitComplete/Rice/completefits6_console_rice.png", width = 519, height = 457) plot(completeGraph6_rice) dev.off()

completeTables7_rice \<- reconstituteTable(data=A330509WT1, fitParams = completeFit7_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[7], O2=21, pressure=mean_press[(7)], tleaf = mean_temps[(7)], ignoreTPU=F, Kc=all_param[7, "Kc"], Ko=all_param[7, "Ko"]) #Save data table write.csv(completeTables7_rice, file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv") SSR7\<-sum(completeTables7_rice\$`res^2`)

completeGraph7_rice \<- reconstituteGraph(data=A330509WT1, fitParams = completeFit7_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[7], O2=21, pressure=mean_press[(7)], tleaf=mean_temps[(7)], ignoreTPU=F, Kc=all_param[7, "Kc"], Ko=all_param[7, "Ko"])

png("Outputs/Graphs/fitComplete/Rice/completefits7_console_rice.png", width = 519, height = 457) plot(completeGraph7_rice) dev.off()

completeTables8_rice \<- reconstituteTable(data=A330509WT2, fitParams = completeFit8_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[8], O2=21, pressure=mean_press[(8)], tleaf = mean_temps[(8)], ignoreTPU=F, Kc=all_param[8, "Kc"], Ko=all_param[8, "Ko"]) #Save data table write.csv(completeTables8_rice, file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") SSR8\<-sum(completeTables8_rice\$`res^2`)

completeGraph8_rice \<- reconstituteGraph(data=A330509WT2, fitParams = completeFit8_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[8], O2=21,pressure=mean_press[(8)], tleaf=mean_temps[(8)], ignoreTPU=F, Kc=all_param[8, "Kc"], Ko=all_param[8, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) plot(completeGraph8_rice) dev.off()

### Combine and save SSR

```{r}
SSR_values <- data.frame(SSR1,SSR2,SSR3,SSR4,SSR5,SSR6,SSR7,SSR8) 
write.csv(SSR_values, file = "Outputs/Parameters/fitComplete/Rice/rice_console_SSR_values.csv", row.names = FALSE)
```

### Export plot coordinates for limitations, example below (consider looping)

```{r}
Ac<-completeGraph1_rice$plot_env$cdat 
Aj<-completeGraph1_rice$plot_env$jdat 
Ap<-completeGraph1_rice$plot_env$pdat 
limitations <- list(Ac,Aj,Ap) 
write.csv(limitations,"Outputs/Tables/fitComplete/Rice/completeFit1_rice_limitations.csv")
```

### 2025-05-01 ComputPhotosynthesisRate.m
Delete ComputPhotosynthesisRate.m

@@ -1,68 +1,0 @@
-%function
-%PhotosynthesisRate=ComputPhotosynthesisRate(PhotosynthesisType,PhotosynthesQ10,Vcmax25,Jmax25,Rd25,R,LeafTemperature,Convert, Radiation_PAR,PhotosynthesisTheta,Ci,Air_O2,GRNC,Einput,Eio) %try including Rd as an input here
-function PhotosynthesisRate=ComputPhotosynthesisRate(PhotosynthesisType,PhotosynthesQ10,Vcmax25,Jmax25,Rd25,R,LeafTemperature,Convert, Radiation_PAR,PhotosynthesisTheta,Ci,Air_O2,GRNC,Einput,Eio,Rd,Gr)
-% %Temporary variables double Q10Temperature;
-% if (PhotosynthesisType == 1.0 || PhotosynthesisType == 1.1)% C3 Farquhar or Metabolic
-%     Rd = Rd25 * exp(18.72 - 46.39 / (R * (LeafTemperature + 273.15))); %comment out since this changes Rd
-%     %Rd = 1.33898789673117; %SV: Rd value from measured data
-% end
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% %Compute C3 photosynthesis %Commented out Farquhar model assimilation
-% %Constant
-% if (PhotosynthesisType == 1.0)% C3 Farquhar
-% Rate_TPu = 23.0; %u moles/m2 leaf area/s
-% %Temporary variables - SV: not used at the moment but should be altered according to species and measured data
-% LeafTemperatureKelvin = LeafTemperature + 273.15; %Leaf temperature in K
-% GammaStar = exp(19.02 - 37.83 / (R * LeafTemperatureKelvin)); %SV: modify GammaStar according to crop
-% Ko = exp(20.30 - 36.38 / (R * LeafTemperatureKelvin)); %SV: modify Kc and Ko 
-% Kc = exp(38.05 - 79.43 / (R * LeafTemperatureKelvin));	%SV: modify Kc and Ko 
-% Vcmax = Vcmax25 * exp(26.35 - 65.33 / (R * LeafTemperatureKelvin)); %SV: substitute Jmax/J value from measured data
[…]

### 2025-05-01 FvCB_check_Vcmax_adj.m
Delete FvCB_check_Vcmax_adj.m

@@ -1,58 +1,0 @@
-% 15/01/2024
-% Calculating assimilation rates for FvCB model to check transition 
-% between Rubisco-limited and electron transport limited phases in A/Ci fit
-
-% Since we averaged Vcmax and J for A/Ci fits,
-% It is important to check that an appropriate range of CA are used to calculate A : 
-% Currently, CA = [100,150,200,250] for Ac and [800,1200,1500,1800] for Aj
-% If using CA in ppm, convert Kcair/Gr/gm to umol/mol and umol/m2s units
-% If converting CA to Pa, convert Kcair/Gr to Pa and gm in umol/m2sPa
-
-% FvCB model parameters
-Vcmax_m = 134.380530667391;% Avg Estimated using msuRACiFit (Gregory et al 2016) with rice Gamma Star at 28.9C
-J = 189.091184437385;% Avg Estimated using msuRACiFit (Gregory et al 2016) with rice Gamma Star at 28.9C
-
-%Gr = 50.2248975;%µbar %Gamma Star calculated from fitting IR64 of IRRI using Hermida-Carrera rice parameters at Tleaf
-Gr = 49.6558492521714;%µmol mol-1
-
-Rd = 1.33898789673117; %Rd estimated using msuRACiFit (Gregory et al 2016) rice parameters at Tleaf 
-
-%Gm = 5.395926789339; %umol m-2 s-1 Pa-1
-Gm = 0.545813281251705; %umol mol-1
-
-%Kc = 348.318266403677;%ubar, 34.832 Pa, avg of Tleaf values, rice c and dHa
-%Ko = 275.324214275076;%mbar, 27.532 kPa, avg of Tleaf values, rice c and dHa 
-%Kc_air = 613.901254795337;%ubar, 61.390 Pa avg of Tleaf values, rice c and dHa
-
-Kc_air = 606.946980366782;%umol mol-1
-
-CA=[100,150,200,250,300]; % range of CA for Ac in ppm
-%CA_j=[800,1200,1500,1800];% range of CA for Aj
-
-global Vrubusco_adj;
[…]

### 2025-05-06 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Update msuRACiFit_rice_params.Rmd

@@
 # ABSOLUTE PATH
-gas_exchange_data <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/Gas_exchange_measurement_WT_plants.xls")
+gas_exchange_data <- read_excel("C:/Users/xxxx/Data/Gas_exchange_measurement_WT_plants.xls")
 ```

### 2025-05-06 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Update msuRACiFit_rice_params.Rmd

@@
 #ABSOLUTE PATHS
-A330502WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
-A330502WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
-A330504WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
-A330504WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
-A330506WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
-A330506WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
-A330509WT1 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
-A330509WT2 <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")
+A330502WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
+A330502WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
+A330504WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
+A330504WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
+A330506WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
+A330506WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
+A330509WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
+A330509WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")
 

### 2025-05-07 CO2_response_fitting/Scripts/03_msuRACiFit_rice.Rmd
Add files via upload

---
title: "msuRACiFits_fits_rice"
author: "Supreeta Vijayakumar"
date: "`r Sys.Date()`"
output: html_document
---

## Install A/Ci fitting package if necessary

msuRACiFit is a package of r scripts used to fit CO2 response curves developed by Thomas Sharkey's lab at Michigan State University.\
\
Source Code:\
<https://github.com/poales/msuRACiFit>

Publication:\
<https://doi.org/10.1111/pce.14153>

### Install the package using devtools:

```{r}
library(devtools)
devtools::install_github("poales/msuRACiFit")
```

### or remotes:

```{r}
remotes::install_github("poales/msuRACiFit")
```

### Load the here, msuRACiFit and readxl libraries:

```{r}
library(here)
library(readxl)
library(msuRACiFit)
```

Using \`here' roots the file path to the project environment.

### Import Excel files containing gas exchange data:

```{r}
A330502WT1 <- read_excel(here("Data","IR64-A009-07-33-05-02_Wildtype1.xlsx"))
A330502WT2 <- read_excel(here("Data","IR64-A009-07-33-05-02_Wildtype2.xlsx"))
A330504WT1 <- read_excel(here("Data","IR64-A009-07-33-05-04_Wildtype1.xlsx"))
A330504WT2 <- read_excel(here("Data","IR64-A009-07-33-05-04_Wildtype2.xlsx"))
A330506WT1 <- read_excel(here("Data","IR64-A009-07-33-05-06_Wildtype1.xlsx"))
A330506WT2 <- read_excel(here("Data","IR64-A009-07-33-05-06_Wildtype2.xlsx"))
A330509WT1 <- read_excel(here("Data","IR64-A009-07-33-05-09_Wildtype1.xlsx"))
A330509WT2 <- read_excel(here("Data","IR64-A009-07-33-05-09_Wildtype2.xlsx"))
```

### Store the files in a list:

```{r}
datasets <- list(c(A330502WT1),
                 c(A330502WT2),
                 c(A330504WT1),
                 c(A330504WT2),
                 c(A330506WT1),
                 c(A330506WT2),
                 c(A330509WT1),
                 c(A330509WT2))
```

### Calculate Gamma Star at different temperatures using calcGammaStar:

```{r}
msuRACiFit::calcGammaStar(c,dHa,tleaf,oxygen)
```

The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.

Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.

$c$ and $\Delta H_a$ for Gamma\* presented in the app/ preset table are for ppm, and gamma\* is corrected as follows:\
\
Gamma\* (Pa) = Gamma\*(ppm) \* 1000 / 1000000 \* Patm,\
Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* Patm\
Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* Patm,\
Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000

### Create vectors of mean temperature and pressure:

```{r}
mean_temps <- numeric(length = 8) 
mean_press <- numeric(length = 8)
```

```{r}
for (i in seq_along(datasets)) { 
  mean_temps[i] <- mean(datasets[[i]]$Tleaf) 
  mean_press[i] <- mean(datasets[[i]]$Press) }
```

### Call calcgammastar function with different temperature inputs and get outputs saved in single vector for 8 files:

```{r}
Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
Gstars_rice_25<-msuRACiFit::calcGammaStar(13.7,24.6,25,21) #rice c and dHa 
```

### Next, we account for the variation in Press for each dataset and converting GammaStar back to Pa:

```{r}
Gstars_Pa_rice<-Gstars_rice*(1000 / 1000000)*mean_press 
```

### Save these gamma star values in a .csv:

```{r}
write.csv(Gstars_rice,file = "Outputs/Parameters/Gstars_rice.csv") #ppm
```

```{r}
write.csv(Gstars_Pa_rice,file = "Outputs/Parameters/Gstars_Pa_rice.csv") #Pa
```

### Alternatively, to fit data using the Shiny app, run:

```{r}
msuRACiFit::genApp()
```

Select *O.sativa* as preset plant and fill in the average Tleaf and Pa for each curve, generating guesses and fits, saving outputs as .png and csv tables.

#### Calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko.

Make sure all constants are named differently within the function to what they are called outside the function.

### Import data for Kc_c and Kc_dHa:

```{r}
Kc_c <- 38.9
Kc_dHa <- 83.1
```

### Import data for Kcair_c and Kcair_dHa:

```{r}
Kcair_c <- 30.5 
Kcair_dHa <- 60.5
```

### Write function to use the mean temperature in celsius from each curve for calculating Kc and Kcair:

```{r}
kinetic_params <- function(tempinC) 
    { ideal_gas <- 0.008314 # Ideal gas constant 
    kelvin <- 273.15 # Kelvin constant 
    Kc_scaling <- Kc_c # Kc scaling constant (unitless)
    Kc_activation <- Kc_dHa # Kc energy of activation (kJ mol -1) 
    Kcair_scaling <- Kcair_c # Kcair scaling constant (unitless) 
    Kcair_activation <- Kcair_dHa # Kcair energy of activation (kJ mol -1) 
    O2 <- 21000 # Oxygen concentration (Pa) 
    # Calculate Kc in umol at a specific temperature 
    Kc <- exp(Kc_scaling - (Kc_activation / (ideal_gas * (kelvin + tempinC)))) 
    # Calculate Kcair in umol at a specific temperature 
    Kcair <- exp(Kcair_scaling - (Kcair_activation / (ideal_gas * (kelvin + tempinC))))      
    return(c(Kc,Kcair)) }
```

### Create an empty dataframe to store all Kc and Kcair outputs:

```{r}
all_param <- data.frame(Kc = numeric(length(mean_temps)), 
                        Kcair = numeric(length(mean_temps)))
```

### Loop through kinetic_params function, calculate Kc and Ko values at each temperature in mean_temps and convert values from ppm to Pa according to each mean_press:

```{r}
for (j in seq_along(mean_temps)) { 
  # Call the kinetic_params function to calculate Kc and Kcair for the current temperature and convert them to Pa based on mean pressure 
  param <- kinetic_params(mean_temps[j])*(1000 / 1000000)*mean_press[j] 
  # Store the results in the output dataframe 
  all_param[j, ] <- param }
```

### Currently Kc and Kcair are in Pa

### Append a column for calculating Ko from Kc and Kcair and converting these values to kPa:

```{r}
all_param$Ko<-(21000 / ((all_param$Kcair / all_param$Kc) - 1))/1000 
all_param$Temperature <- mean_temps 
all_param$Press <- mean_press 
write.csv(all_param,
         file = "Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
```

### Input Kc and Ko values from all_param into fitComplete

### Call fitComplete with different inputs and use a list of lists to store outputs

### Initialise an empty list to store output of fitComplete:

```{r}
complete_Fits_rice_list <- vector("list", length(datasets)) 
```

### This loop indexes through vectors (mean_temps,mean_press,Gstars_Pa_rice) and lists (assimilation_rates, intercellular_CO2) to fit 8 curves using fitComplete and save their outputs

### Vector of forceValues/bound_l/bound_h in order: VcMax, J, TPU, gm, Rd, aG, aS

```{r}
for (k in seq_along(datasets)) {  
  data_k <- datasets[[k]]
  if ("data" %in% colnames(data_k)) {
    data_k <- data_k$data  
  }
  data_k <- as.data.frame(data_k)

  complete_Fits_rice <- fitComplete(
    data = data_k,  
    name_assimilation = "Photo",
    name_ci = "Ci",
    gammastar = Gstars_Pa_rice[k],
    O2 = 21,
    pressure = mean_press[k],
    tleaf = mean_temps[k],
    initialGuess = NA,
    forceValues = c(NA, NA, NA, NA, NA, NA, NA),
    bound_l = c(1, 1, 1, .001, .001, 0, 0),
    bound_h = c(1000, 1000, 1000, 30, 10, 1, .75),
    ignoreTPU = F,
    maxiter = 500,
    Kc = all_param[k, "Kc"],
    Ko = all_param[k, "Ko"]
  )

  complete_Fits_rice_list[[k]] <- complete_Fits_rice
}
```

### Fit curves individually using fitComplete algorithm:

```{r}
completeFit1_rice <- fitComplete(A330502WT1, 
                                name_assimilation = "Photo", 
                                name_ci = "Ci", 
                                gammastar = Gstars_Pa_rice[1], 
                                O2 = 21, 
                                pressure = mean_press[1], 
                                tleaf = mean_temps[1], 
                                initialGuess = NA,
                                forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                ignoreTPU = F, 
                                maxiter = 500, 
                                Kc = all_param[1, "Kc"], 
                                Ko = all_param[1, "Ko"]) 
```

```{r}
completeFit2_rice <- fitComplete(A330502WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[2], 
                                 O2 = 21, 
                                 pressure = mean_press[2], 
                                 tleaf = mean_temps[2], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA),
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, maxiter = 500, 
                                 Kc = all_param[2, "Kc"], 
                                 Ko = all_param[2, "Ko"]) 
```

```{r}
completeFit3_rice <- fitComplete(A330504WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[3], 
                                 O2 = 21, 
                                 pressure = mean_press[3], 
                                 tleaf = mean_temps[3], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[3, "Kc"], 
                                 Ko = all_param[3, "Ko"]) 
```

```{r}
completeFit4_rice <- fitComplete(A330504WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[4], 
                                 O2 = 21, 
                                 pressure = mean_press[4], 
                                 tleaf = mean_temps[4], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[4, "Kc"], 
                                 Ko = all_param[4, "Ko"]) 
```

```{r}
completeFit5_rice <- fitComplete(A330506WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[5], 
                                 O2 = 21, 
                                 pressure = mean_press[5], 
                                 tleaf = mean_temps[5], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[5, "Kc"], 
                                 Ko = all_param[5, "Ko"])
```

```{r}
completeFit6_rice <- fitComplete(A330506WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[6], 
                                 O2 = 21, 
                                 pressure = mean_press[6], 
                                 tleaf = mean_temps[6], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[6, "Kc"], 
                                 Ko = all_param[6, "Ko"]) 
```

```{r}
completeFit7_rice <- fitComplete(A330509WT1, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[7], 
                                 O2 = 21, 
                                 pressure = mean_press[7], 
                                 tleaf = mean_temps[7], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[7, "Kc"], 
                                 Ko = all_param[7, "Ko"]) 
```

```{r}
completeFit8_rice <- fitComplete(A330509WT2, 
                                 name_assimilation = "Photo", 
                                 name_ci = "Ci", 
                                 gammastar = Gstars_Pa_rice[8], 
                                 O2 = 21, pressure = mean_press[8], 
                                 tleaf = mean_temps[8], 
                                 initialGuess = NA, 
                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
                                 ignoreTPU = F, 
                                 maxiter = 500, 
                                 Kc = all_param[8, "Kc"], 
                                 Ko = all_param[8, "Ko"]) 
```

### Save parameter outputs:

```{r}
write.csv(completeFit1_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")

write.csv(completeFit2_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")

write.csv(completeFit3_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")

write.csv(completeFit4_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")

write.csv(completeFit5_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")

write.csv(completeFit6_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")

write.csv(completeFit7_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")

write.csv(completeFit8_rice[[1]], 
          file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
```

## Produce data tables for each curve:

```{r}
completeTables1_rice <- reconstituteTable(data=A330502WT1, 
                                          fitParams = completeFit1_rice[[1]],
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[1],
                                          O2=21, 
                                          pressure=mean_press[(1)], 
                                          tleaf = mean_temps[(1)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[1, "Kc"], 
                                          Ko=all_param[1, "Ko"])

completeTables2_rice <- reconstituteTable(data=A330502WT2, 
                                          fitParams = completeFit2_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[2], 
                                          O2=21, 
                                          pressure=mean_press[(2)], 
                                          tleaf = mean_temps[(2)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[2, "Kc"],
                                          Ko=all_param[2, "Ko"])

completeTables3_rice <- reconstituteTable(data=A330504WT1, 
                                          fitParams = completeFit3_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[3], 
                                          O2=21, 
                                          pressure=mean_press[(3)], 
                                          tleaf = mean_temps[(3)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[3, "Kc"], 
                                          Ko=all_param[3, "Ko"])

completeTables4_rice <- reconstituteTable(data=A330504WT2, 
                                          fitParams = completeFit4_rice[[1]], 
                                          name_assimilation = "Photo",
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[4], 
                                          O2=21, 
                                          pressure=mean_press[(4)], 
                                          tleaf = mean_temps[(4)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[4, "Kc"], 
                                          Ko=all_param[4, "Ko"])

completeTables5_rice <- reconstituteTable(data=A330506WT1, 
                                          fitParams = completeFit5_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[5], 
                                          O2=21, 
                                          pressure=mean_press[(5)], 
                                          tleaf = mean_temps[(5)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[5, "Kc"], 
                                          Ko=all_param[5, "Ko"])

completeTables6_rice <- reconstituteTable(data=A330506WT2, 
                                          fitParams = completeFit6_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[6], 
                                          O2=21, 
                                          pressure=mean_press[(6)], 
                                          tleaf = mean_temps[(6)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[6, "Kc"], 
                                          Ko=all_param[6, "Ko"])

completeTables7_rice <- reconstituteTable(data=A330509WT1, 
                                          fitParams = completeFit7_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[7], 
                                          O2=21, 
                                          pressure=mean_press[(7)], 
                                          tleaf = mean_temps[(7)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[7, "Kc"], 
                                          Ko=all_param[7, "Ko"])

completeTables8_rice <- reconstituteTable(data=A330509WT2, 
                                          fitParams = completeFit8_rice[[1]], 
                                          name_assimilation = "Photo", 
                                          name_ci=c("Ci"), 
                                          gammastar=Gstars_Pa_rice[8], 
                                          O2=21, 
                                          pressure=mean_press[(8)], 
                                          tleaf = mean_temps[(8)], 
                                          ignoreTPU=F, 
                                          Kc=all_param[8, "Kc"], 
                                          Ko=all_param[8, "Ko"])
```

### Save data tables:

```{r}
write.csv(completeTables1_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
write.csv(completeTables2_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv")
write.csv(completeTables3_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") 
write.csv(completeTables4_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv")
write.csv(completeTables5_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv")
write.csv(completeTables6_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") 
write.csv(completeTables7_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv")
write.csv(completeTables8_rice, 
          file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") 
```

### Plot graphs of limitations:

```{r}
completeGraph1_rice <- reconstituteGraph(data=A330502WT1, 
                                         fitParams = completeFit1_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[1], 
                                         O2=21, 
                                         pressure=mean_press[(1)], 
                                         tleaf=mean_temps[(1)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[1, "Kc"], 
                                         Ko=all_param[1, "Ko"])

completeGraph2_rice <- reconstituteGraph(data=A330502WT2, 
                                         fitParams = completeFit2_rice[[1]], 
                                         name_assimilation="Photo", name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[2], O2=21, 
                                         pressure=mean_press[(2)], tleaf=mean_temps[(2)], 
                                         ignoreTPU=F,
                                         Kc=all_param[2, "Kc"], 
                                         Ko=all_param[2, "Ko"])

completeGraph3_rice <- reconstituteGraph(data=A330504WT1, 
                                         fitParams = completeFit3_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[3], 
                                         O2=21, 
                                         pressure=mean_press[(3)], 
                                         tleaf=mean_temps[(3)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[3, "Kc"], 
                                         Ko=all_param[3, "Ko"])

completeGraph4_rice <- reconstituteGraph(data=A330504WT2, 
                                         fitParams = completeFit4_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[4],
                                         O2=21, 
                                         pressure=mean_press[(4)], 
                                         tleaf=mean_temps[(4)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[4, "Kc"], 
                                         Ko=all_param[4, "Ko"])

completeGraph5_rice <- reconstituteGraph(data=A330506WT1, 
                                         fitParams = completeFit5_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[5],
                                         O2=21, 
                                         pressure=mean_press[(5)], 
                                         tleaf=mean_temps[(5)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[5, "Kc"], 
                                         Ko=all_param[5, "Ko"])

completeGraph6_rice <- reconstituteGraph(data=A330506WT2, 
                                         fitParams = completeFit6_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[6],
                                         O2=21, 
                                         pressure=mean_press[(6)], 
                                         tleaf=mean_temps[(6)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[6, "Kc"], 
                                         Ko=all_param[6, "Ko"])

completeGraph7_rice <- reconstituteGraph(data=A330509WT1, 
                                         fitParams = completeFit7_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[7],
                                         O2=21, 
                                         pressure=mean_press[(7)], 
                                         tleaf=mean_temps[(7)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[7, "Kc"], 
                                         Ko=all_param[7, "Ko"])

completeGraph8_rice <- reconstituteGraph(data=A330509WT2, 
                                         fitParams = completeFit8_rice[[1]], 
                                         name_assimilation="Photo", 
                                         name_ci=("Ci"), 
                                         gammastar=Gstars_Pa_rice[8],
                                         O2=21,
                                         pressure=mean_press[(8)], 
                                         tleaf=mean_temps[(8)], 
                                         ignoreTPU=F, 
                                         Kc=all_param[8, "Kc"], 
                                         Ko=all_param[8, "Ko"]) 
```

### Save plots:

```{r}
png("Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
plot(completeGraph1_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits2_console_rice.png", width = 519, height = 457) 
plot(completeGraph2_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits3_console_rice.png", width = 519, height = 457) 
plot(completeGraph3_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) 
plot(completeGraph4_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) 
plot(completeGraph5_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits6_console_rice.png", width = 519, height = 457) 
plot(completeGraph6_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits7_console_rice.png", width = 519, height = 457) 
plot(completeGraph7_rice) 
dev.off()

png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) 
plot(completeGraph8_rice) 
dev.off()
```

#### Calculate sum of squared residuals:

```{r}
SSR1<-sum(completeTables1_rice$res^2)
SSR2<-sum(completeTables2_rice$res^2)
SSR3<-sum(completeTables3_rice$res^2)
SSR4<-sum(completeTables4_rice$res^2)
SSR5<-sum(completeTables5_rice$res^2)
SSR6<-sum(completeTables6_rice$res^2)
SSR7<-sum(completeTables7_rice$res^2)
SSR8<-sum(completeTables8_rice$res^2)
```

### Combine and save SSR values:

```{r}
SSR_values <- data.frame(SSR1,SSR2,SSR3,SSR4,SSR5,SSR6,SSR7,SSR8) 
write.csv(SSR_values, 
          file = "Outputs/Parameters/fitComplete/Rice/rice_console_SSR_values.csv", 
          row.names = FALSE)
```

### Export plot coordinates for limitations, example below:

```{r}
Ac<-completeGraph1_rice$plot_env$cdat 
Aj<-completeGraph1_rice$plot_env$jdat 
Ap<-completeGraph1_rice$plot_env$pdat 
limitations <- list(Ac,Aj,Ap)

write.csv(limitations,"Outputs/Tables/fitComplete/Rice/completeFit1_rice_limitations.csv")
```

### 2025-05-07 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Update and rename 03_msuRACiFit_rice.Rmd to msuRACiFit_rice_params.Rmd

@@
-### Install A/Ci fitting package if necessary
+---
+title: "msuRACiFits_fits_rice_params"
+author: "Supreeta Vijayakumar"
+date: "`r Sys.Date()`"
+output: html_document
+---
 
-## msuRACiFit
+## Install A/Ci fitting package if necessary
+
+msuRACiFit is a package of r scripts used to fit CO2 response curves developed by Thomas Sharkey's lab at Michigan State University.\
+\
+Source Code:\
+<https://github.com/poales/msuRACiFit>
+
+Publication:\
+<https://doi.org/10.1111/pce.14153>
+
+### Install the package using devtools:
 
@@
 
-OR
+### or remotes:
 
@@
 
-### Load the msuRACiFit and readxl libraries:
+### Load the here, msuRACiFit and readxl libraries:
 
 ```{r}
+library(here)
 library(readxl)
@@
 
-### Import excel data from the original file:
+Using \`here' roots the file path to the project environment.
+
+### Import Excel files containing gas exchange data:
 
 ```{r}
-#gas_exchange_data <- read_excel("Data/Gas_exchange_measurement_WT_plants.xls")
-# ABSOLUTE PATH
-gas_exchange_data <- read_excel("C:/Users/xxxx/Data/Gas_exchange_measurement_WT_plants.xls")
+A330502WT1 <- read_excel(here("Data","IR64-A009-07-33-05-02_Wildtype1.xlsx"))
+A330502WT2 <- read_excel(here("Data","IR64-A009-07-33-05-02_Wildtype2.xlsx"))
+A330504WT1 <- read_excel(here("Data","IR64-A009-07-33-05-04_Wildtype1.xlsx"))
+A330504WT2 <- read_excel(here("Data","IR64-A009-07-33-05-04_Wildtype2.xlsx"))
+A330506WT1 <- read_excel(here("Data","IR64-A009-07-33-05-06_Wildtype1.xlsx"))
+A330506WT2 <- read_excel(here("Data","IR64-A009-07-33-05-06_Wildtype2.xlsx"))
+A330509WT1 <- read_excel(here("Data","IR64-A009-07-33-05-09_Wildtype1.xlsx"))
+A330509WT2 <- read_excel(here("Data","IR64-A009-07-33-05-09_Wildtype2.xlsx"))
 ```
 
-#### OR load each dataset as a separate file:
-
-```{r}
-#A330502WT1 <- read_excel("Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
-#A330502WT2 <- read_excel("Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
-#A330504WT1 <- read_excel("Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
-#A330504WT2 <- read_excel("Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
-#A330506WT1 <- read_excel("Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
-#A330506WT2 <- read_excel("Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
-#A330509WT1 <- read_excel("Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
-#A330509WT2 <- read_excel("Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")
-
-#ABSOLUTE PATHS
-A330502WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype1.xlsx")
-A330502WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-02_Wildtype2.xlsx")
-A330504WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype1.xlsx")
-A330504WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-04_Wildtype2.xlsx")
-A330506WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype1.xlsx")
-A330506WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-06_Wildtype2.xlsx")
-A330509WT1 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype1.xlsx")
-A330509WT2 <- read_excel("C:/Users/xxxx/Data/IR64-A009-07-33-05-09_Wildtype2.xlsx")
-
-```
-
-### Append datasets in a list:
+### Store the files in a list:
 
@@
 
-### Calculate Gamma Star at diff temperatures, we use the function
+### Calculate Gamma Star at different temperatures using calcGammaStar:
 
@@
 
-#### The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.
+The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.
 
-##### Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.
+Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.
 
-#### So, the $c$ and $\Delta H_a$ for gamma\* presented in the app/ preset table are for ppm, \#' and gamma\* is corrected \# as follows: gamma(Pa) = gamma(ppm) \* 1000 / 1000000 \* patm, \#' Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* patm, \#' Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* patm, \#' Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000
+$c$ and $\Delta H_a$ for Gamma\* presented in the app/ preset table are for ppm, and gamma\* is corrected as follows:\
+\
+Gamma\* (Pa) = Gamma\*(ppm) \* 1000 / 1000000 \* Patm,\
+Kc (Pa) = Kc(umol mol -1) \* 1000 / 1000000 \* Patm\
+Kcair (Pa) = Kcair(umol mol -1) \* 1000 / 1000000 \* Patm,\
+Ko (kPa) = O(Pa) / ((Kcair(Pa) / Kc(Pa)) - 1)/1000
 
-### Create vectors of mean temperature and pressure
+### Create vectors of mean temperature and pressure:
 
@@
 
-### Call calcgammastar function with different temp inputs and get outputs saved in single vector for 8 files
+### Call calcgammastar function with different temperature inputs and get outputs saved in single vector for 8 files:
 
@@
 Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
+Gstars_rice_25<-msuRACiFit::calcGammaStar(13.7,24.6,25,21) #rice c and dHa 
 ```
 
-### Next, we account for the variation in Press for each dataset and convert GammaStar back to Pa
+### Next, we account for the variation in Press for each dataset and converting GammaStar back to Pa:
 
@@
 
-### Gamma Star at 25C differs for each file/dataset because the mean press differs
-
-```{r}
-Gstars_25_rice<-msuRACiFit::calcGammaStar(13.7,24.6,25,21)  
-Gstars_25_Pa_rice<-Gstars_25_rice*(1000 / 1000000)*mean_press 
-```
-
-### Save these gamma star values
+### Save these gamma star values in a .csv:
 
@@
 
-```{r}
-write(Gstars_25_Pa_rice,file="Outputs/Parameters/Gstars_25_Pa_rice.csv",sep=" ")
-```
-
-### To fit data using Shiny app, run
+### Alternatively, to fit data using the Shiny app, run:
 
@@
 
-### Select O.sativa as preset plant and copy in the average Tleaf and Pa for each curve
+Select *O.sativa* as preset plant and fill in the average Tleaf and Pa for each curve, generating guesses and fits, saving outputs as .png and csv tables.
 
-#### Generate guess and fit, saving output, png and table
+#### Calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko.
 
-#### Compare the fits found using complete sets of Sharkey's parameters for tobacco and Carmen's parameters for rice
+Make sure all constants are named differently within the function to what they are called outside the function.
 
-#### 11/12/2023
-
-#### We couldn't get a good estimate of Ko c and dHa via nls
-
-#### (As it was fitted with near zero residuals, should not have converged)
-
-##### It may be better to calculate a series of Ko values (one at each Tleaf) and pass them onto the fitting function
-
-#### But first- calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko
-
-#### Make sure all constants are named differently within the function to what they are called outside the function
-
-### Load data containing kinetic parameters for rice
+### Import data for Kc_c and Kc_dHa:
 
 ```{r}
-param_data <- read_excel("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Data/Rubisco_kinetics_Oryza_sativa.xlsx")
+Kc_c <- 38.9
+Kc_dHa <- 83.1
 ```
 
-### Import data for Kc_c and Kc_dHa
+### Import data for Kcair_c and Kcair_dHa:
 
 ```{r}
-Kc_c <- mean(na.omit(as.numeric(param_data$`c Kc (from μmolmol-1) (dimensionless)`))) 
-Kc_dHa <- mean(na.omit(as.numeric(param_data$`DHA Kc (from μmolmol-1) (KJmol-1)`)))
+Kcair_c <- 30.5 
+Kcair_dHa <- 60.5
 ```
 
-### Import data for Kcair_c and Kcair_dHa
-
-```{r}
-Kcair_c <- mean(na.omit(as.numeric(param_data$`c Kcair (from μmolmol-1) (dimensionless)`))) 
-Kcair_dHa <- mean(na.omit(as.numeric(param_data$`DHA Kcair (from μmolmol-1) (KJmol-1)`)))
-```
-
-### Write function to use the mean temperature in celsius from each curve for calculating Kc and Kcair
+### Write function to use the mean temperature in celsius from each curve for calculating Kc and Kcair:
 
@@
 
-### Create an empty dataframe to store all Kc and Kcair outputs
+### Create an empty dataframe to store all Kc and Kcair outputs:
 
@@
 
-### Loop through kinetic_params function, calculate Kc and Ko values at each temperature in mean_temps and convert values from ppm to Pa according to each mean_press
+### Loop through kinetic_params function, calculate Kc and Ko values at each temperature in mean_temps and convert values from ppm to Pa according to each mean_press:
 
@@
 
-### Append a column for calculating Ko from Kc and Kcair and converting these values to kPa
+### Append a column for calculating Ko from Kc and Kcair and converting these values to kPa:
 
@@
 all_param$Press <- mean_press 
-write.csv(all_param,file = "C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
+write.csv(all_param,
+         file = "Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
 ```
@@
 
-### Initialise an empty list to store output of fitComplete
+### Initialise an empty list to store output of fitComplete:
 
@@
 
-### Fit curves individually using fitComplete algorithm
+### Fit curves individually using fitComplete algorithm:
 
@@
 
-### Save parameter outputs
-
-```{r}
-write.csv(completeFit1_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")
-```
-
 ```{r}
@@
                                  Ko = all_param[2, "Ko"]) 
-```
-
-### Save parameter outputs
-
-```{r}
-write.csv(completeFit2_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")
 ```
@@
 
-### Save parameter
-
-```{r}
-write.csv(completeFit3_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")
-```
-
 ```{r}
@@
                                  Ko = all_param[4, "Ko"]) 
-```
-
-### Save parameter outputs
-
-```{r}
-write.csv(completeFit4_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")
 ```
@@
 
-### Save parameter outputs
-
-```{r}
-write.csv(completeFit5_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")
-```
-
 ```{r}
@@
                                  Ko = all_param[6, "Ko"]) 
-```
-
-### Save parameter outputs
-
-```{r}
-write.csv(completeFit6_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")
 ```
@@
 
-### Save parameter outputs
-
-```{r}
-write.csv(completeFit7_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")
-```
-
 ```{r}
@@
 
-### Save parameter outputs
+### Save parameter outputs:
 
 ```{r}
-write.csv(completeFit8_rice[[1]], file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
+write.csv(completeFit1_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")
+
+write.csv(completeFit2_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")
+
+write.csv(completeFit3_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")
+
+write.csv(completeFit4_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")
+
+write.csv(completeFit5_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")
+
+write.csv(completeFit6_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")
+
+write.csv(completeFit7_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")
+
+write.csv(completeFit8_rice[[1]], 
+          file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
 ```
 
-## Produce data tables for each curve
+## Produce data tables for each curve:
 
 ```{r}
-completeTables1_rice <- reconstituteTable(data=A330502WT1, fitParams = completeFit1_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[1], O2=21, pressure=mean_press[(1)], tleaf = mean_temps[(1)], ignoreTPU=F, Kc=all_param[1, "Kc"], Ko=all_param[1, "Ko"])
+completeTables1_rice <- reconstituteTable(data=A330502WT1, 
+                                          fitParams = completeFit1_rice[[1]],
+                                          name_assimilation = "Photo", 
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[1],
+                                          O2=21, 
+                                          pressure=mean_press[(1)], 
+                                          tleaf = mean_temps[(1)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[1, "Kc"], 
+                                          Ko=all_param[1, "Ko"])
 
+completeTables2_rice <- reconstituteTable(data=A330502WT2, 
+                                          fitParams = completeFit2_rice[[1]], 
+                                          name_assimilation = "Photo", 
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[2], 
+                                          O2=21, 
+                                          pressure=mean_press[(2)], 
+                                          tleaf = mean_temps[(2)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[2, "Kc"],
+                                          Ko=all_param[2, "Ko"])
+
+completeTables3_rice <- reconstituteTable(data=A330504WT1, 
+                                          fitParams = completeFit3_rice[[1]], 
+                                          name_assimilation = "Photo", 
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[3], 
+                                          O2=21, 
+                                          pressure=mean_press[(3)], 
+                                          tleaf = mean_temps[(3)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[3, "Kc"], 
+                                          Ko=all_param[3, "Ko"])
+
+completeTables4_rice <- reconstituteTable(data=A330504WT2, 
+                                          fitParams = completeFit4_rice[[1]], 
+                                          name_assimilation = "Photo",
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[4], 
+                                          O2=21, 
+                                          pressure=mean_press[(4)], 
+                                          tleaf = mean_temps[(4)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[4, "Kc"], 
+                                          Ko=all_param[4, "Ko"])
+
+completeTables5_rice <- reconstituteTable(data=A330506WT1, 
+                                          fitParams = completeFit5_rice[[1]], 
+                                          name_assimilation = "Photo", 
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[5], 
+                                          O2=21, 
+                                          pressure=mean_press[(5)], 
+                                          tleaf = mean_temps[(5)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[5, "Kc"], 
+                                          Ko=all_param[5, "Ko"])
+
+completeTables6_rice <- reconstituteTable(data=A330506WT2, 
+                                          fitParams = completeFit6_rice[[1]], 
+                                          name_assimilation = "Photo", 
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[6], 
+                                          O2=21, 
+                                          pressure=mean_press[(6)], 
+                                          tleaf = mean_temps[(6)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[6, "Kc"], 
+                                          Ko=all_param[6, "Ko"])
+
+completeTables7_rice <- reconstituteTable(data=A330509WT1, 
+                                          fitParams = completeFit7_rice[[1]], 
+                                          name_assimilation = "Photo", 
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[7], 
+                                          O2=21, 
+                                          pressure=mean_press[(7)], 
+                                          tleaf = mean_temps[(7)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[7, "Kc"], 
+                                          Ko=all_param[7, "Ko"])
+
+completeTables8_rice <- reconstituteTable(data=A330509WT2, 
+                                          fitParams = completeFit8_rice[[1]], 
+                                          name_assimilation = "Photo", 
+                                          name_ci=c("Ci"), 
+                                          gammastar=Gstars_Pa_rice[8], 
+                                          O2=21, 
+                                          pressure=mean_press[(8)], 
+                                          tleaf = mean_temps[(8)], 
+                                          ignoreTPU=F, 
+                                          Kc=all_param[8, "Kc"], 
+                                          Ko=all_param[8, "Ko"])
 ```
 
-### Save data table
+### Save data tables:
 
 ```{r}
-write.csv(completeTables1_rice, file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
+write.csv(completeTables1_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
+write.csv(completeTables2_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv")
+write.csv(completeTables3_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") 
+write.csv(completeTables4_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv")
+write.csv(completeTables5_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv")
+write.csv(completeTables6_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") 
+write.csv(completeTables7_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv")
+write.csv(completeTables8_rice, 
+          file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") 
 ```
 
-`{SSR1<-sum(completeTables1_rice$res^2)}`
-
-### Plot graph of limitations
+### Plot graphs of limitations:
 
@@
                                          Ko=all_param[1, "Ko"])
+
+completeGraph2_rice <- reconstituteGraph(data=A330502WT2, 
+                                         fitParams = completeFit2_rice[[1]], 
+                                         name_assimilation="Photo", name_ci=("Ci"), 
+                                         gammastar=Gstars_Pa_rice[2], O2=21, 
+                                         pressure=mean_press[(2)], tleaf=mean_temps[(2)], 
+                                         ignoreTPU=F,
+                                         Kc=all_param[2, "Kc"], 
+                                         Ko=all_param[2, "Ko"])
+
+completeGraph3_rice <- reconstituteGraph(data=A330504WT1, 
+                                         fitParams = completeFit3_rice[[1]], 
+                                         name_assimilation="Photo", 
+                                         name_ci=("Ci"), 
+                                         gammastar=Gstars_Pa_rice[3], 
+                                         O2=21, 
+                                         pressure=mean_press[(3)], 
+                                         tleaf=mean_temps[(3)], 
+                                         ignoreTPU=F, 
+                                         Kc=all_param[3, "Kc"], 
+                                         Ko=all_param[3, "Ko"])
+
+completeGraph4_rice <- reconstituteGraph(data=A330504WT2, 
+                                         fitParams = completeFit4_rice[[1]], 
+                                         name_assimilation="Photo", 
+                                         name_ci=("Ci"), 
+                                         gammastar=Gstars_Pa_rice[4],
+                                         O2=21, 
+                                         pressure=mean_press[(4)], 
+                                         tleaf=mean_temps[(4)], 
+                                         ignoreTPU=F, 
+                                         Kc=all_param[4, "Kc"], 
+                                         Ko=all_param[4, "Ko"])
+
+completeGraph5_rice <- reconstituteGraph(data=A330506WT1, 
+                                         fitParams = completeFit5_rice[[1]], 
+                                         name_assimilation="Photo", 
+                                         name_ci=("Ci"), 
+                                         gammastar=Gstars_Pa_rice[5],
+                                         O2=21, 
+                                         pressure=mean_press[(5)], 
+                                         tleaf=mean_temps[(5)], 
+                                         ignoreTPU=F, 
+                                         Kc=all_param[5, "Kc"], 
+                                         Ko=all_param[5, "Ko"])
+
+completeGraph6_rice <- reconstituteGraph(data=A330506WT2, 
+                                         fitParams = completeFit6_rice[[1]], 
+                                         name_assimilation="Photo", 
+                                         name_ci=("Ci"), 
+                                         gammastar=Gstars_Pa_rice[6],
+                                         O2=21, 
+                                         pressure=mean_press[(6)], 
+                                         tleaf=mean_temps[(6)], 
+                                         ignoreTPU=F, 
+                                         Kc=all_param[6, "Kc"], 
+                                         Ko=all_param[6, "Ko"])
+
+completeGraph7_rice <- reconstituteGraph(data=A330509WT1, 
+                                         fitParams = completeFit7_rice[[1]], 
+                                         name_assimilation="Photo", 
+                                         name_ci=("Ci"), 
+                                         gammastar=Gstars_Pa_rice[7],
+                                         O2=21, 
+                                         pressure=mean_press[(7)], 
+                                         tleaf=mean_temps[(7)], 
+                                         ignoreTPU=F, 
+                                         Kc=all_param[7, "Kc"], 
+                                         Ko=all_param[7, "Ko"])
+
+completeGraph8_rice <- reconstituteGraph(data=A330509WT2, 
+                                         fitParams = completeFit8_rice[[1]], 
+                                         name_assimilation="Photo", 
+                                         name_ci=("Ci"), 
+                                         gammastar=Gstars_Pa_rice[8],
+                                         O2=21,
+                                         pressure=mean_press[(8)], 
+                                         tleaf=mean_temps[(8)], 
+                                         ignoreTPU=F, 
+                                         Kc=all_param[8, "Kc"], 
+                                         Ko=all_param[8, "Ko"]) 
 ```
 
+### Save plots:
+
 ```{r}
-#png("C:/Users/vijayak2/OneDrive - Lancaster University/Code/Rice/IRRI_data/msuRACiFit/third/Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
+png("Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
 plot(completeGraph1_rice) 
-#dev.off()
+dev.off()
+
+png("Outputs/Graphs/fitComplete/Rice/completefits2_console_rice.png", width = 519, height = 457) 
+plot(completeGraph2_rice) 
+dev.off()
+
+png("Outputs/Graphs/fitComplete/Rice/completefits3_console_rice.png", width = 519, height = 457) 
+plot(completeGraph3_rice) 
+dev.off()
+
+png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) 
+plot(completeGraph4_rice) 
+dev.off()
+
+png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) 
+plot(completeGraph5_rice) 
+dev.off()
+
+png("Outputs/Graphs/fitComplete/Rice/completefits6_console_rice.png", width = 519, height = 457) 
+plot(completeGraph6_rice) 
+dev.off()
+
+png("Outputs/Graphs/fitComplete/Rice/completefits7_console_rice.png", width = 519, height = 457) 
+plot(completeGraph7_rice) 
+dev.off()
+
+png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) 
+plot(completeGraph8_rice) 
+dev.off()
 ```
 
-completeTables2_rice \<- reconstituteTable(data=A330502WT2, fitParams = completeFit2_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[2], O2=21, pressure=mean_press[(2)], tleaf = mean_temps[(2)], ignoreTPU=F, Kc=all_param[2, "Kc"], Ko=all_param[2, "Ko"]) #Save data table write.csv(completeTables2_rice, file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv") SSR2\<-sum(completeTables2_rice\$`res^2`)
+#### Calculate sum of squared residuals:
 
-completeGraph2_rice \<- reconstituteGraph(data=A330502WT2, fitParams = completeFit2_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[2], O2=21, pressure=mean_press[(2)], tleaf=mean_temps[(2)], ignoreTPU=F, Kc=all_param[2, "Kc"], Ko=all_param[2, "Ko"])
+```{r}
+SSR1<-sum(completeTables1_rice$res^2)
+SSR2<-sum(completeTables2_rice$res^2)
+SSR3<-sum(completeTables3_rice$res^2)
+SSR4<-sum(completeTables4_rice$res^2)
+SSR5<-sum(completeTables5_rice$res^2)
+SSR6<-sum(completeTables6_rice$res^2)
+SSR7<-sum(completeTables7_rice$res^2)
+SSR8<-sum(completeTables8_rice$res^2)
+```
 
-png("Outputs/Graphs/fitComplete/Rice/completefits2_console_rice.png", width = 519, height = 457) plot(completeGraph2_rice) dev.off()
-
-completeTables3_rice \<- reconstituteTable(data=A330504WT1, fitParams = completeFit3_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[3], O2=21, pressure=mean_press[(3)], tleaf = mean_temps[(3)], ignoreTPU=F, Kc=all_param[3, "Kc"], Ko=all_param[3, "Ko"]) #Save data table write.csv(completeTables3_rice, file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") SSR3\<-sum(completeTables3_rice\$`res^2`)
-
-completeGraph3_rice \<- reconstituteGraph(data=A330504WT1, fitParams = completeFit3_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[3], O2=21, pressure=mean_press[(3)], tleaf=mean_temps[(3)], ignoreTPU=F, Kc=all_param[3, "Kc"], Ko=all_param[3, "Ko"])
-
-png("Outputs/Graphs/fitComplete/Rice/completefits3_console_rice.png", width = 519, height = 457) plot(completeGraph3_rice) dev.off()
-
-completeTables4_rice \<- reconstituteTable(data=A330504WT2, fitParams = completeFit4_rice[[1]], name_assimilation = "Photo",name_ci=c("Ci"), gammastar=Gstars_Pa_rice[4], O2=21, pressure=mean_press[(4)], tleaf = mean_temps[(4)], ignoreTPU=F, Kc=all_param[4, "Kc"], Ko=all_param[4, "Ko"]) #Save data table write.csv(completeTables4_rice, file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv") SSR4\<-sum(completeTables4_rice\$`res^2`)
-
-completeGraph4_rice \<- reconstituteGraph(data=A330504WT2, fitParams = completeFit4_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[4], O2=21, pressure=mean_press[(4)], tleaf=mean_temps[(4)], ignoreTPU=F, Kc=all_param[4, "Kc"], Ko=all_param[4, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) plot(completeGraph4_rice) dev.off()
-
-completeTables5_rice \<- reconstituteTable(data=A330506WT1, fitParams = completeFit5_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[5], O2=21, pressure=mean_press[(5)], tleaf = mean_temps[(5)], ignoreTPU=F, Kc=all_param[5, "Kc"], Ko=all_param[5, "Ko"]) #Save data table write.csv(completeTables5_rice, file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv") SSR5\<-sum(completeTables5_rice\$`res^2`)
-
-completeGraph5_rice \<- reconstituteGraph(data=A330506WT1, fitParams = completeFit5_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[5], O2=21, pressure=mean_press[(5)], tleaf=mean_temps[(5)], ignoreTPU=F, Kc=all_param[5, "Kc"], Ko=all_param[5, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) plot(completeGraph5_rice) dev.off()
-
-completeTables6_rice \<- reconstituteTable(data=A330506WT2, fitParams = completeFit6_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[6], O2=21, pressure=mean_press[(6)], tleaf = mean_temps[(6)], ignoreTPU=F, Kc=all_param[6, "Kc"], Ko=all_param[6, "Ko"]) #Save data table write.csv(completeTables6_rice, file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") SSR6\<-sum(completeTables6_rice\$`res^2`)
-
-completeGraph6_rice \<- reconstituteGraph(data=A330506WT2, fitParams = completeFit6_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[6], O2=21, pressure=mean_press[(6)], tleaf=mean_temps[(6)], ignoreTPU=F, Kc=all_param[6, "Kc"], Ko=all_param[6, "Ko"])
-
-png("Outputs/Graphs/fitComplete/Rice/completefits6_console_rice.png", width = 519, height = 457) plot(completeGraph6_rice) dev.off()
-
-completeTables7_rice \<- reconstituteTable(data=A330509WT1, fitParams = completeFit7_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[7], O2=21, pressure=mean_press[(7)], tleaf = mean_temps[(7)], ignoreTPU=F, Kc=all_param[7, "Kc"], Ko=all_param[7, "Ko"]) #Save data table write.csv(completeTables7_rice, file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv") SSR7\<-sum(completeTables7_rice\$`res^2`)
-
-completeGraph7_rice \<- reconstituteGraph(data=A330509WT1, fitParams = completeFit7_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[7], O2=21, pressure=mean_press[(7)], tleaf=mean_temps[(7)], ignoreTPU=F, Kc=all_param[7, "Kc"], Ko=all_param[7, "Ko"])
-
-png("Outputs/Graphs/fitComplete/Rice/completefits7_console_rice.png", width = 519, height = 457) plot(completeGraph7_rice) dev.off()
-
-completeTables8_rice \<- reconstituteTable(data=A330509WT2, fitParams = completeFit8_rice[[1]], name_assimilation = "Photo", name_ci=c("Ci"), gammastar=Gstars_Pa_rice[8], O2=21, pressure=mean_press[(8)], tleaf = mean_temps[(8)], ignoreTPU=F, Kc=all_param[8, "Kc"], Ko=all_param[8, "Ko"]) #Save data table write.csv(completeTables8_rice, file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") SSR8\<-sum(completeTables8_rice\$`res^2`)
-
-completeGraph8_rice \<- reconstituteGraph(data=A330509WT2, fitParams = completeFit8_rice[[1]], name_assimilation="Photo", name_ci=("Ci"), gammastar=Gstars_Pa_rice[8], O2=21,pressure=mean_press[(8)], tleaf=mean_temps[(8)], ignoreTPU=F, Kc=all_param[8, "Kc"], Ko=all_param[8, "Ko"]) png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) plot(completeGraph8_rice) dev.off()
-
-### Combine and save SSR
+### Combine and save SSR values:
 
@@
 SSR_values <- data.frame(SSR1,SSR2,SSR3,SSR4,SSR5,SSR6,SSR7,SSR8) 
-write.csv(SSR_values, file = "Outputs/Parameters/fitComplete/Rice/rice_console_SSR_values.csv", row.names = FALSE)
+write.csv(SSR_values, 
+          file = "Outputs/Parameters/fitComplete/Rice/rice_console_SSR_values.csv", 
+          row.names = FALSE)
 ```
 
-### Export plot coordinates for limitations, example below (consider looping)
+### Export plot coordinates for limitations, example below:
 
@@
 limitations <- list(Ac,Aj,Ap)
+
 write.csv(limitations,"Outputs/Tables/fitComplete/Rice/completeFit1_rice_limitations.csv")

### 2025-05-12 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Add files via upload

@@
 ---
-title: "msuRACiFits_fits_rice_params"
+title: "msuRACiFits_fits_rice"
 author: "Supreeta Vijayakumar"
@@
 Using \`here' roots the file path to the project environment.
+
+### Specify an output directory:
+
+```{r}
+base_path <- here("Outputs", "Parameters")
+```
 
@@
 ```{r}
-write.csv(Gstars_rice,file = "Outputs/Parameters/Gstars_rice.csv") #ppm
+Gstars_rice_file <- file.path(base_path, "Gstars_rice.csv")
+write.csv(Gstars_rice,Gstars_rice_file) #ppm
 ```
@@
 ```{r}
-write.csv(Gstars_Pa_rice,file = "Outputs/Parameters/Gstars_Pa_rice.csv") #Pa
+Gstars_Pa_rice_file <- file.path(base_path, "Gstars_Pa_rice.csv")
+write.csv(Gstars_Pa_rice,Gstars_Pa_rice_file) #Pa
 ```
@@
 ```{r}
-msuRACiFit::genApp()
+# msuRACiFit::genApp()
 ```
@@
 
-### Import data for Kc_c and Kc_dHa:
+### Import data for Kc_c and Kc_dHa (from Hermida-Carrera et al, 2016):
 
 ```{r}
-Kc_c <- 38.9
-Kc_dHa <- 83.1
+Kc_c <- 38.9   # unitless
+Kc_dHa <- 83.1 # kJ mol -1
 ```
 
-### Import data for Kcair_c and Kcair_dHa:
+### Import data for Kcair_c and Kcair_dHa from Hermida-Carrera et al, 2016:
 
 ```{r}
-Kcair_c <- 30.5 
-Kcair_dHa <- 60.5
+Kcair_c <- 30.5   # unitless
+Kcair_dHa <- 60.5 # kJ mol -1
 ```
@@
 all_param$Press <- mean_press
-write.csv(all_param,
-         file = "Outputs/Parameters/fitComplete/Rice/kinetic_parameters_rice.csv")
+
+all_param_file <- file.path(base_path, "kinetic_parameters_rice.csv")
+write.csv(all_param,all_param_file)
 ```
@@
   data_k <- datasets[[k]]
-  if ("data" %in% colnames(data_k)) {
+    if (hasName(data_k, "data")) {
     data_k <- data_k$data
@@
 
-### Fit curves individually using fitComplete algorithm:
+## Save parameter outputs:
 
 ```{r}
-completeFit1_rice <- fitComplete(A330502WT1, 
+for (o in seq_along(complete_Fits_rice_list)) {
+  filename <- sprintf("completeFits_rice_params_%d.csv", o)
+  output_filename <- file.path(base_path,filename)
+  write.csv(complete_Fits_rice_list[[o]][[1]], 
+            file = output_filename, 
+            row.names = FALSE)
+}
+```
+
+### Initialise an empty list to store table outputs and sums of squared residuals:
+
+```{r}
+complete_Tables_rice_list <- vector("list", length(datasets))
+SSR <- numeric(length(complete_Tables_rice_list))
+```
+
+## Produce data tables using parameters fitted for each curve and the SSR assoaciated with each fit:
+
+```{r}
+    for (k in seq_along(datasets)) {  
+    data_k <- datasets[[k]]
+      if (hasName(data_k, "data")) {
+      data_k <- data_k$data
+    }
+  data_k <- as.data.frame(data_k)
+
+    complete_Tables_rice <- reconstituteTable(
+    data = data_k,  
+    fitParams = complete_Fits_rice_list[[k]][[1]],
     name_assimilation = "Photo",
     name_ci = "Ci",
-                                gammastar = Gstars_Pa_rice[1], 
+    gammastar = Gstars_Pa_rice[k],
     O2 = 21,
-                                pressure = mean_press[1], 
-                                tleaf = mean_temps[1], 
-                                initialGuess = NA,
-                                forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
-                                bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                ignoreTPU = F, 
-                                maxiter = 500, 
-                                Kc = all_param[1, "Kc"], 
-                                Ko = all_param[1, "Ko"]) 
-```
+    pressure=mean_press[(k)], 
+    tleaf = mean_temps[(k)], 
+    ignoreTPU=F, 
+    Kc=all_param[k, "Kc"], 
+    Ko=all_param[k, "Ko"])
 
-```{r}
-completeFit2_rice <- fitComplete(A330502WT2, 
-                                 name_assimilation = "Photo", 
-                                 name_ci = "Ci", 
-                                 gammastar = Gstars_Pa_rice[2], 
-                                 O2 = 21, 
-                                 pressure = mean_press[2], 
-                                 tleaf = mean_temps[2], 
-                                 initialGuess = NA, 
-                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA),
-                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                 ignoreTPU = F, maxiter = 500, 
-                                 Kc = all_param[2, "Kc"], 
-                                 Ko = all_param[2, "Ko"]) 
-```
-
-```{r}
-completeFit3_rice <- fitComplete(A330504WT1, 
-                                 name_assimilation = "Photo", 
-                                 name_ci = "Ci", 
-                                 gammastar = Gstars_Pa_rice[3], 
-                                 O2 = 21, 
-                                 pressure = mean_press[3], 
-                                 tleaf = mean_temps[3], 
-                                 initialGuess = NA, 
-                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
-                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                 ignoreTPU = F, 
-                                 maxiter = 500, 
-                                 Kc = all_param[3, "Kc"], 
-                                 Ko = all_param[3, "Ko"]) 
-```
-
-```{r}
-completeFit4_rice <- fitComplete(A330504WT2, 
-                                 name_assimilation = "Photo", 
-                                 name_ci = "Ci", 
-                                 gammastar = Gstars_Pa_rice[4], 
-                                 O2 = 21, 
-                                 pressure = mean_press[4], 
-                                 tleaf = mean_temps[4], 
-                                 initialGuess = NA, 
-                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
-                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                 ignoreTPU = F, 
-                                 maxiter = 500, 
-                                 Kc = all_param[4, "Kc"], 
-                                 Ko = all_param[4, "Ko"]) 
-```
-
-```{r}
-completeFit5_rice <- fitComplete(A330506WT1, 
-                                 name_assimilation = "Photo", 
-                                 name_ci = "Ci", 
-                                 gammastar = Gstars_Pa_rice[5], 
-                                 O2 = 21, 
-                                 pressure = mean_press[5], 
-                                 tleaf = mean_temps[5], 
-                                 initialGuess = NA, 
-                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
-                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                 ignoreTPU = F, 
-                                 maxiter = 500, 
-                                 Kc = all_param[5, "Kc"], 
-                                 Ko = all_param[5, "Ko"])
-```
-
-```{r}
-completeFit6_rice <- fitComplete(A330506WT2, 
-                                 name_assimilation = "Photo", 
-                                 name_ci = "Ci", 
-                                 gammastar = Gstars_Pa_rice[6], 
-                                 O2 = 21, 
-                                 pressure = mean_press[6], 
-                                 tleaf = mean_temps[6], 
-                                 initialGuess = NA, 
-                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
-                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                 ignoreTPU = F, 
-                                 maxiter = 500, 
-                                 Kc = all_param[6, "Kc"], 
-                                 Ko = all_param[6, "Ko"]) 
-```
-
-```{r}
-completeFit7_rice <- fitComplete(A330509WT1, 
-                                 name_assimilation = "Photo", 
-                                 name_ci = "Ci", 
-                                 gammastar = Gstars_Pa_rice[7], 
-                                 O2 = 21, 
-                                 pressure = mean_press[7], 
-                                 tleaf = mean_temps[7], 
-                                 initialGuess = NA, 
-                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
-                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                 ignoreTPU = F, 
-                                 maxiter = 500, 
-                                 Kc = all_param[7, "Kc"], 
-                                 Ko = all_param[7, "Ko"]) 
-```
-
-```{r}
-completeFit8_rice <- fitComplete(A330509WT2, 
-                                 name_assimilation = "Photo", 
-                                 name_ci = "Ci", 
-                                 gammastar = Gstars_Pa_rice[8], 
-                                 O2 = 21, pressure = mean_press[8], 
-                                 tleaf = mean_temps[8], 
-                                 initialGuess = NA, 
-                                 forceValues = c(NA, NA, NA, NA, NA, NA, NA), 
-                                 bound_l = c(1, 1, 1, .001, .001, 0, 0), 
-                                 bound_h = c(1000, 1000, 1000, 30, 10, 1, .75), 
-                                 ignoreTPU = F, 
-                                 maxiter = 500, 
-                                 Kc = all_param[8, "Kc"], 
-                                 Ko = all_param[8, "Ko"]) 
-```
-
-### Save parameter outputs:
-
-```{r}
-write.csv(completeFit1_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit1_console_rice_params.csv")
-
-write.csv(completeFit2_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit2_console_rice_params.csv")
-
-write.csv(completeFit3_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit3_console_rice_params.csv")
-
-write.csv(completeFit4_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit4_console_rice_params.csv")
-
-write.csv(completeFit5_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit5_console_rice_params.csv")
-
-write.csv(completeFit6_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit6_console_rice_params.csv")
-
-write.csv(completeFit7_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit7_console_rice_params.csv")
-
-write.csv(completeFit8_rice[[1]], 
-          file = "Outputs/Parameters/fitComplete/Rice/completefit8_console_rice_params.csv")
-```
-
-## Produce data tables for each curve:
-
-```{r}
-completeTables1_rice <- reconstituteTable(data=A330502WT1, 
-                                          fitParams = completeFit1_rice[[1]],
-                                          name_assimilation = "Photo", 
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[1],
-                                          O2=21, 
-                                          pressure=mean_press[(1)], 
-                                          tleaf = mean_temps[(1)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[1, "Kc"], 
-                                          Ko=all_param[1, "Ko"])
-
-completeTables2_rice <- reconstituteTable(data=A330502WT2, 
-                                          fitParams = completeFit2_rice[[1]], 
-                                          name_assimilation = "Photo", 
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[2], 
-                                          O2=21, 
-                                          pressure=mean_press[(2)], 
-                                          tleaf = mean_temps[(2)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[2, "Kc"],
-                                          Ko=all_param[2, "Ko"])
-
-completeTables3_rice <- reconstituteTable(data=A330504WT1, 
-                                          fitParams = completeFit3_rice[[1]], 
-                                          name_assimilation = "Photo", 
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[3], 
-                                          O2=21, 
-                                          pressure=mean_press[(3)], 
-                                          tleaf = mean_temps[(3)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[3, "Kc"], 
-                                          Ko=all_param[3, "Ko"])
-
-completeTables4_rice <- reconstituteTable(data=A330504WT2, 
-                                          fitParams = completeFit4_rice[[1]], 
-                                          name_assimilation = "Photo",
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[4], 
-                                          O2=21, 
-                                          pressure=mean_press[(4)], 
-                                          tleaf = mean_temps[(4)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[4, "Kc"], 
-                                          Ko=all_param[4, "Ko"])
-
-completeTables5_rice <- reconstituteTable(data=A330506WT1, 
-                                          fitParams = completeFit5_rice[[1]], 
-                                          name_assimilation = "Photo", 
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[5], 
-                                          O2=21, 
-                                          pressure=mean_press[(5)], 
-                                          tleaf = mean_temps[(5)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[5, "Kc"], 
-                                          Ko=all_param[5, "Ko"])
-
-completeTables6_rice <- reconstituteTable(data=A330506WT2, 
-                                          fitParams = completeFit6_rice[[1]], 
-                                          name_assimilation = "Photo", 
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[6], 
-                                          O2=21, 
-                                          pressure=mean_press[(6)], 
-                                          tleaf = mean_temps[(6)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[6, "Kc"], 
-                                          Ko=all_param[6, "Ko"])
-
-completeTables7_rice <- reconstituteTable(data=A330509WT1, 
-                                          fitParams = completeFit7_rice[[1]], 
-                                          name_assimilation = "Photo", 
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[7], 
-                                          O2=21, 
-                                          pressure=mean_press[(7)], 
-                                          tleaf = mean_temps[(7)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[7, "Kc"], 
-                                          Ko=all_param[7, "Ko"])
-
-completeTables8_rice <- reconstituteTable(data=A330509WT2, 
-                                          fitParams = completeFit8_rice[[1]], 
-                                          name_assimilation = "Photo", 
-                                          name_ci=c("Ci"), 
-                                          gammastar=Gstars_Pa_rice[8], 
-                                          O2=21, 
-                                          pressure=mean_press[(8)], 
-                                          tleaf = mean_temps[(8)], 
-                                          ignoreTPU=F, 
-                                          Kc=all_param[8, "Kc"], 
-                                          Ko=all_param[8, "Ko"])
+  complete_Tables_rice_list[[k]] <- complete_Tables_rice
+  SSR[k] <- sum(complete_Tables_rice_list[[k]]$`res^2`)
+}
 ```
@@
 ```{r}
-write.csv(completeTables1_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit1_console_rice_dataTable.csv") 
-write.csv(completeTables2_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit2_console_rice_dataTable.csv")
-write.csv(completeTables3_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit3_console_rice_dataTable.csv") 
-write.csv(completeTables4_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit4_console_rice_dataTable.csv")
-write.csv(completeTables5_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit5_console_rice_dataTable.csv")
-write.csv(completeTables6_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit6_console_rice_dataTable.csv") 
-write.csv(completeTables7_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit7_console_rice_dataTable.csv")
-write.csv(completeTables8_rice, 
-          file = "Outputs/Tables/fitComplete/Rice/completefit8_console_rice_dataTable.csv") 
+for (p in seq_along(complete_Tables_rice_list)) {
+  filename <- sprintf("completeFits_rice_dataTable_%d.csv", p)
+  output_filename <- file.path(base_path,filename)
+  write.csv(complete_Tables_rice_list[[p]], 
+            file = output_filename, 
+            row.names = FALSE)
+}
 ```
 
-### Plot graphs of limitations:
+### Save SSR values:
 
 ```{r}
-completeGraph1_rice <- reconstituteGraph(data=A330502WT1, 
-                                         fitParams = completeFit1_rice[[1]], 
-                                         name_assimilation="Photo", 
-                                         name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[1], 
-                                         O2=21, 
-                                         pressure=mean_press[(1)], 
-                                         tleaf=mean_temps[(1)], 
-                                         ignoreTPU=F, 
-                                         Kc=all_param[1, "Kc"], 
-                                         Ko=all_param[1, "Ko"])
-
-completeGraph2_rice <- reconstituteGraph(data=A330502WT2, 
-                                         fitParams = completeFit2_rice[[1]], 
-                                         name_assimilation="Photo", name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[2], O2=21, 
-                                         pressure=mean_press[(2)], tleaf=mean_temps[(2)], 
-                                         ignoreTPU=F,
-                                         Kc=all_param[2, "Kc"], 
-                                         Ko=all_param[2, "Ko"])
-
-completeGraph3_rice <- reconstituteGraph(data=A330504WT1, 
-                                         fitParams = completeFit3_rice[[1]], 
-                                         name_assimilation="Photo", 
-                                         name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[3], 
-                                         O2=21, 
-                                         pressure=mean_press[(3)], 
-                                         tleaf=mean_temps[(3)], 
-                                         ignoreTPU=F, 
-                                         Kc=all_param[3, "Kc"], 
-                                         Ko=all_param[3, "Ko"])
-
-completeGraph4_rice <- reconstituteGraph(data=A330504WT2, 
-                                         fitParams = completeFit4_rice[[1]], 
-                                         name_assimilation="Photo", 
-                                         name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[4],
-                                         O2=21, 
-                                         pressure=mean_press[(4)], 
-                                         tleaf=mean_temps[(4)], 
-                                         ignoreTPU=F, 
-                                         Kc=all_param[4, "Kc"], 
-                                         Ko=all_param[4, "Ko"])
-
-completeGraph5_rice <- reconstituteGraph(data=A330506WT1, 
-                                         fitParams = completeFit5_rice[[1]], 
-                                         name_assimilation="Photo", 
-                                         name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[5],
-                                         O2=21, 
-                                         pressure=mean_press[(5)], 
-                                         tleaf=mean_temps[(5)], 
-                                         ignoreTPU=F, 
-                                         Kc=all_param[5, "Kc"], 
-                                         Ko=all_param[5, "Ko"])
-
-completeGraph6_rice <- reconstituteGraph(data=A330506WT2, 
-                                         fitParams = completeFit6_rice[[1]], 
-                                         name_assimilation="Photo", 
-                                         name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[6],
-                                         O2=21, 
-                                         pressure=mean_press[(6)], 
-                                         tleaf=mean_temps[(6)], 
-                                         ignoreTPU=F, 
-                                         Kc=all_param[6, "Kc"], 
-                                         Ko=all_param[6, "Ko"])
-
-completeGraph7_rice <- reconstituteGraph(data=A330509WT1, 
-                                         fitParams = completeFit7_rice[[1]], 
-                                         name_assimilation="Photo", 
-                                         name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[7],
-                                         O2=21, 
-                                         pressure=mean_press[(7)], 
-                                         tleaf=mean_temps[(7)], 
-                                         ignoreTPU=F, 
-                                         Kc=all_param[7, "Kc"], 
-                                         Ko=all_param[7, "Ko"])
-
-completeGraph8_rice <- reconstituteGraph(data=A330509WT2, 
-                                         fitParams = completeFit8_rice[[1]], 
-                                         name_assimilation="Photo", 
-                                         name_ci=("Ci"), 
-                                         gammastar=Gstars_Pa_rice[8],
-                                         O2=21,
-                                         pressure=mean_press[(8)], 
-                                         tleaf=mean_temps[(8)], 
-                                         ignoreTPU=F, 
-                                         Kc=all_param[8, "Kc"], 
-                                         Ko=all_param[8, "Ko"]) 
+SSR_file <- file.path(base_path, "SSR_values_rice.csv")
+write.csv(SSR,SSR_file)
 ```
 
-### Save plots:
+### Initialise an empty list to store graph outputs:
 
 ```{r}
-png("Outputs/Graphs/fitComplete/Rice/completefits1_console_rice.png", width = 519, height = 457) 
-plot(completeGraph1_rice) 
-dev.off()
-
-png("Outputs/Graphs/fitComplete/Rice/completefits2_console_rice.png", width = 519, height = 457) 
-plot(completeGraph2_rice) 
-dev.off()
-
-png("Outputs/Graphs/fitComplete/Rice/completefits3_console_rice.png", width = 519, height = 457) 
-plot(completeGraph3_rice) 
-dev.off()
-
-png("Outputs/Graphs/fitComplete/Rice/completefits4_console_rice.png", width = 519, height = 457) 
-plot(completeGraph4_rice) 
-dev.off()
-
-png("Outputs/Graphs/fitComplete/Rice/completefits5_console_rice.png", width = 519, height = 457) 
-plot(completeGraph5_rice) 
-dev.off()
-
-png("Outputs/Graphs/fitComplete/Rice/completefits6_console_rice.png", width = 519, height = 457) 
-plot(completeGraph6_rice) 
-dev.off()
-
-png("Outputs/Graphs/fitComplete/Rice/completefits7_console_rice.png", width = 519, height = 457) 
-plot(completeGraph7_rice) 
-dev.off()
-
-png("Outputs/Graphs/fitComplete/Rice/completefits8_console_rice.png", width = 519, height = 457) 
-plot(completeGraph8_rice) 
-dev.off()
+complete_Graphs_rice_list <- vector("list", length(datasets))
 ```
 
-#### Calculate sum of squared residuals:
+## Produce graphs of limitations using parameters fitted for each curve:
 
 ```{r}
-SSR1<-sum(completeTables1_rice$res^2)
-SSR2<-sum(completeTables2_rice$res^2)
-SSR3<-sum(completeTables3_rice$res^2)
-SSR4<-sum(completeTables4_rice$res^2)
-SSR5<-sum(completeTables5_rice$res^2)
-SSR6<-sum(completeTables6_rice$res^2)
-SSR7<-sum(completeTables7_rice$res^2)
-SSR8<-sum(completeTables8_rice$res^2)
+    for (k in seq_along(datasets)) {  
+    data_k <- datasets[[k]]
+      if (hasName(data_k, "data")) {
+      data_k <- data_k$data
+    }
+  data_k <- as.data.frame(data_k)
+
+    complete_Graphs_rice <- reconstituteGraph(
+    data = data_k,  
+    fitParams = complete_Fits_rice_list[[k]][[1]],
+    name_assimilation = "Photo",
+    name_ci = "Ci",
+    gammastar = Gstars_Pa_rice[k],
+    O2 = 21,
+    pressure=mean_press[(k)], 
+    tleaf = mean_temps[(k)], 
+    ignoreTPU=F, 
+    Kc=all_param[k, "Kc"], 
+    Ko=all_param[k, "Ko"])
+
+  complete_Graphs_rice_list[[k]] <- complete_Graphs_rice
+}
 ```
 
-### Combine and save SSR values:
+### Save graphs:
 
 ```{r}
-SSR_values <- data.frame(SSR1,SSR2,SSR3,SSR4,SSR5,SSR6,SSR7,SSR8) 
-write.csv(SSR_values, 
-          file = "Outputs/Parameters/fitComplete/Rice/rice_console_SSR_values.csv", 
-          row.names = FALSE)
+for (p in seq_along(complete_Graphs_rice_list)) {
+  filename <- sprintf("completefits_rice_Graph_%d.png", p)
+  output_filename <- file.path(base_path, filename)
+
+  png(output_filename, width = 519, height = 457)
+  plot(complete_Graphs_rice_list[[p]])
+  dev.off()
+}
 ```
 
-### Export plot coordinates for limitations, example below:
+### Create output for limitation data:
 
 ```{r}
-Ac<-completeGraph1_rice$plot_env$cdat 
-Aj<-completeGraph1_rice$plot_env$jdat 
-Ap<-completeGraph1_rice$plot_env$pdat 
-limitations <- list(Ac,Aj,Ap)
+limitations_list <- vector("list", length(complete_Graphs_rice_list))
+```
 
-write.csv(limitations,"Outputs/Tables/fitComplete/Rice/completeFit1_rice_limitations.csv")
+### Export plot coordinates for limitations:
+
+```{r}
+for (q in seq_along(complete_Graphs_rice_list)) {
+  graph <- complete_Graphs_rice_list[[q]]
+  Ac <- graph$plot_env$cdat
+  Aj <- graph$plot_env$jdat
+  Ap <- graph$plot_env$pdat
+
+  limitations_list[[q]] <- list(Ac, Aj, Ap)
+}
 ```
+
+### Write limitations to output file:
+
+```{r}
+limitations_file <- file.path(base_path, "completeFit_rice_limitations.csv")
+write.csv(limitations_list,limitations_file)
+```

### 2025-05-28 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Updated fitting script

@@
 ```{r}
-base_path <- here("Outputs", "Parameters")
+output_path <- here("Outputs", "Parameters")
 ```
@@
 
-### Calculate Gamma Star at different temperatures using calcGammaStar:
+Gamma Star can be calculated for different temperatures using the calcGammaStar function.
 
-```{r}
-msuRACiFit::calcGammaStar(c,dHa,tleaf,oxygen)
-```
+msuRACiFit uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.
 
-The tool uses preset in-vitro values from Hermida-Carrera et al (2016), where everything is presented in ppm, except for N. tabacum and A. thaliana.
+Since the A/Ci responses are analysed in Pa, the resulting Gamma\*, Kc and Ko must be adjusted from ppm to Pa units before running calculations.
 
-Since we are analyzing the A/Ci in Pa, we have to adjust the resulting Gamma\*, Kc and Ko that we get in ppm to Pa before running calculations.
-
-$c$ and $\Delta H_a$ for Gamma\* presented in the app/ preset table are for ppm, and gamma\* is corrected as follows:\
+$c$ and $\Delta H_a$ for Gamma\* presented in the app/ preset table are for ppm, and Gamma\* is corrected as follows:\
 \
@@
 
-### Call calcgammastar function with different temperature inputs and get outputs saved in single vector for 8 files:
+### Call the calcgammastar function with different temperature inputs and get outputs saved in a single vector for 8 files:
 
@@
 
-### Next, we account for the variation in Press for each dataset and converting GammaStar back to Pa:
+### Next, account for the variation in Press for each dataset and converting GammaStar back to Pa:
 
@@
 ```{r}
-Gstars_rice_file <- file.path(base_path, "Gstars_rice.csv")
+Gstars_rice_file <- file.path(output_path, "Gstars_rice.csv")
 write.csv(Gstars_rice,Gstars_rice_file) #ppm
@@
 ```{r}
-Gstars_Pa_rice_file <- file.path(base_path, "Gstars_Pa_rice.csv")
+Gstars_Pa_rice_file <- file.path(output_path, "Gstars_Pa_rice.csv")
 write.csv(Gstars_Pa_rice,Gstars_Pa_rice_file) #Pa
@@
 
-#### Calculate Kc and Kcair for our Tleaf values in umol mol-1 then convert them into Pa before working out Ko.
+#### Calculate Kc and Kcair for our Tleaf values in umol mol-1, then convert them into Pa before working out Ko.
 
@@
 
+### Call the kinetic_params function to calculate $K_{cair}$ in $umol \ mol^{-1}$ :
+
+```{r}
+Kcair_umol <- vector("list", length(mean_temps)) 
+for (j in seq_along(mean_temps)) { 
+    Kcair_umol[[j]] <- kinetic_params(mean_temps[j])[2]}
+```
+
+### Save Kcair and temperature values in .csv files:
+
+```{r}
+Kcair_file <- file.path(output_path, "Kcair_umol_rice.csv")
+temp_file <- file.path(output_path, "temps_rice.csv")
+
+write.csv(Kcair_umol, Kcair_file)
+write.csv(mean_temps,temp_file)
+```
+
 ### Append a column for calculating Ko from Kc and Kcair and converting these values to kPa:
@@
 all_param$Press <- mean_press
+```
 
-all_param_file <- file.path(base_path, "kinetic_parameters_rice.csv")
+### Save parameters in a file:
+
+```{r}
+all_param_file <- file.path(output_path, "kinetic_parameters_rice.csv")
 write.csv(all_param,all_param_file)
@@
   filename <- sprintf("completeFits_rice_params_%d.csv", o)
-  output_filename <- file.path(base_path,filename)
+  output_filename <- file.path(output_path,filename)
   write.csv(complete_Fits_rice_list[[o]][[1]], 
@@
 }
+```
+
+### Calculate $g_{m}$ in $umol \ m^{-2} \ s^{-1}$:
+
+```{r}
+gm_umol <- vector("list", length(mean_press)) 
+for (j in seq_along(mean_press)) { 
+    gm_umol[[j]] <- complete_Fits_rice_list[[j]][[1]]$gm*(mean_press[j]/1000)}
+```
+
+### Save gm values in a file:
+
+```{r}
+gm_file <- file.path(output_path, "gm_umol_rice.csv")
+write.csv(gm_umol,gm_file)
 ```
@@
 
-### Save data tables:
+### Save data tables in separate files:
 
@@
   filename <- sprintf("completeFits_rice_dataTable_%d.csv", p)
-  output_filename <- file.path(base_path,filename)
+  output_filename <- file.path(output_path,filename)
   write.csv(complete_Tables_rice_list[[p]], 
@@
 
+### Extract the parameter values from each list and combine them in a single dataframe, adding an identifier column 1-9 (based on k) as the first column:
+
+```{r}
+combined_results <- do.call(rbind, 
+                            lapply(seq_along(complete_Fits_rice_list), function(k) {
+  if(!is.null(complete_Fits_rice_list[[k]][[1]])) {
+    df <- complete_Fits_rice_list[[k]][[1]]  
+    df$Dataset_ID <- k  
+    df <- df[, c("Dataset_ID", 
+                 setdiff(names(df), 
+                         "Dataset_ID"))]  
+    return(df)
+  } else {
+    return(NULL)
+  }
+}))
+```
+
+### Save combined parameter values:
+
+```{r}
+parameters_file <- file.path(output_path, "complete_Fits_rice_params_all.csv")
+write.csv(combined_results,parameters_file)
+```
+
 ### Save SSR values:
@@
 ```{r}
-SSR_file <- file.path(base_path, "SSR_values_rice.csv")
+SSR_file <- file.path(output_path, "SSR_values_rice.csv")
 write.csv(SSR,SSR_file)
@@
   filename <- sprintf("completefits_rice_Graph_%d.png", p)
-  output_filename <- file.path(base_path, filename)
+  output_filename <- file.path(output_path, filename)
 
@@
 ```{r}
-limitations_file <- file.path(base_path, "completeFit_rice_limitations.csv")
+limitations_file <- file.path(output_path, "completeFit_rice_limitations.csv")
 write.csv(limitations_list,limitations_file)

### 2025-05-28 Plotting/plot_limitations_new.m
Add MATLAB Script for plotting A/Cc fits

@@ -1,0 +1,66 @@
+%% Plot A/Cc fits using limitations file
+%% Load data
+% Load limitations
+lim = readtable("completeFit_rice_limitations.csv"); % Limitation data
+ccVars = lim.Properties.VariableNames(startsWith(lim.Properties.VariableNames, 'Cc')); % Cc columns
+aVars  = lim.Properties.VariableNames(startsWith(lim.Properties.VariableNames, 'A')); % A columns
+
+% Load Gstar file
+gstar = readtable("Gstars_Pa_rice.csv");
+
+% Extract Gstar values
+Gstars = zeros(8,1);
+for i=1:numel(Gstars)
+    Gstars(i)= gstar{i,2};
+end
+
+% Extract data points by reading data from tables
+data = cell(1, 8);
+for j = 1:8
+    filename = sprintf('completeFits_rice_dataTable_%d.csv', j);
+    data{j} = readtable(filename);
+end
+
+%% Graph plotting - group of columns in lim
+nGroups = min(numel(ccVars), numel(aVars)) / 3;  % Columns per group
+nPlots = 3;     % Number of sets to plot (Cc/Ac, Cc/Aj, Cc/Ap)
+
+% Specify 4x2 layout for panel figure 
+fig = figure;
+t = tiledlayout(fig,4, 2, 'TileSpacing', 'Compact', 'Padding', 'Compact');
+
+for k = 0:(nGroups-1)
+    ax = nexttile;
+    
+    % Column names for each group k
+    ccCols = ccVars(k*3 + (1:3));
+    aCols  = aVars(k*3 + (1:3));
+
+    hold(ax, 'on');
+
+    % Plot limitation sets using column indices
+    p = scatter(ax,lim.(ccCols{1}), lim.(aCols{1}), 'filled', 'MarkerFaceColor', "#C00000");
+    q = scatter(ax,lim.(ccCols{2}), lim.(aCols{2}), 'filled', 'MarkerFaceColor', "#0000FF");
+    r = scatter(ax,lim.(ccCols{3}), lim.(aCols{3}), 'filled', 'MarkerFaceColor', "#FFC000");
+
+    % Plot data using column indices
+    d = scatter(ax, data{1, k+1}.Cc, data{1, k+1}.A, 'filled', 'MarkerFaceColor', 'black');
+
+    % Plot Gstar line 
[…]

### 2025-06-04 CO2_response_fitting/Scripts/msuRACiFit_rice_params.Rmd
Updated fitting script

@@
   mean_temps[i] <- mean(datasets[[i]]$Tleaf) 
-  mean_press[i] <- mean(datasets[[i]]$Press) }
+  mean_press[i] <- mean(datasets[[i]]$Press)
+  sem_mean_temps <- sd(mean_temps) / sqrt(length(mean_temps))
+  sem_mean_press <- sd(mean_press) / sqrt(length(mean_press))
+}
 ```
@@
 Gstars_rice<-msuRACiFit::calcGammaStar(13.7,24.6,mean_temps,21) #rice c and dHa 
+sem_Gstars_rice<- sd(Gstars_rice)/ sqrt(length(Gstars_rice))
 Gstars_rice_25<-msuRACiFit::calcGammaStar(13.7,24.6,25,21) #rice c and dHa 
@@
 Gstars_Pa_rice<-Gstars_rice*(1000 / 1000000)*mean_press 
+sem_Gstars_Pa_rice<- sd(Gstars_Pa_rice)/ sqrt(length(Gstars_Pa_rice))
 ```
@@
 all_param$Press <- mean_press
+mean_Kc<-mean(all_param$Kc)
+mean_Ko<-mean(all_param$Ko)
+mean_Kcair<-mean(all_param$Kcair)
+
+sem_Kc <- sd(all_param$Kc)/ sqrt(length(all_param$Kc))
+sem_Ko <- sd(all_param$Ko)/ sqrt(length(all_param$Ko))
+sem_Kcair <- sd(all_param$Kcair)/ sqrt(length(all_param$Kcair))
 ```
@@
 
-## Save parameter outputs:
+### Save parameter outputs:
 
@@
 
-## Produce data tables using parameters fitted for each curve and the SSR assoaciated with each fit:
+## Produce data tables using parameters fitted for each curve and the SSR associated with each fit:
 
@@
 }))
+```
+
+## Compute mean and SEM of parameter values:
+
+```{r}
+VcMax <- mean(combined_results$VcMax)
+J <- mean(combined_results$J)
+TPU <- mean(combined_results$TPU)
+Rd <-  mean(combined_results$rL)
+gm <-  mean(combined_results$gm)
+sem_VcMax <- sd(combined_results$VcMax)/ sqrt(length(combined_results$VcMax))
+sem_J <- sd(combined_results$J)/ sqrt(length(combined_results$J))  
+sem_TPU <- sd(combined_results$TPU)/ sqrt(length(combined_results$TPU)) 
+sem_Rd <- sd(combined_results$rL)/ sqrt(length(combined_results$rL))
+sem_gm <- sd(combined_results$gm)/ sqrt(length(combined_results$gm))   
 ```
